### 2022-09-18 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@b36dda614849f1c7ff3c76e051f1614e8966d6c2 🚀

%!TEX TS-program = xelatex
\documentclass[11pt]{article}

\usepackage[english]{babel}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage[scaled]{helvet}
\usepackage[scaled]{inconsolata}

\usepackage{lastpage}

\usepackage{setspace}

\usepackage{ccicons}

\usepackage[hang,flushmargin]{footmisc}

\usepackage{geometry}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}

\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\makeatletter
\newcounter{tableno}
\newenvironment{tablenos:no-prefix-table-caption}{
  \caption@ifcompatibility{}{
    \let\oldthetable\thetable
    \let\oldtheHtable\theHtable
    \renewcommand{\thetable}{tableno:\thetableno}
    \renewcommand{\theHtable}{tableno:\thetableno}
    \stepcounter{tableno}
    \captionsetup{labelformat=empty}
  }
}{
  \caption@ifcompatibility{}{
    \captionsetup{labelformat=default}
    \let\thetable\oldthetable
    \let\theHtable\oldtheHtable
    \addtocounter{table}{-1}
  }
}
\makeatother

\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\let\PBS=\PreserveBackslash

\usepackage[breaklinks=true]{hyperref}
\hypersetup{colorlinks,%
citecolor=blue,%
filecolor=blue,%
linkcolor=blue,%
urlcolor=blue}
\usepackage{url}

\usepackage{caption}
\setcounter{secnumdepth}{0}
\usepackage{cleveref}

\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

\usepackage{longtable}
\usepackage{booktabs}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

\pagestyle{plain}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\doublespacing

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily The missing link: discerning true from false
negatives when sampling species interaction networks}
\vskip 5em

%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{,}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{,}\quad %
\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
%
\,\textsuperscript{,}\quad %
\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
%
\,\textsuperscript{,}

\textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences\quad \textsuperscript{3}\,Université de
Montréal

\textbf{Correspondance to:}\\
Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\

\vfill
This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
Last revision: \emph{\today}

\clearpage
\thispagestyle{empty}

\vfill

\vfill

\clearpage
\linenumbers
\pagestyle{normal}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Community ecology is fundamentaly about understanding species
interactions. Understanding how species interact underlies many question
in evolutionary biology, community ecology, and is an increasing
imperative to mitigate the anthropogoenic change on Earth's biodiversity
(Jordano 2016a; Makiola \emph{et al.} 2020) and to predict potential
spillover of zoonotic disease (Becker \emph{et al.} 2021). Over the past
couple decades biodiversity data has become increasingly
available---remote-sensing has enabled collection of data on spatial
scales and resolutions previously unimaginable, and improved in-situ
sensing (Stephenson 2020) and adoption of open data practices (Kenall
\emph{et al.} 2014) have substantially amount of data available to
ecologists. Still, widespread data about species \emph{interactions}
remains elusive (\textbf{TIM\_DATASET\_PAPER?}). Often, observing an
interaction between two species requires human sampling, typically
because remote sampling methods can only detect co-occurrence, and this
itself is not necessarily indicative of interaction (Blanchet \emph{et
al.} 2020). This constraint induces biases on species interaction data
subject to the spatial and temporal scales that humans can feasibly
sample.

\emph{Sampling effort} and its impact on the resulting data collected
from ecosystems has encouraged a long history of discourse. The recorded
number of species in a sample depends on the total number of
observations (Walther \emph{et al.} 1995; Willott 2001), as do estimates
of population abundance (Griffiths 1998). This has motivated more
quantitatively robust approaches to account for error in sampling data
in many contexts: to determine if a given species is extinct (Boakes
\emph{et al.} 2015), to determine sampling design (Moore \& McCarthy
2016), and to measure species richness across large scales (Carlson
\emph{et al.} 2020). In the context of interactions, the initial concern
was the compounding effects of limited sampling effort combined with the
amalgamation of data (across both study sites and across taxonomic
scales) could lead any empirical set of observations to inadequately
reflect the reality of how species interact (Paine 1988). Martinez
\emph{et al.} (1999) showed that in a plant-endophyte trophic network,
network connectance is robust to sampling effort, but this done in the
context of a system for which observation of 62,000 total interactions
derived from 164,000 plant-stems was feasible. In some systems
(e.g.~megafauna food-webs) this many observations is either impractical
or infeasible due to the absolute abundance of the species in question.

Because we cannot feasibly observe all (or even many) of the
interactions that occur in nature, our samples end up capturing only a
small fraction of those interactions. This means we can be reasonably
confident two species actually interact if we have a record of it, but
not at all confident that two species \emph{do not} interact if we have
no record of those species observed together. In other words, it is
difficult to distinguish true-negatives (two species \emph{never}
interact) from \emph{false-negatives} (two species interact in some
capacity, but we have not observed it). This is then amplified as the
interaction data we have is geographically toward the usual suspects
(Poisot \emph{et al.} 2021a), This noise in data has practical
consequences for answering questions about species interactions (de
Aguiar \emph{et al.} 2019)---these false-negatives could go on to effect
the inferences we make about network properties and relations among
species, and our predictions about how species will interact in the
future.

This is compounded by semantic confusion about the definition of
``interaction''. Here distinguish between: a species \emph{occurring}, a
species being \emph{observed occurring}, two species being observed
\emph{co-occurring}, and two species being observed \emph{interacting}
(fig.~\ref{fig:taxonomy}). In this manuscript, we refer to species
either as ``interacting''---two species co-occur (and, at least
sometimes, interact)---or ``not-interacting'' (two species that,
regardless of whether they co-occur, neither exhibits any meaningful
effect on the biomass of the other). In fig.~\ref{fig:taxonomy} we see
that, under our definition, observing two species co-occurring is a
prerequisite for observing an interaction between two species.

But species are not observed with equal probability but instead in
proportion to their relative biomass---you are much more likely to
observe a species of high relative abundance than one of very low
relative abundance (Poisot \emph{et al.} 2015). This assumes that there
are no associations in species co-occurrence due to an interaction
(perhaps because this interaction is ``important'' for both species)
(Cazelles \emph{et al.} 2016), but here we show increasing strength of
associations leads to increasing probability of false-negatives in
interaction data. Further observed co-occurrence is often equated with
meaningful interaction strength, but this is not necessarily the case
(Blanchet \emph{et al.} 2020; Strydom \emph{et al.} 2021). Bears and
salmon \emph{interact}---a bear and the microbes in the soil of a dens
interact, but less so.

Here, we show that the probability of observing a actual
``non-interaction'' between species depends on sampling effort, and
suggest that surveys of species interactions can benefit from simulation
modeling of detection probability (Jordano 2016b). We demonstrate that
the realized false-negative rate of interactions is directly related the
relative abundance of a particular species, relationship between total
sampling effort (the total count of all individuals of all species seen)
and false-negative rate. questions we pose and attempt to answer are: 1)
How many times do you have to observe a non-interaction between two
species to be confident in saying that is a true negative? 2) How
``wrong'' are the measurements of network structure as a function of
false-negative probability? and lastly 3) How do false-negatives impact
our ability to make reliable predictions about interactions? We show
that positive associations in co-occurrence data can increase realized
probability of false negatives, and demonstrate these positive
associations are present in two spatially-replicated systems. We
conclude by suggesting that simulation of sampling effort and species
occurrence can and should be used to help design surveys of species
diversity (Moore \& McCarthy 2016), and by advocating use of null models
like those presented here as a tool for guiding design of surveys of
species interactions, and for modeling detection error in predictive
ecological models.

\hypertarget{how-many-observations-of-a-non-interaction-do-we-need-to-classify-it-as-a-true-negative}{%
\section{How many observations of a non-interaction do we need to
classify it as a true
negative?}\label{how-many-observations-of-a-non-interaction-do-we-need-to-classify-it-as-a-true-negative}}

To answer the titular question of this section, we present a naive model
of interaction detection: we assume that every interacting pair of
species is incorrectly observed as a not-interacting with an independent
and fixed probability, which we denote \(p_{fn}\) and subsequently refer
to as the False-Negative Rate (FNR). If we observe the same species
not-interacting \(N\) times, then the probability of a true-negative
(denoted \(p_{tn}\)) is given by \(p_{tn} = 1 - (p_{fn})^N\). This
relation (callend the geometric distribution, a special case of the
negative-binomial distribution) is shown in fig.~\ref{fig:negativebinom}
for varying values of the false negative rate \(p_{fn}\). This
illustrates a fundamental link between our ability to reliably say an
interaction doesn't exist---\(p_{tn}\)---and the number of times we have
observed a given species. In addition, note that there also is no
non-zero \(p_{fn}\) for which we can ever \emph{prove} that an
interaction does not exist---no matter how many observations of
non-interaction \(N\) we have, \(p_{tn} < 1\).

From fig.~\ref{fig:fig1} (A) (and general intuition) it is clear that
the more times we see two species \emph{occurring}, but \emph{not}
interacting, the more likely the interaction is a true negative. But how
does one decide what this threshold of number of observations should be
when planning to sample a given system? If false-negative rates
presented in fig.~\ref{fig:fig1} seem unrealistically high, consider
that species are not observed independent of their relative abundance.
In the next section we demonstrate that distribution of abundance in
ecosystems can lead to realized values of \(p_{fn}\) similar to those in
fig.~\ref{fig:negativebinom} for species with low relative abundance,
simply as a artifact of sampling effort.

\hypertarget{false-negatives-as-a-product-of-relative-abundance}{%
\subsection{False-negatives as a product of relative
abundance}\label{false-negatives-as-a-product-of-relative-abundance}}

Here we show the realized false-negative rate of species interactions
changes drastically with sampling effort, largely due to the intrinsic
variation of abundances within a community. We do this by simulating the
process of observation of species interactions, applied both to 243
empirical food webs from the Mangal database (Banville \emph{et al.}
2021) as well as random food-webs generated using the niche model
(Williams \& Martinez 2000). Our neutral model of observation assumes
each observed species is drawn from the distribution of those species'
abundances at that place and time. Although there is no shortage of
debate as to the processes the govern this distribution of abundances
within a community, this abundance distribution can be reasonably-well
described by a log-normal distribution (Volkov \emph{et al.} 2003) (Note
that in addition to the log-normal distribution, we also tested the case
where the abundance distribution is derived from power-law scaling
\(Z^{(T_i-1)}\) where \(T_i\) is the trophic level of species \(i\) and
\(Z\) is a scaling coefficient. (Savage \emph{et al.} 2004), which
yields the same qualitative behavior, \emph{supplement figure 1}). The
practical consequence of abundance distributions spanning many order of
magnitude is seeing two ``rare'' species interacting requires two low
probability events: observing two rare species \emph{at the same time}.

To simulate the process of observation, for an ecological network \(A\)
with \(S\) species, we sample abundances for each species from a
standard-log-normal distribution. For each true interaction in \(A\)
(i.e.~\(A_{ij} = 1\)) we estimate the probability of observing both
species \(i\) and \(j\) at given place and time by simulating \(n\)
observations of individuals, where the species of the individual
observed at the \(1,2,\dots,n\)-th observation is drawn from the
generated log-normal distribution of abundances. For each pair of
species \((i,j)\), if both \(i\) and \(j\) are observed within the \(n\)
observations, the interaction is tallied as a true positive if
\(A_{ij}=1\) and a false positive otherwise. Similarly, if only one of
\(i\) and \(j\) are observed---\emph{but not both}---in these \(n\)
observations, but \(A_{ij}=1\), this is counted as a false-negative, and
a true-negative otherwise.

In fig.~\ref{fig:fig1} (C) and (D) we see this model of observation
applied to networks generated using the niche model (Williams \&
Martinez 2000) across varying levels of species richness, and in (b)
applied to 243 food-webs from the Mangal database. For all niche model
simulations in this manuscript, for a given number of species \(S\) the
number of interactions is drawn from the flexible-links model fit to
Mangal data (MacDonald \emph{et al.} 2020), effectively drawing the
number of interactions \(L\) for a random niche model food-web as
\(L \sim \text{BetaBinomial}(S^2-S+1, \mu \phi, (1-\mu)\phi)\), where
the MAP estimate of (\(\mu\), \(\phi\)) applied to Mangal data from
MacDonald \emph{et al.} (2020) is \((\mu = 0.086, \phi =24.3)\). All
simulations were done with 500 independent replicates per unique number
of observations \(n\). All analyses presented here are done in Julia
v1.6 (Bezanson \emph{et al.} 2015) using both EcologicalNetworks.jl v0.5
and Mangal.jl v0.4 {[}Banville \emph{et al.} (2021); ZENODO link
TODO{]}. Note that the empirical data also is, due to the phenomena
described here, very likely to \emph{already} have many false negatives,
which is why we are interested in prediction of networks in the first
place---we'll revisit this in the final section.

\begin{figure}
\hypertarget{fig:fig1}{%
\centering
\includegraphics{./figures/fig1.png}
\caption{A) The probability an observed interaction is a true negative
(y-axis) given how many times it has been sampled as a non-interaction
(x-axis). Each color reflects a different value of \(p_{fn}\), the
false-negative rate (FNR). this is effectively the cdf of the
negative-binomial distribution with \(r=1\). (B) The expected needed
observations of all individuals of all species (y-axis) required to
obtain a goal number of observations (colors) of a particular species,
and a function of the relative abundance of that focal species (x-axis).
(C) and (D): False negative rate (y-axis) as a function of total
sampling effort (x-axis) and network size, computed using the method
described above. For 500 independent draws from the niche model
Williams2000SimRul at varying levels of species richness (colors) with
connectance drawn according to the flexible-links model
MacDonald2020RevLin as described in the main text. For each draw from
the niche model, 200 sets of 1500 observations are simulated, for which
each the mean false negative rate at each observation-step is computed.
Means denoted with points, with \(1\sigma\) in the first shade and
\(2\sigma\) in the second. B: empirical food webs from Mangal database
in teal, applied to the same process as the A. The outlier on panel B is
a 714 species food-web}\label{fig:fig1}
}
\end{figure}

In panel (c) of fig.~\ref{fig:totalobs}, we show the expected number of
total observations needed to obtain a ``goal'' number of observations
(colors) of a particular ``focal'' species. As an example, if we
hypothesize that \(A\) and \(B\) do not interact, and we want to see
species \(A\) and \(B\) both co-occurring and not-interacting 10 times
to be confident this is a negative (a la fig.~\ref{fig:negativebinom}),
then we need an expected 10,000 observations of all species if the
relative abundance of \(A\) is 0.00125.

Empirical data on interactions are subject to the practical limitations
of funding and human-work hours, and therefore existing data tend to
fall on the order on 100s or 1000s observations of individuals per site
(Nielsen \& Bascompte 2007; Schwarz \emph{et al.} 2020; Resasco \emph{et
al.} 2021). Clear aggregation of this data has proven difficult to find
and a meta-analysis of network data and sampling effort seems both
pertinent and necessary, in addition to the effects of aggregation of
interactions across taxonomic scales (Gauzens \emph{et al.} 2013;
Giacomuzzo \& Jordán 2021). Further, from fig.~\ref{fig:totalobs} it is
evident that the number of species considered in a study is inseparable
from the false-negative rate in that study, and this effect should be
taken into account when designing samples of ecological networks in the
future.

We conclude this section by advocating for the use of neutral models
similar to above to generate expectations about the number of
false-negatives in a data set of a given size. This could prove fruitful
both for designing surveys of interactions (Canard \emph{et al.} 2012),
but also because we may want to incorporate models of observation error
into predictive models (Joseph 2020). Additionally, one must consider
the context for sampling---is the goal to detect a particular species
\(A\) (as in fig.~\ref{fig:totalobs} (c)), or to get a representative
sample of interactions across the species pool? This argument is
well-considered when sampling species (Willott 2001), but has not yet
been internalized for designing samples of communities.

\hypertarget{positive-associations-can-increase-the-probability-of-false-negatives}{%
\subsection{Positive associations can increase the probability of
false-negatives}\label{positive-associations-can-increase-the-probability-of-false-negatives}}

This model above doesn't consider the possibility that there are
positive or negative associations which shift the probability of
observing two species together due to their interaction (Cazelles
\emph{et al.} 2016). However, here we demonstrate that the probability
of observing a false negative can be \emph{higher} if there is some
positive association between occurrence of species \(A\) and \(B\).

If we denote the probability that we observe an interaction we know
exists between \(A\) and \(B\) as \(P(AB)\), and if there is \emph{no}
association between the marginal probabilities of observing \(A\) and
observing \(B\), denoted \(P(A)\) and \(P(B)\) respectively, then the
probability of observing the interaction \(P(AB) = P(A)P(B)\). In the
other case where there \emph{is} some positive strength of association
between observing both \(A\) and \(B\) because this interaction is
``important'' for each species, then the probability of observation both
\(A\) and \(B\), \(P(AB)\), is greater than \(P(A)P(B)\) as \(P(A)\) and
\(P(B)\) are not independent and instead are positively correlated,
\emph{i.e.} \(P(AB) > P(A)P(B)\). In this case, the probability of
observing a false negative in our naive model from
fig.~\ref{fig:negativebinom} is \(p_{fn} = 1 - P(AB)\) which due to the
above inequality implies \(p_{fn} \geq 1 - P(A)P(B)\) which indicates
increasingly greater probability of a false negative as
\(P(AB) \to P(AB) \gg P(A)P(B)\).

However this does not consider variation in species abundance in space
and time, (Poisot \emph{et al.} 2015). If positive or negative
associations between species structure variation in the distribution of
\(P(AB)\) across space/time, then the spatial/temporal biases induced by
data collection would further impact the realized false negative rate,
as the probability of false negative would not be constant for each pair
of species across sites. To test for this association empirical data, we
use two datasets: a set of host-parasite interactions sampled across 51
sites with 327 total taxa (Hadfield \emph{et al.} 2014) and a set of 18
New Zealand freshwater stream food webs with 566 total taxa (Thompson \&
Townsend 2000). We simply compute the empirical marginal distribution of
species occurrence, and compare the product of the marginals,
\(P(A)P(B)\), to the empirical joint distribution \(P(AB)\).

\begin{figure}
\hypertarget{fig:associations}{%
\centering
\includegraphics{./figures/positiveassociations.png}
\caption{Top: Hadfield, Bottom: NZ Stream Foodwebs. Effectively a
version of Cazelles \emph{et al.} (2016) figure 1 panel A. Both
distributions have \(\mu \neq 0\) with
\(p < 10^{-50}\)}\label{fig:associations}
}
\end{figure}

In fig.~\ref{fig:associations}, both host-parasite system (top) and
food-web (bottom) exhibit these positive associations. There is no
reason to expect the strength of this association to be the same in
different systems. At the moment, computing this metric for all of the
networks in the Mangal database proves challenging as most data sets use
different taxonmic identifiers, often at different resolutions. These
particular datasets (Thompson \& Townsend 2000; Hadfield \emph{et al.}
2014) were usable because they already have been sorted to have a fixed
taxonomic backbone (as part of EcologicalNetworks.jl (Banville \emph{et
al.} 2021)). Applying this in bulk to Mangal food-webs presents the
difficulty of resolving different taxon identifiers across spatial
samples of species with to different resolutions, which is why we can't
simply apply this to the whole Mangal database---this highlights a
general problem of resolving taxonomic indentifiers which use different
names and different resolutions in different ecological datasets, which
is a problem that needs to be addressed for computational approaches to
scale up to the world of big-ecological-data we hope to build, although
this is a task that may be aided via natural-language-processing
methods.

\hypertarget{the-impact-of-false-negatives-on-network-analysis-and-prediction}{%
\section{The impact of false-negatives on network analysis and
prediction}\label{the-impact-of-false-negatives-on-network-analysis-and-prediction}}

We now transition toward assessing the effects of false negatives in
data on the properties of the networks which we derive from this
interaction data, and their effect on models for predicting interactions
in the future.

\hypertarget{effects-of-false-negatives-on-network-properties}{%
\subsection{Effects of false-negatives on network
properties}\label{effects-of-false-negatives-on-network-properties}}

Here we simulate the process of observation with error to generate
synthetic data with a known proportion of false negatives, and compare
the computed network properties of the original ``true'' network to the
computed properties of the ``observed'' network with added
false-negatives. In fig.~\ref{fig:properties} we see the mean-squared
error of connectance, mean degree-centrality, and spectral radius,
computed across 2000, 2000, and 300 replicates respectively at each
value of the false negative rate \(p_{fn}\). All replicates use random
food-webs simulated using the niche model (Williams \& Martinez 2000)
with \(100\) species and connectance drawn from the flexible-links model
(MacDonald \emph{et al.} 2020) as before.

\begin{figure}
\hypertarget{fig:properties}{%
\centering
\includegraphics{./figures/props_specrad.png}
\caption{The mean-squared error (y-axis) of various network properties
(different colors) across various simulated false-negative rates
(x-axis). Means denoted with points, with \(1\sigma\) in the first shade
and \(2\sigma\) in the second.}\label{fig:properties}
}
\end{figure}

We consider three properties: connectance, mean-degree-centrality, and
spectral radius, indicative of local, meso, and global structure.
Connectance is effectively a node-level property, a proxy for the degree
distribution. Degree-centrality captures a different aspect of network
structure than connectance, more indicative of meso-level properties
that describe local `regions' of nodes interact. Spectral radius
(equivalent to the magnitude of the largest eigenvalue of \(A\)) is a
measure of global structure, and demonstrates the most variability in
response to false-negatives. For example, if a false-negative splits a
metaweb into two components, spectral-radius becomes the largest
eigenvalue of each of those two components. Also note that the form of
this error function varies little as species richness changes
(\emph{supplemental figure 2}). Practically, fig.~\ref{fig:properties}
shows us that different scales of measuring network structure vary in
their response to false negatives---connectance responds roughly
linearly to false negatives, whereas mean-degree-centrality decisively
does not. This implies that false-negatives adversely could effect
indirect interactions (Williams \emph{et al.} 2002).

\hypertarget{effects-of-false-negatives-on-ability-to-make-predictions}{%
\subsection{Effects of false negatives on ability to make
predictions}\label{effects-of-false-negatives-on-ability-to-make-predictions}}

Here, we assess the effect of false negatives in data on our ability to
make predictions about interactions. The prevalence of false-negatives
in data is the catalyst for interaction prediction in the first place,
and as a result methods have been proposed to counteract this bias
(Stock \emph{et al.} 2017; Poisot \emph{et al.} 2021b). However, it is
feasible this could induce too much noise for a interaction prediction
model to detect the signal of interaction chance from to the latent
properties of each species derived from the empirical network if the
number of false-negatives in a dataset becomes too overwhelming.

To test this, we use the same predictive model and dataset as in Strydom
\emph{et al.} (2021) to predict a metaweb from various empirical slices
of the species pool observed across space. This dataset from Hadfield
\emph{et al.} (2014) describes host-parasite interaction networks
sampled across 51 sites. We partition the data into 80-20 training-test
split, and then seed the training data with false negatives varying
rates, but crucially do nothing to the test data. We use the same model,
a neural-network with 3 feed-forward layers to predict outputs based on
features extracted from co-occurence (see Strydom \emph{et al.} (2021)
for more details). The single modification we make to the model is not
enforcing a number of positives in the training data as this constraint
is eventually impossible for increasing FNR. In fig.~\ref{fig:rocpr}, we
show receiving-operating-characteristic (ROC) and precision-recall (PR)
curves for the model with varying levels of synthetic false-negatives
added to the data.

\begin{figure}
\hypertarget{fig:rocpr}{%
\centering
\includegraphics{./figures/rocpr_falsenegatives.png}
\caption{Receiver-operating-characteristic (left) and precision-recall
(right) curves for the model on varying levels of false-negatives in the
data (colors). For each value of FNR, we run 30 random training/test
splits on 80/20 percent of the data. Replica of figure 1 in Strydom
\emph{et al.} (2021)}\label{fig:rocpr}
}
\end{figure}

Interestingly, the performance of the model from Strydom \emph{et al.}
(2021) changes little with many added false-negatives, which is good
evidence in favor neural-networks as a class of model for interaction
detection. Again, similar to our caveat in the previous section, this
dazta is \emph{already} likely to have many false-negatives, so the
effects of adding more as we do in this illustration might be mitigated
because there are already non-simulated false-negatives in the original
data which impact the models performance, even in the \(p_{fn} = 0\)
case.

We conclude be proposing that simulating the effects of false negatives
in this way can serve as an additional validation tool when aiming to
detect structural properties of networks using generative null models
(Connor \emph{et al.} 2017), or when evaluating the robustness of a
predictive model.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Here, we have demonstrated that we expect false-negatives in species
interaction datasets purely due to the distribution of abundances within
a community. Positive associations between species occurrence (Cazelles
\emph{et al.} 2016) can increase the realized false-negative rate if the
sampling effort is limited, and we have presented evidence of this
non-random structure of co-occurrence in two sets of
spatially-replicated ecological network samples. We have also shown that
false-negatives can cause varying responses in our measurements of
network properties and further could impact our ability to reliably
predict interactions, which highlights the need for further research
into methods for correcting this bias in existing data (Stock \emph{et
al.} 2017). A brief caveat here is that we do not consider the rate of
false-positives---in large part false-positives can be explained by
misidentification of species, although this could be a relevant
consideration in some cases.

What does the future hold for this research? A better understanding of
how false-negatives impact our analyses and prediction of ecological
networks is a practical necessity. False-negatives could pose a problem
for many forms of inference in network ecology. For example, if we aim
to measure structural or dynamic stability of a network, or to infer
indirect interactions (Williams \emph{et al.} 2002), these estimates
could be prone to error if the observed network is not sampled
``enough''. What exactly ``enough'' means is then specific to the
application, and should be assessed via methods like those here when
designing samples. Further, predictions about network rewiring (Thompson
\& Gonzalez 2017) due to a changing climate could be error-prone without
accounting for interactions that have not been observed but that still
may become climatically infeasible.

This highlights the need for a quantitatively robust approach samples
design: for interactions (Jordano 2016b) and otherwise (Carlson \emph{et
al.} 2020). The primary takeaway is that when planning the sampling
effort across sites, it is necessary to take both the size of the
species pool into account. Further, simulating the process of
observation could be a powerful tool for planing study design which
takes relative abundance into account, and provide a null baseline for
detection of interaction strength. A model similar to that here can and
should be used to provide a neutral expectation of true-negative
probability given a number of observations of individuals at a given
place and time.

As we derive from fig.~\ref{fig:negativebinom}, we can never guarantee
there are no false-negatives in data. In recent years, there has been
interest toward explicitly accounting for false-negatives in models
(Stock \emph{et al.} 2017; Young \emph{et al.} 2021), and toward a
predictive approach toward interactions ---rather than expect that our
samples can fully capture all interactions, we know that some
interactions between species will not be observed due to finite sampling
capacity, and instead we must impute the true metaweb of interactions
given a set of samples (Strydom \emph{et al.} 2021). As a result, better
predictive approaches are needed for interaction networks (Strydom
\emph{et al.} 2021), and building models that explicitly account for
observation error is a necessary step forward for predictive ecological
models (Johnson \& Larremore 2021; Young \emph{et al.} 2021). Neural
networks, like the one used to predict interactions in the above
section, have been used to reflect hidden states which account for
detection error in occupancy modeling (Joseph 2020), and could be
integrated in the predictive models of the future.

A better conceptual framework for designing surveys and monitoring
networks, and incorporating sequential observations over time is clearly
needed (Carlson \emph{et al.} 2020), combined with a meta-analysis of
sampling effort and taxonomic resolution in existing data. Incorporating
a better understanding of sampling effects and bias on both the future
design of biodiversity monitoring systems, and the predictive models we
wish to apply to this data, is imperative in making actionable
predictions about the future of ecological interactions on our planet.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Banville2021ManJl}{}}%
Banville, F., Vissault, S. \& Poisot, T. (2021).
\href{https://doi.org/10.21105/joss.02721}{Mangal.jl and
EcologicalNetworks.jl: Two complementary packages for analyzing
ecological networks in Julia}. \emph{Journal of Open Source Software},
6, 2721.

\leavevmode\vadjust pre{\hypertarget{ref-Becker2021OptPre}{}}%
Becker, D.J., Albery, G.F., Sjodin, A.R., Poisot, T., Bergner, L.M.,
Dallas, T.A., \emph{et al.} (2021).
\href{https://doi.org/10.1101/2020.05.22.111344}{Optimizing predictive
models to prioritize viral discovery in zoonotic reservoirs}.
\emph{bioRxiv}, 2020.05.22.111344.

\leavevmode\vadjust pre{\hypertarget{ref-Bezanson2015JulFre}{}}%
Bezanson, J., Edelman, A., Karpinski, S. \& Shah, V.B. (2015).
\href{https://arxiv.org/abs/1411.1607}{Julia: A Fresh Approach to
Numerical Computing}. \emph{arXiv:1411.1607 {[}cs{]}}.

\leavevmode\vadjust pre{\hypertarget{ref-Blanchet2020CooNot}{}}%
Blanchet, F.G., Cazelles, K. \& Gravel, D. (2020).
\href{https://doi.org/10.1111/ele.13525}{Co-occurrence is not evidence
of ecological interactions}. \emph{Ecology Letters}, 23, 1050--1063.

\leavevmode\vadjust pre{\hypertarget{ref-Boakes2015InfSpe}{}}%
Boakes, E.H., Rout, T.M. \& Collen, B. (2015).
\href{https://doi.org/10.1111/2041-210X.12365}{Inferring species
extinction: The use of sighting records}. \emph{Methods in Ecology and
Evolution}, 6, 678--687.

\leavevmode\vadjust pre{\hypertarget{ref-Canard2012EmeStr}{}}%
Canard, E., Mouquet, N., Marescot, L., Gaston, K.J., Gravel, D. \&
Mouillot, D. (2012).
\href{https://doi.org/10.1371/journal.pone.0038295}{Emergence of
Structural Patterns in Neutral Trophic Networks}. \emph{PLOS ONE}, 7,
e38295.

\leavevmode\vadjust pre{\hypertarget{ref-Carlson2020WhaWou}{}}%
Carlson, C.J., Dallas, T.A., Alexander, L.W., Phelan, A.L. \& Phillips,
A.J. (2020). \href{https://doi.org/10.1098/rspb.2020.1841}{What would it
take to describe the global diversity of parasites?} \emph{Proceedings
of the Royal Society B: Biological Sciences}, 287, 20201841.

\leavevmode\vadjust pre{\hypertarget{ref-Cazelles2016TheSpe}{}}%
Cazelles, K., Araújo, M.B., Mouquet, N. \& Gravel, D. (2016).
\href{https://doi.org/10.1007/s12080-015-0281-9}{A theory for species
co-occurrence in interaction networks}. \emph{Theoretical Ecology}, 9,
39--48.

\leavevmode\vadjust pre{\hypertarget{ref-Connor2017UsiNul}{}}%
Connor, N., Barberán, A. \& Clauset, A. (2017).
\href{https://doi.org/10.1371/journal.pone.0176751}{Using null models to
infer microbial co-occurrence networks}. \emph{PLOS ONE}, 12, e0176751.

\leavevmode\vadjust pre{\hypertarget{ref-deAguiar2019RevBia}{}}%
de Aguiar, M.A.M., Newman, E.A., Pires, M.M., Yeakel, J.D., Boettiger,
C., Burkle, L.A., \emph{et al.} (2019).
\href{https://doi.org/10.7717/peerj.7566}{Revealing biases in the
sampling of ecological interaction networks}. \emph{PeerJ}, 7, e7566.

\leavevmode\vadjust pre{\hypertarget{ref-Gauzens2013FooAgg}{}}%
Gauzens, B., Legendre, S., Lazzaro, X. \& Lacroix, G. (2013). Food-web
aggregation, methodological and functional issues. \emph{Oikos}, 122,
1606--1615.

\leavevmode\vadjust pre{\hypertarget{ref-Giacomuzzo2021FooWeb}{}}%
Giacomuzzo, E. \& Jordán, F. (2021).
\emph{\href{https://doi.org/10.1101/2021.04.18.440319}{Food web
aggregation: Effects on key positions}} (Preprint). Ecology.

\leavevmode\vadjust pre{\hypertarget{ref-Griffiths1998SamEff}{}}%
Griffiths, D. (1998).
\href{https://doi.org/10.1046/j.1365-2656.1998.00244.x}{Sampling effort,
regression method, and the shape and slope of sizeabundance relations}.
\emph{Journal of Animal Ecology}, 67, 795--804.

\leavevmode\vadjust pre{\hypertarget{ref-Hadfield2014TalTwo}{}}%
Hadfield, J.D., Krasnov, B.R., Poulin, R. \& Nakagawa, S. (2014).
\href{https://doi.org/10.1086/674445}{A Tale of Two Phylogenies:
Comparative Analyses of Ecological Interactions}. \emph{The American
Naturalist}, 183, 174--187.

\leavevmode\vadjust pre{\hypertarget{ref-Johnson2021BayEst}{}}%
Johnson, E.K. \& Larremore, D.B. (2021).
\href{https://doi.org/10.1101/2021.07.06.451319}{Bayesian estimation of
population size and overlap from random subsamples}. \emph{bioRxiv},
2021.07.06.451319.

\leavevmode\vadjust pre{\hypertarget{ref-Jordano2016ChaEco}{}}%
Jordano, P. (2016a).
\href{https://doi.org/10.1371/journal.pbio.1002559}{Chasing Ecological
Interactions}. \emph{PLOS Biology}, 14, e1002559.

\leavevmode\vadjust pre{\hypertarget{ref-Jordano2016SamNet}{}}%
Jordano, P. (2016b).
\href{https://doi.org/10.1111/1365-2435.12763}{Sampling networks of
ecological interactions}. \emph{Functional Ecology}.

\leavevmode\vadjust pre{\hypertarget{ref-Joseph2020NeuHie}{}}%
Joseph, M.B. (2020). \href{https://doi.org/10.1111/ele.13462}{Neural
hierarchical models of ecological populations}. \emph{Ecology Letters},
23, 734--747.

\leavevmode\vadjust pre{\hypertarget{ref-Kenall2014OpeFut}{}}%
Kenall, A., Harold, S. \& Foote, C. (2014).
\href{https://doi.org/10.1186/1471-2148-14-66}{An open future for
ecological and evolutionary data?} \emph{BMC Evolutionary Biology}, 14,
66.

\leavevmode\vadjust pre{\hypertarget{ref-MacDonald2020RevLin}{}}%
MacDonald, A.A.M., Banville, F. \& Poisot, T. (2020).
\href{https://doi.org/10.1016/j.patter.2020.100079}{Revisiting the
Links-Species Scaling Relationship in Food Webs}. \emph{Patterns}, 1.

\leavevmode\vadjust pre{\hypertarget{ref-Makiola2020KeyQue}{}}%
Makiola, A., Compson, Z.G., Baird, D.J., Barnes, M.A., Boerlijst, S.P.,
Bouchez, A., \emph{et al.} (2020).
\href{https://doi.org/10.3389/fenvs.2019.00197}{Key Questions for
Next-Generation Biomonitoring}. \emph{Frontiers in Environmental
Science}, 7.

\leavevmode\vadjust pre{\hypertarget{ref-Martinez1999EffSam}{}}%
Martinez, N.D., Hawkins, B.A., Dawah, H.A. \& Feifarek, B.P. (1999).
\href{https://doi.org/10.1890/0012-9658(1999)080\%5B1044:EOSEOC\%5D2.0.CO;2}{Effects
of Sampling Effort on Characterization of Food-Web Structure}.
\emph{Ecology}, 80, 1044--1055.

\leavevmode\vadjust pre{\hypertarget{ref-Moore2016OptEco}{}}%
Moore, A.L. \& McCarthy, M.A. (2016).
\href{https://doi.org/10.1111/2041-210X.12564}{Optimizing ecological
survey effort over space and time}. \emph{Methods in Ecology and
Evolution}, 7, 891--899.

\leavevmode\vadjust pre{\hypertarget{ref-Nielsen2007EcoNet}{}}%
Nielsen, A. \& Bascompte, J. (2007).
\href{https://doi.org/10.1111/j.1365-2745.2007.01271.x}{Ecological
networks, nestedness and sampling effort}. \emph{Journal of Ecology},
95, 1134--1141.

\leavevmode\vadjust pre{\hypertarget{ref-Paine1988RoaMap}{}}%
Paine, R.T. (1988). \href{https://doi.org/10.2307/1941141}{Road Maps of
Interactions or Grist for Theoretical Development?} \emph{Ecology}, 69,
1648--1654.

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2021GloKno}{}}%
Poisot, T., Bergeron, G., Cazelles, K., Dallas, T., Gravel, D.,
MacDonald, A., \emph{et al.} (2021a).
\href{https://doi.org/10.1111/jbi.14127}{Global knowledge gaps in
species interaction networks data}. \emph{Journal of Biogeography},
jbi.14127.

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2021ImpMam}{}}%
Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M.J., Becker, D.J.,
Albery, G.F., \emph{et al.} (2021b).
\href{https://arxiv.org/abs/2105.14973}{Imputing the mammalian virome
with linear filtering and singular value decomposition}.
\emph{arXiv:2105.14973 {[}q-bio{]}}.

\leavevmode\vadjust pre{\hypertarget{ref-Poisot2015SpeWhy}{}}%
Poisot, T., Stouffer, D.B. \& Gravel, D. (2015).
\href{https://doi.org/10.1111/oik.01719}{Beyond species: Why ecological
interaction networks vary through space and time}. \emph{Oikos}, 124,
243--251.

\leavevmode\vadjust pre{\hypertarget{ref-Resasco2021PlaPol}{}}%
Resasco, J., Chacoff, N.P. \& Vázquez, D.P. (2021).
\href{https://doi.org/10.1002/ecy.3359}{Plantpollinator interactions
between generalists persist over time and space}. \emph{Ecology}, 102,
e03359.

\leavevmode\vadjust pre{\hypertarget{ref-Savage2004EffBod}{}}%
Savage, V.M., Gillooly, J.F., Brown, J.H., West, G.B. \& Charnov, E.L.
(2004). \href{https://doi.org/10.1086/381872}{Effects of Body Size and
Temperature on Population Growth.} \emph{The American Naturalist}, 163,
429--441.

\leavevmode\vadjust pre{\hypertarget{ref-Schwarz2020TemSca}{}}%
Schwarz, B., Vázquez, D.P., CaraDonna, P.J., Knight, T.M., Benadi, G.,
Dormann, C.F., \emph{et al.} (2020).
\href{https://doi.org/10.1111/oik.07303}{Temporal scale-dependence of
plantpollinator networks}. \emph{Oikos}, 129, 1289--1302.

\leavevmode\vadjust pre{\hypertarget{ref-Stephenson2020TecAdv}{}}%
Stephenson, P. (2020).
\href{https://doi.org/10.1016/j.cosust.2020.08.005}{Technological
advances in biodiversity monitoring: Applicability, opportunities and
challenges}. \emph{Current Opinion in Environmental Sustainability}, 45,
36--41.

\leavevmode\vadjust pre{\hypertarget{ref-Stock2017LinFil}{}}%
Stock, M., Poisot, T., Waegeman, W. \& De Baets, B. (2017).
\href{https://doi.org/10.1038/srep45908}{Linear filtering reveals false
negatives in species interaction data}. \emph{Scientific Reports}, 7,
45908.

\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021RoaPre}{}}%
Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
Desjardins-Proulx, P., \emph{et al.} (2021).
\emph{\href{https://doi.org/10.32942/osf.io/eu7k3}{A Roadmap Toward
Predicting Species Interaction Networks (Across Space and Time)}}
(Preprint). EcoEvoRxiv.

\leavevmode\vadjust pre{\hypertarget{ref-Thompson2017DisGov}{}}%
Thompson, P.L. \& Gonzalez, A. (2017).
\href{https://doi.org/10.1038/s41559-017-0162}{Dispersal governs the
reorganization of ecological networks under environmental change}.
\emph{Nature Ecology \& Evolution}, 1, 1--8.

\leavevmode\vadjust pre{\hypertarget{ref-Thompson2000ResSol}{}}%
Thompson, R.M. \& Townsend, C.R. (2000).
\href{https://doi.org/10.1046/j.1365-2427.2000.00579.x}{Is resolution
the solution?: The effect of taxonomic resolution on the calculated
properties of three stream food webs}. \emph{Freshwater Biology}, 44,
413--422.

\leavevmode\vadjust pre{\hypertarget{ref-Volkov2003NeuThe}{}}%
Volkov, I., Banavar, J.R., Hubbell, S.P. \& Maritan, A. (2003).
\href{https://doi.org/10.1038/nature01883}{Neutral theory and relative
species abundance in ecology}. \emph{Nature}, 424, 1035--1037.

\leavevmode\vadjust pre{\hypertarget{ref-Walther1995SamEff}{}}%
Walther, B.A., Cotgreave, P., Price, R.D., Gregory, R.D. \& Clayton,
D.H. (1995).
\href{https://doi.org/10.1016/0169-4758(95)80047-6}{Sampling Effort and
Parasite Species Richness}. \emph{Parasitology Today}, 11, 306--310.

\leavevmode\vadjust pre{\hypertarget{ref-Williams2002TwoDeg}{}}%
Williams, R.J., Berlow, E.L., Dunne, J.A., Barabasi, A.-L. \& Martinez,
N.D. (2002). \href{https://doi.org/10.1073/pnas.192448799}{Two degrees
of separation in complex food webs}. \emph{Proceedings of the National
Academy of Sciences}, 99, 12913--12916.

\leavevmode\vadjust pre{\hypertarget{ref-Williams2000SimRul}{}}%
Williams, R.J. \& Martinez, N.D. (2000).
\href{https://doi.org/10.1038/35004572}{Simple rules yield complex food
webs}. \emph{Nature}, 404, 180--183.

\leavevmode\vadjust pre{\hypertarget{ref-Willott2001SpeAcc}{}}%
Willott, S.J. (2001).
\href{https://doi.org/10.1046/j.1365-2664.2001.00589.x}{Species
accumulation curves and the measure of sampling effort}. \emph{Journal
of Applied Ecology}, 38, 484--486.

\leavevmode\vadjust pre{\hypertarget{ref-Young2021RecPla}{}}%
Young, J.-G., Valdovinos, F.S. \& Newman, M.E.J. (2021).
\href{https://doi.org/10.1038/s41467-021-24149-x}{Reconstruction of
plantpollinator networks from observational data}. \emph{Nature
Communications}, 12, 3911.

\end{CSLReferences}

\end{document}

### 2022-09-18 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@b36dda614849f1c7ff3c76e051f1614e8966d6c2 🚀

--- 2022-09-18 draft.tex
@@
 %!TEX TS-program = xelatex
-\documentclass[11pt]{article}
+\documentclass[10pt,oneside]{article}
+\usepackage[fontsize=9pt]{scrextend}
 
@@
 \newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}
-
-\usepackage{lineno}
-\usepackage[nolists,noheads]{endfloat}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}
+
+\geometry{includemp,
+            letterpaper,
+            top=2.4cm,
+            bottom=2.4cm,
+            left=1.0cm,
+            right=1.0cm,
+            marginparwidth=5cm,
+            marginparsep=1.0cm}
+
+\usepackage[singlelinecheck=off]{caption}
+
+\captionsetup{
+  font={small},
+  labelfont={bf},
+  format=plain,
+  labelsep=quad
+}
+
+\usepackage{floatrow}
+
+\floatsetup[figure]{margins=hangright,
+              facing=no,
+              capposition=beside,
+              capbesideposition={center,outside},
+              floatwidth=\textwidth}
+
+% \floatsetup[table]{margins=hangright,
+%              facing=no,
+%              capposition=beside,
+%              capbesideposition={center,outside},
+%              floatwidth=\textwidth}
 
@@
 
-\tolerance=1
-\emergencystretch=\maxdimen
-\hyphenpenalty=10000
-\hbadness=10000
-
-\doublespacing
+\setcounter{secnumdepth}{5}
+
+\usepackage{titlesec}
+
+\titleformat{\section}[block]
+{\normalfont\large\sffamily}
+{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}
+
+\titleformat{\subsection}[runin]
+{\normalfont\fontseries{b}\selectfont\filright\sffamily}
+{\thesubsection.}{.5em}{}
+
+\titleformat{\subsubsection}[runin]
+{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}
+
+\fancypagestyle{firstpage}
+{
+   \fancyhf{}
+   \renewcommand{\headrulewidth}{0pt}
+   \fancyfoot[R]{\footnotesize\ccby}
+   \fancyfoot[L]{\footnotesize\sffamily\today}
+}
 
@@
 }
+
+\usepackage{tikz}
 \begin{document}
-\raggedright
-\thispagestyle{empty}
-{\Large\bfseries\sffamily The missing link: discerning true from false
-negatives when sampling species interaction networks}
-\vskip 5em
-
+\tikz [remember picture, overlay] %
+\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
+\pagestyle{normal}
+\thispagestyle{firstpage}
+
+\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}
+
+\noindent {\LARGE \textbf{\textsf{The missing link: discerning true from
+false negatives when sampling species interaction networks}}}
+
+\medskip
+\begin{flushleft}
+{\small
 %
@@
 %
-\,\textsuperscript{,}\quad %
+\,\textsuperscript{,}, %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
 %
-\,\textsuperscript{,}\quad %
+\,\textsuperscript{,}, %
 \href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
 %
-\,\textsuperscript{,}\quad %
+\,\textsuperscript{,}, %
 \href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
@@
 \,\textsuperscript{,}
-
-\textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences\quad \textsuperscript{3}\,Université de
-Montréal
-
+\vskip 1em
+\textsuperscript{1}\,McGill University; \textsuperscript{2}\,Québec
+Centre for Biodiversity Sciences; \textsuperscript{3}\,Université de
+Montréal\\
+\vskip 1em
 \textbf{Correspondance to:}\\
 Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\
-
-\vfill
-This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
-Last revision: \emph{\today}
-
-\clearpage
-\thispagestyle{empty}
-
-\vfill
-
-\vfill
-
-\clearpage
-\linenumbers
-\pagestyle{normal}
+}
+\end{flushleft}
+
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
+\noindent
+
+\marginpar{\vskip 1em\flushright
+{\small{\bfseries Keywords}:\par
+pandoc\\pandoc-crossref\\github actions\\}
+}
+
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
 

### 2022-09-24 src/_computemeasures.jl
:sparkles: code updates

@@ -1,0 +1,95 @@
+struct ConfusionMatrix
+    tp::Any
+    tn::Any
+    fp::Any
+    fn::Any
+    function ConfusionMatrix(a, b, c, d)
+        s = a + b + c + d
+        return new(a / s, b / s, c / s, d / s)
+    end
+end
+
+ConfusionMatrix(A::Matrix{Float64}) = ConfusionMatrix(A[1, 1], A[2, 2], A[2, 1], A[1, 2])
+ConfusionMatrix(A::Matrix) = ConfusionMatrix(A[1, 1], A[2, 2], A[2, 1], A[1, 2])
+
+tpr(M::ConfusionMatrix) = M.tp / (M.tp + M.fn)
+tnr(M::ConfusionMatrix) = M.tn / (M.tn + M.fp)
+ppv(M::ConfusionMatrix) = M.tp / (M.tp + M.fp)
+npv(M::ConfusionMatrix) = M.tn / (M.tn + M.fn)
+fnr(M::ConfusionMatrix) = M.fn / (M.fn + M.tp)
+fpr(M::ConfusionMatrix) = M.fp / (M.fp + M.tn)
+fdir(M::ConfusionMatrix) = M.fp / (M.fp + M.tp)
+fomr(M::ConfusionMatrix) = M.fn / (M.fn + M.tn)
+plr(M::ConfusionMatrix) = tpr(M) / fpr(M)
+nlr(M::ConfusionMatrix) = fnr(M) / tnr(M)
+pt(M::ConfusionMatrix) = sqrt(fpr(M)) / (sqrt(tpr(M)) + sqrt(fpr(M)))
+csi(M::ConfusionMatrix) = M.tp / (M.tp + M.fn + M.fp)
+prevalence(M::ConfusionMatrix) = (M.tp + M.fn) / (M.tp + M.fn + M.tn + M.fp)
+accuracy(M::ConfusionMatrix) = (M.tp + M.tn) / (M.tp + M.tn + M.fp + M.fn)
+balanced(M::ConfusionMatrix) = (tpr(M) + tnr(M)) * 0.5
+f1(M::ConfusionMatrix) = 2 * (ppv(M) * tpr(M)) / (ppv(M) + tpr(M))
+fm(M::ConfusionMatrix) = sqrt(ppv(M) * tpr(M))
+informedness(M::ConfusionMatrix) = tpr(M) + tnr(M) - 1.0
[…]

### 2022-09-24 src/clean_mangal_data.jl

@@ -4,133 +4,218 @@ using ProgressMeter
 using Plots
 using DataFrames
 using CSV
-
+using BSON
 datasets()
 
 
 sets = Dict(
-    "hawkins_goeden_1984" => "Hawkins & Goeden (1984)",     
+    #"hawkins_goeden_1984" => "Hawkins & Goeden (1984)",      # not enough samples
     "kolpelke_et_al_2017" => "Kopelke et al. (2017)",
     "hadfield_2014" => "Hafield et al (2014)",
     "havens_1992" => "Havens (1992)", 
-    "ricciardi_2010" => "Ricciardi & MacIsaac (2010)",
     "ponisio_2017" => "Ponisio et al. (2017)",
-    "ruzicka_2012" => "Ruzicka et al. (2012)",
-    "RMBL_pollination" => "CaraDonna et al. (2015)", # this is not fully connected and thus breaks 
-    "fryer_1959" => "Fryer (1959)",
+    "RMBL_pollination" => "CaraDonna et al. (2015)",        
     "closs_1994" => "Closs & Lake (1994)",
-    "primack_1983" => "Primack (1983)",
-    "parker_huryn_2006" => "Parker & Huryn (2006)"
+    #"parker_huryn_2006" => "Parker & Huryn (2006)",         
+    #"ricciardi_2010" => "Ricciardi & MacIsaac (2010)",       # not many species 
+        #"fryer_1959" => "Fryer (1959)",                         # Not usable
+    #"primack_1983" => "Primack (1983)",                     # Only 3 loctations, toss
+    #"ruzicka_2012" => "Ruzicka et al. (2012)",              # This isn't usable
 )
 
 
 
 # I = findall(x->x>5, count.(MangalNetwork, datasets()))
-datanames = collect(keys(sets))
-data = [dataset(d) for d in datanames]
-
-allnets = [networks(d) for d in data]
-
-allnets
-
-nets = [convert.(UnipartiteNetwork, d) for d in allnets]
-
-splist = vcat([i for i in species.(nets[1])]...)
-unique(splist)
+data = Dict([s => dataset(s) for (s,n) in sets])
+allnets = Dict([n=>networks(d) for (n,d) in data])
 
 
-nets[1]
+# Estimate how long htis takes, but it might involve IO? 
+# Just save a BSON is the best option 
+nets = Dict([n=>convert.(UnipartiteNetwork, d) for (n,d) in allnets])
 
[…]

### 2022-09-24 src/mlj_model_comparison.jl

@@ -1,0 +1,113 @@
+using MLJ
+using MLJFlux
+using EcologicalNetworks
+using DataFrames
+using MultivariateStats
+
+include("_computemeasures.jl")
+
+function load_features()
+    # Get the data from the Web of Life database, and merge them into a metaweb M
+    ids = map(i -> i.ID, filter(i -> contains(i.Reference, "Hadfield"), web_of_life()))
+    B = convert.(BipartiteNetwork, web_of_life.(ids))
+    M = reduce(∪, B)
+
+    N = convert(UnipartiteNetwork, M)
+    K = EcologicalNetworks.mirror(N)
+
+    pc = fit(PPCA, Float64.(Array(K.edges)))
+    pr = MultivariateStats.transform(pc, Float64.(Array(K.edges)))
+
+    nf = 15
+
+    cooc = zeros(Bool, prod(size(M)))                  # H/P co-occurrence?
+    labels = zeros(Bool, prod(size(M)))                # H/P interaction?
+    features = zeros(Float64, (2 * nf, prod(size(M))))   # H/P latent traits
+
+    # We then move through the metaweb step by step
+    cursor = 0
+    for i in species(M; dims=1), j in species(M; dims=2)
+        cursor += 1
+        # Interaction in the metaweb?
+        labels[cursor] = M[i, j]
+        # Values in the PCA space
+        p_i = findfirst(i .== species(N))
+        p_j = findfirst(j .== species(N))
+        features[1:nf, cursor] .= pr[1:nf, p_i]
+        features[(nf + 1):end, cursor] .= pr[1:nf, p_j]
+        # Co-occurrence?
+        for b in B
+            if i in species(b)
+                if j in species(b)
+                    cooc[cursor] = true
+                end
+            end
+        end
+    end
+
+    # We only work on the species pairs that DO co-occur
+    kept = findall(cooc)
+    x = Float32.(copy(features[:, kept])) # Latent traits
+    y = labels[kept]     # Interaction bit
+
+    x,y
+end
+
+function feature_dataframe(featuresmatrix, labels)
+    total_nf, nlabels = size(featuresmatrix)
+    nf_per_species = Int32(total_nf/2)
+
+    df = DataFrame(label=labels)
+    for i in 1:nf_per_species
[…]

### 2022-09-25 src/clean_mangal_data.jl
:pencil: word

@@ -5,6 +5,7 @@ using Plots
 using DataFrames
 using CSV
 using BSON
+using StatsBase
 datasets()
 
 
@@ -203,22 +204,129 @@ final_nets
 plot([spy(adjacency(reduce(∪,v)), title=n) for (n,v) in unipartite_nets]..., layout=(2,4), size=(1200, 900))
 
 diffs = Dict()
-for (n,v) in unipartite_nets
+for (n,v) in final_nets
     diff, joints, margs = makejointmargplots(v)
-    @info n, length(diff)
     merge!(diffs, Dict(n=>diff))
 end
-
-diffs["parker_huryn_2006"]
-
-
 
 
 plot([histogram(d, title=n, bins=30) for (n,d) in diffs] ..., layout=(2,4),size=(1200,900))
  
 
+#=
+    Info or write the information for each network 
+=#
+
+# Write diffs 
+
+diffs_df = DataFrame(dataset=[], diff=[])
+for (n,v) in final_nets
+    thesediffs = diffs[n]
+    for d in thesediffs
+    push!(diffs_df.diff, d)
+    push!(diffs_df.dataset,n)
+    end
+end
+
+CSV.write(joinpath("src", "artifacts", "joint_marginal_diffs.csv"), diffs_df)
+
+titles = Dict(
+    #"hawkins_goeden_1984" => "Hawkins & Goeden (1984)",      # not enough samples
+    "kolpelke_et_al_2017" => "Kopelke et al. (2017)",
+    "hadfield_2014" => "Hafield et al (2014)",
+    "havens_1992" => "Havens (1992)", 
+    "ponisio_2017" => "Ponisio et al. (2017)",
+    "RMBL_pollination" => "CaraDonna et al. (2015)",        
+    "closs_1994" => "Closs & Lake (1994)",
+    "nz_stream_foodweb" => "Townsend & Thompson (1995)";
+    #"parker_huryn_2006" => "Parker & Huryn (2006)",         
+    #"ricciardi_2010" => "Ricciardi & MacIsaac (2010)",       # not many species 
+        #"fryer_1959" => "Fryer (1959)",                         # Not usable
+    #"primack_1983" => "Primack (1983)",                     # Only 3 loctations, toss
+    #"ruzicka_2012" => "Ruzicka et al. (2012)",              # This isn't usable
+)
 
 
+
+
+# Beta div
[…]

### 2022-09-25 src/make_fig02.jl

@@ -1,0 +1,101 @@
+using Makie, CairoMakie
+using Distributions
+using ColorSchemes
+using Formatting
+using MathTeXEngine: latexstring
+using Colors
+using DataFrames, CSV
+using HypothesisTests
+using StatsBase
+
+CairoMakie.activate!(; px_per_unit=3)
+
+diffs = CSV.read(joinpath("src", "artifacts", "joint_marginal_diffs.csv"), DataFrame)
+
+metadata = CSV.read(joinpath("src", "artifacts", "metadata.csv"), DataFrame)
+
+titles = Dict(
+    "kolpelke_et_al_2017" => "Kopelke et al. (2017)",
+    "hadfield_2014" => "Hadfield et al. (2014)",
+    "havens_1992" => "Havens (1992)", 
+    "ponisio_2017" => "Ponisio et al. (2017)",
+    "RMBL_pollination" => "CaraDonna et al. (2015)",        
+    "closs_1994" => "Closs & Lake (1994)",
+    "nz_stream_foodweb" => "Townsend & Thompson (1995)";
+)
+ 
+
+typeofnet = Dict(
+    "kolpelke_et_al_2017" => :foodweb,
+    "hadfield_2014" => :hostparasite,
+    "havens_1992" => :foodweb, 
+    "ponisio_2017" => :plantpollinator,
+    "RMBL_pollination" => :plantpollinator,     
+    "closs_1994" => :foodweb,
+    "nz_stream_foodweb" => :foodweb,
+)
+
+
+colmap = Dict(
+    :foodweb=>:steelblue3,
+    :plantpollinator=>:mediumseagreen,
+    :hostparasite=>:mediumpurple4,
+)
+
+
+
+
+fig = Figure(resolution=(1200,600))
+i = 1
+indlist = [(1,1), (1,2), (1,3), (1,4), 
+           (2,1), (2,2), (2,3)]
+
+xpos = [0.0025, 0.000075,0.00035,0.0008, 0.00025, 0.0006,0.0005]
+        
+xticks = [0:0.002:0.004, 0:0.00005:0.0001, 0.0:0.00025:0.0005, 0.0:0.0005:0.001,-0.005:0.0005:0.0005, 0:0.0005:0.001, -0.001:0.001:0.001]
+
+for (n,t) in titles
+    thisdf = filter(r->r.dataset==n,diffs)
[…]

### 2022-09-25 src/mlj_model_comparison.jl

@@ -3,6 +3,7 @@ using MLJFlux
 using EcologicalNetworks
 using DataFrames
 using MultivariateStats
+using Plots
 
 include("_computemeasures.jl")
 
@@ -79,6 +80,39 @@ function split(X, y, prop = 0.8)
     train, test
 end
 
+
+function add_false_negatives(y, Itrain, fnr)
+    y_with_fn = similar(y)
+    y_with_fn = zeros(Bool, length(y))
+
+    for i in Itrain
+        if y[i]==true && rand() < (1-fnr)
+            y_with_fn[i] = 1
+        else
+            y_with_fn[i] = 0
+        end
+    end
+
+    boolvec = [yi == true for yi in y]
+    creal, cobs = sum(boolvec[Itrain])/length(boolvec[Itrain]), sum(y_with_fn[Itrain])/length(y_with_fn[Itrain])
+    @info "Took C=$creal, added FNs to make it C=$cobs"
+    coerce(y_with_fn, Multiclass{2})
+end
+
+function test(model, X, y, Itrain, Itest; fnr=0.1)
+
+    y_with_fn = add_false_negatives(y, Itrain, fnr)
+
+    mach = machine(model, X, y_with_fn)
+    fit!(mach, rows = Itrain)
+    pred = MLJ.predict(mach, rows = Itest)
+    prediction = pred.prob_given_ref[2]
+    obs = Bool.(y[Itest] .== true)
+    prediction, computemeasures(obs, prediction)
+end
+
+
+
 featdf = feature_dataframe(load_features()...)
 
 y, X = unpack(featdf, ==(:label); rng = 123)
@@ -94,9 +128,9 @@ KNN = @load KNNClassifier
 
 
 # Does amount of bagging matter? 
-brt = EnsembleModel(model = Tree(), n = 100)
-rf = EnsembleModel(model = RandomForest(), n = 100)
-dt = EnsembleModel(model = DecisionTree(), n = 100)
+brt = EnsembleModel(model = Tree(), n = 200)
+rf = EnsembleModel(model = RandomForest(), n = 200)
+dt = EnsembleModel(model = DecisionTree(), n = 200)
 ada = EnsembleModel(model = Ada(), n = 100)
 logit = Logistic()
[…]

### 2022-09-25 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@ca8be5724c03133d25e66cdaf98a9186c978d96b 🚀

@@
 
-Community ecology is fundamentaly about understanding species
-interactions. Understanding how species interact underlies many question
-in evolutionary biology, community ecology, and is an increasing
-imperative to mitigate the anthropogoenic change on Earth's biodiversity
+Understanding which and how species interact underlies many questions in
+evolutionary biology and ecology, but also is an increasing imperative
+to both mitigate the anthropogenic change on Earth's biodiversity
 (Jordano 2016a; Makiola \emph{et al.} 2020) and to predict potential
 spillover of zoonotic disease (Becker \emph{et al.} 2021). Over the past
-couple decades biodiversity data has become increasingly
-available---remote-sensing has enabled collection of data on spatial
-scales and resolutions previously unimaginable, and improved in-situ
-sensing (Stephenson 2020) and adoption of open data practices (Kenall
-\emph{et al.} 2014) have substantially amount of data available to
-ecologists. Still, widespread data about species \emph{interactions}
-remains elusive (\textbf{TIM\_DATASET\_PAPER?}). Often, observing an
-interaction between two species requires human sampling, typically
-because remote sampling methods can only detect co-occurrence, and this
-itself is not necessarily indicative of interaction (Blanchet \emph{et
-al.} 2020). This constraint induces biases on species interaction data
-subject to the spatial and temporal scales that humans can feasibly
-sample.
+few decades biodiversity data has become increasingly available:
+remote-sensing has enabled collection of data on spatial scales and
+resolutions previously unimaginable, automation of in-situ sensing
+(Stephenson 2020), and adoption of open data practices (Kenall \emph{et
+al.} 2014) have substantially amount of data available to ecologists.
+Still, widespread data about species \emph{interactions} remains elusive
+(\textbf{TIM\_DATASET\_PAPER?}). Often, observing an interaction between
+two species requires human sampling, typically because remote sampling
+methods can only detect co-occurrence, and this itself is not
+necessarily indicative of interaction (Blanchet \emph{et al.} 2020).
+This constraint induces biases on species interaction data subject to
+the spatial and temporal scales that humans can feasibly sample.
 

### 2022-10-14 src/01_mangal_data.jl
:pencil:

@@ -1,0 +1,416 @@
+using Mangal
+using EcologicalNetworks
+using ProgressMeter
+using Plots
+using DataFrames
+using CSV
+using BSON
+using StatsBase
+using Random
+Random.seed!(42)
+
+sets = Dict(
+    "kolpelke_et_al_2017" => "Kopelke et al. (2017)",
+    "hadfield_2014" => "Hadfield et al (2014)",
+    "havens_1992" => "Havens (1992)", 
+    "ponisio_2017" => "Ponisio et al. (2017)",
+    "RMBL_pollination" => "CaraDonna et al. (2017)",        
+    "closs_1994" => "Closs & Lake (1994)"
+)
+
+
+
+# I = findall(x->x>5, count.(MangalNetwork, datasets()))
+data = Dict([s => dataset(s) for (s,n) in sets])
+allnets = Dict([n=>networks(d) for (n,d) in data])
+
+
+# Estimate how long htis takes, but it might involve IO? 
+# Just save a BSON is the best option 
+nets = Dict([n=>convert.(UnipartiteNetwork, d) for (n,d) in allnets])
+
+
+# HUGE NOTE
+# Each network in RMBL needs to be aggregated before it is used to build the
+# metaweb because they contain sepeare 2-node networks for each interaction 
+# This should be possible by unioning all the interactions, but it might take a while
+
+
+# Convert each list of networks to one with the same taxonomic backbone 
+function convert_taxa(net)
+    name, As = net
+
+    thesenets = []
+
+    namesdf = CSV.read(joinpath("src", "artifacts", "species_translations", "$name.csv"), DataFrame)
+    for (netnum,A) in enumerate(As)
+        spnames = String[]
+        Ind = []
+        thisnet_df = filter(r->r.network_number==netnum, namesdf)            
+
+        num_dropped = length(findall(r-> ismissing(r.DROP) || r.DROP==true, eachrow(thisnet_df)))
+        filter!(r-> ismissing(r.DROP) || r.DROP == false, thisnet_df)
+
+        for (i,r) in enumerate(eachrow(thisnet_df))
+            mang_taxa  = !(ismissing(r.mangal_taxon_name)) ? r.mangal_taxon_name : nothing 
+            mang_species = !(ismissing(r.mangal_species_name)) ? r.mangal_species_name : nothing
+
+            if ismissing(r.DROP) || r.DROP == false
+                i = findall(n -> n.name == mang_species || mang_taxa == (!ismissing(n.taxon) ? n.taxon.name : ""), species(A))
[…]

### 2022-10-14 src/02_simulated_observation.jl

@@ -1,0 +1,134 @@
+using EcologicalNetworks
+using StatsBase: mean, std
+using Distributions: LogNormal, Categorical
+using ColorSchemes, Colors
+using Plots
+using Measures
+using Random
+Random.seed!(42)
+
+include(joinpath("utils", "flexiblelinks.jl"))
+include(joinpath("utils", "all_mangal_networks.jl"))
+
+function observe(numobservations, relativeabundances)
+    counts = zeros(length(relativeabundances))
+    for i in 1:numobservations
+        ind = rand(Categorical(relativeabundances))
+        counts[ind] += 1
+    end
+    return counts
+end
+
+function countfp(A, observations)
+    metaweb = adjacency(A)
+    S = richness(A)
+    tp, fn = 0,0
+    for i in 1:S, j in 1:S
+        if metaweb[i,j] == 1
+            if observations[i] > 0 && observations[j] > 0
+                tp += 1
+            elseif observations[i] > 0 || observations[j] > 0
+                fn += 1
+            end
+        end
+    end
+    return tp, fn
+end
+
+function getabundances(A)
+    S = richness(A)
+    # By trophic levels: 
+    # Z = 2
+    # abundances = Z.^[trophdict["s$i"]-1 for i in 1:S]
+    # abundance_dist = abundances ./ sum(abundances)
+
+    # By lognormal dist:
+    abundances = rand(LogNormal(),S)
+    return  abundances ./ sum(abundances)
+end
+
+function runreplicate(numobservations, A)
+    relativeabundances = getabundances(A)
+    observations = observe(numobservations, relativeabundances)
+    tp, fn = countfp(A, observations)
+
+    fnr = fn/(fn+tp)
+    return fnr
+end
+
+function buildplot(A;  
+    numreplicates = 200,
+    samplingeffort = vcat(1,25, 50:50:1500))
+
+
+    means = zeros(length(samplingeffort))
+    sds = zeros(length(samplingeffort))
+
+    for (s, numobs) in enumerate(samplingeffort)
+        thesefrs = zeros(numreplicates)
+        for r in 1:numreplicates
+            # sample metaweb if as is a function for generating,
+            # otherwise it is an empirical web so just use it 
[…]

### 2022-10-14 src/03_prediction_comparison.jl

@@ -1,0 +1,226 @@
+using MLJ
+using MLJFlux
+using EcologicalNetworks
+using DataFrames
+using MultivariateStats
+using Plots
+using Random
+Random.seed!(42)
+
+include(joinpath("utils", "confusionmatrix.jl"))
+
+function load_features()
+    # Get the data from the Web of Life database, and merge them into a metaweb M
+    ids = map(i -> i.ID, filter(i -> contains(i.Reference, "Hadfield"), web_of_life()))
+    B = convert.(BipartiteNetwork, web_of_life.(ids))
+    M = reduce(∪, B)
+
+    N = convert(UnipartiteNetwork, M)
+    K = EcologicalNetworks.mirror(N)
+
+    pc = fit(PPCA, Float64.(Array(K.edges)))
+    pr = MultivariateStats.transform(pc, Float64.(Array(K.edges)))
+
+    nf = 15
+
+    cooc = zeros(Bool, prod(size(M)))                  # H/P co-occurrence?
+    labels = zeros(Bool, prod(size(M)))                # H/P interaction?
+    features = zeros(Float64, (2 * nf, prod(size(M))))   # H/P latent traits
+
+    # We then move through the metaweb step by step
+    cursor = 0
+    for i in species(M; dims=1), j in species(M; dims=2)
+        cursor += 1
+        # Interaction in the metaweb?
+        labels[cursor] = M[i, j]
+        # Values in the PCA space
+        p_i = findfirst(i .== species(N))
+        p_j = findfirst(j .== species(N))
+        features[1:nf, cursor] .= pr[1:nf, p_i]
+        features[(nf + 1):end, cursor] .= pr[1:nf, p_j]
+        # Co-occurrence?
+        for b in B
+            if i in species(b)
+                if j in species(b)
+                    cooc[cursor] = true
+                end
+            end
+        end
+    end
+
+    # We only work on the species pairs that DO co-occur
+    kept = findall(cooc)
+    x = Float32.(copy(features[:, kept])) # Latent traits
+    y = labels[kept]     # Interaction bit
+
[…]

### 2022-10-14 src/04_trophic_levels.jl

@@ -1,0 +1,141 @@
+using Makie, CairoMakie
+using EcologicalNetworks
+using StatsBase
+using Statistics: std
+using ProgressMeter
+using DataFrames
+using Colors
+using CSV
+using Random
+Random.seed!(42)
+
+include("flexiblelinks.jl")
+
+function add_falsenegatives(truenetwork, p_fn)
+    mat = adjacency(truenetwork)
+    for (i,el) in enumerate(mat)
+        if el == 1 && rand() < p_fn
+            mat[i] = 0 
+        elseif el == 1 
+            mat[i] = 1
+        end
+    end
+    return size(truenetwork,1) == size(truenetwork,2) ? UnipartiteNetwork(mat) : BipartiteNetwork(mat)
+end
+
+function make_perfect_nested(T,B)
+    mat = zeros(Bool, T, B)
+    
+    for i in 1:T
+        for j in 1:B
+            if i > j
+                mat[i,j] = 1
+            end 
+        end
+    end
+    BipartiteNetwork(mat)
+end 
+
+
+S = 150
+nreps = 50
+
+trophic_means, trophic_vars = Float32[], Float32[]
+fnrs = Float32[]
+
+df = DataFrame(trophic_means=Float32[], 
+    trophic_vars=Float32[], index=[], fnr=Float32[], numspecies=Float32[])
+
+NS = [100, 250, 500, 1000]
+for ns in NS
+    @info ns
+    truenetwork = flexiblelinksmodel(ns)
+    for (ind,p_fn) in enumerate(0:0.05:1)
+        for i in 1:50
+            observednet = add_falsenegatives(truenetwork, p_fn)
+            vals = collect(values(trophic_level(observednet)))
+            push!(df.fnr,p_fn )
+            push!(df.trophic_means, mean(vals))
+            push!(df.trophic_vars, var(vals))
+            push!(df.numspecies, ns)
+            push!(df.index, ind)
+        end 
+    end 
+end 
+
+fig = Figure(resolution=(700,700))
+
+ax1 = Axis(fig[1,1], 
+    xticks=0:0.1:1,
+    xlabel="Added FNR",
+    ylabel="Mean trophic level",
+    xminorgridvisible=true,
+    xminorticks=0:0.05:1,
+    yminorticksvisible=true,
+    yminorticks=0:0.5:1,
+    xlabelsize=22,
+    ylabelsize=22,
+)
[…]

### 2022-10-14 src/SUPP_network_properties.jl

@@ -1,75 +1,0 @@
-using Plots
-using EcologicalNetworks
-using StatsBase
-using Statistics: std
-
-include("_common.jl")
-
-function add_falsenegatives(truenetwork, p_fn)
-    mat = adjacency(truenetwork)
-    for (i,el) in enumerate(mat)
-        if el == 1 && rand() < p_fn
-            mat[i] = 0 
-        elseif el == 0 && rand() < p_fn
-            mat[i] = 1
-        end
-    end
-    return UnipartiteNetwork(mat)
-end
-
-function errors(f;
-    S = 100,
-    fnr = 0:0.02:1,
-    nreps= 30
-)
-
-    err = zeros(length(fnr))
-    sd_err = zeros(length(fnr))
-    for (fni,p_fn) in enumerate(fnr)
-        errorlist = zeros(nreps)
-
-        for rep in 1:nreps
-
-            truenetwork = flexiblelinksmodel(S)
-            observednet = add_falsenegatives(truenetwork, p_fn)
-
-            errorlist[rep] = sqrt((f(truenetwork) - f(observednet) )^2)
-        end
-        err[fni] = mean(filter(x -> !isnan(x), errorlist))
-        sd_err[fni] = std(filter(x -> !isnan(x), errorlist))
-    end
-
-    return fnr, err, sd_err
-end
-
-meandegcent(x) = mean(collect(values(centrality_degree(x))))
-meankatzcent(x) = mean(collect(values(centrality_katz(x))))
-meanclosenessctr(x) = mean(collect(values(centrality_closeness(x))))
-
-fnr, connect_err, connect_sd = errors(connectance, nreps=2000)
-fnr, degcent_err, degcent_sd = errors(meandegcent, nreps=2000)
-
-fnr, specrad_err, specrad_sd = errors(ρ, nreps=300) 
-
-
-fnt = font(20, "Roboto")
-
-plot(dpi=300, fontfamily=fnt, size=(500,500), frame=:box, ylim=(0,1),xlim=(0,1))
-plot!(fnr, connect_err, label="", ribbon=connect_sd, c=:dodgerblue4, fa=0.2, )
-plot!(fnr, connect_err, label="", ribbon=2connect_sd, c=:dodgerblue4, fa=0.1)
-scatter!(fnr, connect_err, mc=:white, msc=:dodgerblue4, msw=1.5, ms=4,label="connectance")
-
[…]

### 2022-10-14 src/_possible_new_1b.jl

@@ -1,0 +1,43 @@
+using CairoMakie, Distributions
+using MathTeXEngine
+using MathTeXEngine: latexstring
+CairoMakie.activate!(; px_per_unit=2)
+
+
+p_a = 0.01:0.01:0.5
+p_b = 0.01:0.01:0.5
+
+
+exp_obs = zeros(length(p_a), length(p_b))
+
+expectednumobs(target_negatives, p_a, p_b) = target_negatives/(p_a*p_b)
+
+
+# p_a = 0.1, p_b = 0.2
+# how many of all species to see this pair 5 times?
+# 0.1  *  0.2
+
+# to see A and B once, you need an expected 1/(p_a*p_b) exp_obs
+
+targ = 10
+for I in CartesianIndices(size(exp_obs))
+    exp_obs[I] = expectednumobs(targ, p_a[I[1]], p_a[I[2]])
+end
+
+function maketicks(x)
+    latexstring.(["10^{$(i)}" for i in x])
+end
+
+fig = Figure(resolution=(800,700))
+ax = Axis(fig[1,1], xlabel=L"P(A)", ylabel=L"P(B)", xlabelsize=22,
+ylabelsize=22)
+limits!(ax,0.01,0.5,0.01,0.5)
+co = contourf!(ax, p_a, p_b, log10.(exp_obs), colorlimits=1:5, levels=range(1,5, length = 10))
+Colorbar(fig[1,2], co, ticksize=20, label="Expected number of observations of all individuals to see A and B together 10 times",ticks=[i for i in 1:0.5:5], tickformat=maketicks)
+
+
+
+
+fig
+
+fig |> save("new_1b.png")

### 2022-10-14 src/clean_mangal_data.jl

@@ -1,446 +1,0 @@
-using Mangal
-using EcologicalNetworks
-using ProgressMeter
-using Plots
-using DataFrames
-using CSV
-using BSON
-using StatsBase
-datasets()
-
-
-sets = Dict(
-    #"hawkins_goeden_1984" => "Hawkins & Goeden (1984)",      # not enough samples
-    "kolpelke_et_al_2017" => "Kopelke et al. (2017)",
-    "hadfield_2014" => "Hafield et al (2014)",
-    "havens_1992" => "Havens (1992)", 
-    "ponisio_2017" => "Ponisio et al. (2017)",
-    "RMBL_pollination" => "CaraDonna et al. (2015)",        
-    "closs_1994" => "Closs & Lake (1994)",
-    #"parker_huryn_2006" => "Parker & Huryn (2006)",         
-    #"ricciardi_2010" => "Ricciardi & MacIsaac (2010)",       # not many species 
-        #"fryer_1959" => "Fryer (1959)",                         # Not usable
-    #"primack_1983" => "Primack (1983)",                     # Only 3 loctations, toss
-    #"ruzicka_2012" => "Ruzicka et al. (2012)",              # This isn't usable
-)
-
-
-
-# I = findall(x->x>5, count.(MangalNetwork, datasets()))
-data = Dict([s => dataset(s) for (s,n) in sets])
-allnets = Dict([n=>networks(d) for (n,d) in data])
-
-
-# Estimate how long htis takes, but it might involve IO? 
-# Just save a BSON is the best option 
-nets = Dict([n=>convert.(UnipartiteNetwork, d) for (n,d) in allnets])
-
-bson("mangal_networks.bson")
-
-
-# HUGE NOTE
-# Each network in RMBL needs to be aggregated before it is used to build the
-# metaweb because they contain sepeare 2-node networks for each interaction 
-# This should be possible by unioning all the interactions, but it might take a while
-
-
-# Convert each list of networks to one with the same taxonomic backbone 
-function convert_taxa(net)
-    name, As = net
-
-    thesenets = []
-
-    namesdf = CSV.read(joinpath("src", "artifacts", "species_translations", "$name.csv"), DataFrame)
-    for (netnum,A) in enumerate(As)
-        spnames = String[]
-        Ind = []
-        thisnet_df = filter(r->r.network_number==netnum, namesdf)            
-
-        num_dropped = length(findall(r-> ismissing(r.DROP) || r.DROP==true, eachrow(thisnet_df)))
[…]

### 2022-10-14 src/generate_simulated_observation_data.jl

@@ -1,242 +1,0 @@
-include("_common.jl")
-using EcologicalNetworks
-include("get_mangal_data.jl")
-
-using StatsBase: mean, std
-using Distributions: LogNormal, Categorical
-using ColorSchemes, Colors
-using Plots
-using Measures
-
-function observe(numobservations, relativeabundances)
-    counts = zeros(length(relativeabundances))
-    for i in 1:numobservations
-        ind = rand(Categorical(relativeabundances))
-        counts[ind] += 1
-    end
-    return counts
-end
-
-function countfp(A, observations)
-    metaweb = adjacency(A)
-    S = richness(A)
-    tp, fn = 0,0
-    for i in 1:S, j in 1:S
-        if metaweb[i,j] == 1
-            if observations[i] > 0 && observations[j] > 0
-                tp += 1
-            elseif observations[i] > 0 || observations[j] > 0
-                fn += 1
-            end
-        end
-    end
-    return tp, fn
-end
-
-function getabundances(A)
-    S = richness(A)
-    # By trophic levels: 
-    # Z = 2
-    # abundances = Z.^[trophdict["s$i"]-1 for i in 1:S]
-    # abundance_dist = abundances ./ sum(abundances)
-
-    # By lognormal dist:
-    abundances = rand(LogNormal(),S)
-    return  abundances ./ sum(abundances)
-end
-
-function runreplicate(numobservations, A)
-    relativeabundances = getabundances(A)
-    observations = observe(numobservations, relativeabundances)
-    tp, fn = countfp(A, observations)
-
-    fnr = fn/(fn+tp)
-    return fnr
-end
-
-function buildplot(A;  
-    numreplicates = 200,
-    samplingeffort = vcat(1,25, 50:50:1500))
-
-
-    means = zeros(length(samplingeffort))
-    sds = zeros(length(samplingeffort))
-
-    for (s, numobs) in enumerate(samplingeffort)
-        thesefrs = zeros(numreplicates)
-        for r in 1:numreplicates
-            # sample metaweb if as is a function for generating,
-            # otherwise it is an empirical web so just use it 
[…]

### 2022-10-14 src/make_fig01.jl

@@ -62,44 +62,58 @@ end
 gb = GridLayout(f[1,2])
 
 ax2 = Axis(gb[1,1],
-    xticks=0:0.1:1,
-    yticks=[10^i for i in 0:7],
+    xticks=0:0.1:0.5,
     xminorticks = 0:0.05:0.5,
+    yticks=0:0.1:0.5,
+    yminorticks = 0:0.05:0.5,
     xminorticksvisible = true,
     xminorgridvisible = true,
-    ytickformat=maketex,
-    xlabel="Relative abundance of particular species",
-    ylabel="Expected number of observations of all species",
-    yscale=log10,
+    xlabel=L"P(A)",
+    ylabel=L"P(B)",
     xlabelsize=22,
     ylabelsize=22,
     yticksize=28)
 
-limits!(ax2, 0, 0.5, 1, 10^7)
-function expected_samples(numobs)
-    relativeabund = Float64[]
-    obs = Float64[]
-    for relabd in vcat(0.001:0.001:0.5)
-        push!(relativeabund, relabd)
-        push!(obs, numobs/relabd)
-    end
-    relativeabund, obs
+
+p_a = 0.01:0.01:0.5
+p_b = 0.01:0.01:0.5
+expectednumobs(target_negatives, p_a, p_b) = target_negatives/(p_a*p_b)
+exp_obs = zeros(length(p_a), length(p_b))
+targ = 10
+for I in CartesianIndices(size(exp_obs))
+    exp_obs[I] = expectednumobs(targ, p_a[I[1]], p_a[I[2]])
 end
 
-for (i,numobs) in enumerate([1,10,100,1000,10000])
-    relabd, req = expected_samples(numobs)
-    lines!(ax2,relabd, req,
-        strokewidth = 2,
-        linewidth = 4,
-        markersize = 12, 
-        color = ColorSchemes.tableau_sunset_sunrise[i],
-        strokecolor = ColorSchemes.tableau_sunset_sunrise[i], 
-    #    markercolor = :white,
-        label="$numobs"
-    )
-
+function maketicks_1b(x)
+    latexstring.(["10^{$(i)}" for i in x])
 end
-axislegend("Target obs. of particular species",orientation = :horizontal, position=:rt)
+
+
+cmap_1b = parse.(Colorant, [
+    "#fa6d3f",
[…]

### 2022-10-14 src/make_fig02.jl

@@ -19,9 +19,9 @@ titles = Dict(
     "hadfield_2014" => "Hadfield et al. (2014)",
     "havens_1992" => "Havens (1992)", 
     "ponisio_2017" => "Ponisio et al. (2017)",
-    "RMBL_pollination" => "CaraDonna et al. (2015)",        
+    "RMBL_pollination" => "CaraDonna et al. (2017)",        
     "closs_1994" => "Closs & Lake (1994)",
-    "nz_stream_foodweb" => "Townsend & Thompson (1995)";
+    "nz_stream_foodweb" => "Townsend & Thompson (2000)";
 )
  
 
@@ -98,4 +98,4 @@ Legend(fig[2,4], width=220, [fw,pp,hp], ["Food Web", "Plant-Pollinator", "Host-P
 
 fig
 
-fig |> save("fig3.png")
+fig |> save(joinpath("figures","fig2.png"))

### 2022-10-14 src/make_fig03.jl

@@ -1,0 +1,236 @@
+using Makie, CairoMakie
+using DataFrames
+using Colors
+using StatsBase
+using CSV
+
+CairoMakie.activate!(; px_per_unit=2)
+
+model_data = CSV.read(joinpath("src", "artifacts", "model_comparison.csv"), DataFrame)
+trophic_data = CSV.read(joinpath("src", "artifacts", "trophic_levels.csv"), DataFrame)
+
+fig = Figure(resolution=(900,900))
+ga = GridLayout(fig[1,1])
+
+ax1 = Axis(ga[1,1],
+    xticks=0:0.1:1,
+    yticks=0:0.1:1,
+    xminorticks=0:0.05:1,
+    xminorgridvisible=true,
+    xminorticksvisible=true,
+    yminorticks=0:0.05:1,
+    yminorgridvisible=true,
+    yminorticksvisible=true,
+    xlabel="Added FNR",
+    ylabel="ROC-AUC",
+    xlabelsize=22,
+    ylabelsize=22
+)
+limits!(ax1, 0, 0.95, 0,1)
+
+
+grey, red, orange, green = ([colorant"grey35", colorant"red", colorant"orange", colorant"green"])
+
+addalpha(x,alpha) = RGBA(x.r,x.g,x.b, alpha)
+
+grey, red, orange, green = addalpha.([grey, red, orange, green], 0.3) 
+
+poly!(ax1, 
+    Rect(0, 0, 1.0, 0.5),
+    color = (:grey, 0.3),
+    transparency = true
+)
+text!(ax1, 0.63, 0.46, text="Worse than random", textsize=12, justification=:center)
+
+
+poly!(ax1, 
+    Rect(0, 0.5, 1.0, 0.25),
+    color = red,
+    transparency = true
+)
+text!(ax1, 0.68, 0.52, color=:firebrick, textsize=12, text="Close to random")
+
+poly!(ax1, 
+    Rect(0, 0.75, 1.0, 0.15),
+    color = orange,
+    transparency = true
+)
+text!(ax1, 0.72, 0.85, color=:salmon2, textsize=12, text="Fair Classifier")
+
+poly!(ax1, 
+    Rect(0, 0.9, 1.0, 0.1),
+    color = green,
+    transparency = true
+)
+text!(ax1, 0.65, 0.94, color=:darkgreen, textsize=12, text="Excellent Classifier")
+
+models = unique(model_data.model)
+
+colors = Colors.JULIA_LOGO_COLORS
[…]

### 2022-10-14 src/mlj_model_comparison.jl

@@ -1,222 +1,0 @@
-using MLJ
-using MLJFlux
-using EcologicalNetworks
-using DataFrames
-using MultivariateStats
-using Plots
-
-include("_computemeasures.jl")
-
-function load_features()
-    # Get the data from the Web of Life database, and merge them into a metaweb M
-    ids = map(i -> i.ID, filter(i -> contains(i.Reference, "Hadfield"), web_of_life()))
-    B = convert.(BipartiteNetwork, web_of_life.(ids))
-    M = reduce(∪, B)
-
-    N = convert(UnipartiteNetwork, M)
-    K = EcologicalNetworks.mirror(N)
-
-    pc = fit(PPCA, Float64.(Array(K.edges)))
-    pr = MultivariateStats.transform(pc, Float64.(Array(K.edges)))
-
-    nf = 15
-
-    cooc = zeros(Bool, prod(size(M)))                  # H/P co-occurrence?
-    labels = zeros(Bool, prod(size(M)))                # H/P interaction?
-    features = zeros(Float64, (2 * nf, prod(size(M))))   # H/P latent traits
-
-    # We then move through the metaweb step by step
-    cursor = 0
-    for i in species(M; dims=1), j in species(M; dims=2)
-        cursor += 1
-        # Interaction in the metaweb?
-        labels[cursor] = M[i, j]
-        # Values in the PCA space
-        p_i = findfirst(i .== species(N))
-        p_j = findfirst(j .== species(N))
-        features[1:nf, cursor] .= pr[1:nf, p_i]
-        features[(nf + 1):end, cursor] .= pr[1:nf, p_j]
-        # Co-occurrence?
-        for b in B
-            if i in species(b)
-                if j in species(b)
-                    cooc[cursor] = true
-                end
-            end
-        end
-    end
-
-    # We only work on the species pairs that DO co-occur
-    kept = findall(cooc)
-    x = Float32.(copy(features[:, kept])) # Latent traits
-    y = labels[kept]     # Interaction bit
-
-    x,y
-end
-
[…]

### 2022-10-14 src/utils/all_mangal_networks.jl

@@ -1,0 +1,157 @@
+"""
+    This code is primanry adapted from 
+    https://github.com/PoisotLab/JuliaEcoNetworksValuePack/blob/v0.0.1/paper/main.jl
+    in order to query Mangal and save id's of networks based on network type 
+    (foodweb,parasitism,mutalism,misc) in files in the artifacts directory.  
+"""
+
+
+using Mangal
+using DataFrames
+using ProgressMeter
+using SparseArrays
+using CSV
+
+mangal_networks = nothing 
+
+
+function querymangal()
+    global mangal_networks
+
+    if isnothing(mangal_networks)
+        numnetworks = count(MangalNetwork)
+        mangal_networks = DataFrame(zeros(Int32, numnetworks,7), [:id, :S, :L, :pred, :herb, :mutu, :para])
+        
+        count_per_page = 100
+        number_of_pages = convert(Int, ceil(numnetworks/count_per_page))
+        cursor = 1
+        @showprogress for page in 1:number_of_pages
+            networks_in_page = Mangal.networks("count" => count_per_page, "page" => page-1)
+            for current_network in networks_in_page
+                S = count(MangalNode, current_network)
+                L = count(MangalInteraction, current_network)
+                pred = count(MangalInteraction, current_network, "type" => "predation")
+                herb = count(MangalInteraction, current_network, "type" => "herbivory")
+                mutu = count(MangalInteraction, current_network, "type" => "mutualism")
+                para = count(MangalInteraction, current_network, "type" => "parasitism")
+                mangal_networks[cursor,:] .= (current_network.id, S, L, pred, herb, mutu, para)
+                cursor = cursor + 1
+            end
+        end
+    end
+    CSV.write(joinpath("src", "artifacts", "allmangal", "mangal.csv"), mangal_networks)
+
+    # remove networks with less than 5 links
+    mangal_networks2 = mangal_networks[mangal_networks.L .> 4, :]
+
+    # number of interactions in food webs (sum of predation and herbivory interactions)
+    mangal_networks.foodweb = mangal_networks.pred .+ mangal_networks.herb
+
+    # number of other types of interactions
[…]

### 2022-10-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@230beaa0261730b22ad4cadb32c74b1331cb84d4 🚀

@@
 
-Understanding which and how species interact underlies many questions in
-evolutionary biology and ecology, but also is an increasing imperative
-to both mitigate the anthropogenic change on Earth's biodiversity
-(Jordano 2016a; Makiola \emph{et al.} 2020) and to predict potential
-spillover of zoonotic disease (Becker \emph{et al.} 2021). Over the past
-few decades biodiversity data has become increasingly available:
-remote-sensing has enabled collection of data on spatial scales and
-resolutions previously unimaginable, automation of in-situ sensing
-(Stephenson 2020), and adoption of open data practices (Kenall \emph{et
-al.} 2014) have substantially amount of data available to ecologists.
-Still, widespread data about species \emph{interactions} remains elusive
-(\textbf{TIM\_DATASET\_PAPER?}). Often, observing an interaction between
-two species requires human sampling, typically because remote sampling
-methods can only detect co-occurrence, and this itself is not
-necessarily indicative of interaction (Blanchet \emph{et al.} 2020).
-This constraint induces biases on species interaction data subject to
-the spatial and temporal scales that humans can feasibly sample.
-
-\emph{Sampling effort} and its impact on the resulting data collected
-from ecosystems has encouraged a long history of discourse. The recorded
-number of species in a sample depends on the total number of
-observations (Walther \emph{et al.} 1995; Willott 2001), as do estimates
-of population abundance (Griffiths 1998). This has motivated more
+Species interactions drive many processes in evolutionary biology and
+community ecology. A better understanding of interactions among species
+is an imperative to both mitigate the potentially harmful impacts of
+anthropogenic change on Earth's biodiversity (Makiola \emph{et al.}
+2020) and to predict zoonotic spillover of disease to prevent future
+pandemics (Becker \emph{et al.} 2021). However, meeting these challenges
+is difficult because interactions are intrinsically hard to sample
+(Jordano 2016). Over the past few decades biodiversity data has become
+increasingly available--for example, remote-sensing has enabled
+collection of data on spatial scales and resolutions previously
+unimaginable, and improved in-situ sensing (Stephenson 2020), while the
+adoption of open data practices (Kenall \emph{et al.} 2014) have
+substantially increased the amount of data available to ecologists.
+Still, widespread data about species interactions remains elusive
+(Poisot \emph{et al.} 2021). Observing an interaction between two
+species often requires human observation because remote sampling methods
+can primarily detect co-occurrence (Niedballa \emph{et al.} 2019), and
+this itself is not necessarily indicative of an interaction (Blanchet
+\emph{et al.} 2020). This constraint induces biases on species
+interaction data subject to the spatial and temporal scales that current
+observation methods can feasibly sample. This is further compounded by
+semantic confusion around the word ``interaction''---for example one
+could consider competition a form of species interaction, even though
+this is marked by a lack of co-occurrence between species, unlike other
+types of interactions, like trophism or pollination, which require both
+species to be together at the same place and time. Here we define
+interaction in the latter sense, where two species have fitness
+consequences on one-another if they are in the sample place at the same
+time. Further we only consider direct (not higher-order) interactions.
+
+The importance of sampling effort and its impact on resulting ecological
+data has produced a rich body of literature. The recorded number of
+species in a dataset or sample depends on the total number of
+observations (Walther \emph{et al.} 1995; Willott 2001)---as do
+estimates of population abundance (Griffiths 1998)---in addition to
+spatial coverage and species detectability. This has motivated more
 quantitatively robust approaches to account for error in sampling data
@@
 \emph{et al.} 2015), to determine sampling design (Moore \& McCarthy
-2016), and to measure species richness across large scales (Carlson
-\emph{et al.} 2020). In the context of interactions, the initial concern
+2016),and to measure species richness across large scales (Carlson
+\emph{et al.} 2020). In the context of interactions, an initial concern
 was the compounding effects of limited sampling effort combined with the
-amalgamation of data (across both study sites and across taxonomic
-scales) could lead any empirical set of observations to inadequately
-reflect the reality of how species interact (Paine 1988). Martinez
-\emph{et al.} (1999) showed that in a plant-endophyte trophic network,
-network connectance is robust to sampling effort, but this done in the
-context of a system for which observation of 62,000 total interactions
-derived from 164,000 plant-stems was feasible. In some systems
-(e.g.~megafauna food-webs) this many observations is either impractical
-or infeasible due to the absolute abundance of the species in question.
-
-Because we cannot feasibly observe all (or even many) of the
-interactions that occur in nature, our samples end up capturing only a
-small fraction of those interactions. This means we can be reasonably
-confident two species actually interact if we have a record of it, but
-not at all confident that two species \emph{do not} interact if we have
-no record of those species observed together. In other words, it is
-difficult to distinguish true-negatives (two species \emph{never}
-interact) from \emph{false-negatives} (two species interact in some
-capacity, but we have not observed it). This is then amplified as the
-interaction data we have is geographically toward the usual suspects
-(Poisot \emph{et al.} 2021a), This noise in data has practical
-consequences for answering questions about species interactions (de
-Aguiar \emph{et al.} 2019)---these false-negatives could go on to effect
-the inferences we make about network properties and relations among
-species, and our predictions about how species will interact in the
-future.
-
-This is compounded by semantic confusion about the definition of
-``interaction''. Here distinguish between: a species \emph{occurring}, a
-species being \emph{observed occurring}, two species being observed
-\emph{co-occurring}, and two species being observed \emph{interacting}
-(fig.~\ref{fig:taxonomy}). In this manuscript, we refer to species
-either as ``interacting''---two species co-occur (and, at least
-sometimes, interact)---or ``not-interacting'' (two species that,
-regardless of whether they co-occur, neither exhibits any meaningful
-effect on the biomass of the other). In fig.~\ref{fig:taxonomy} we see
-that, under our definition, observing two species co-occurring is a
-prerequisite for observing an interaction between two species.
-
-But species are not observed with equal probability but instead in
-proportion to their relative biomass---you are much more likely to
-observe a species of high relative abundance than one of very low
-relative abundance (Poisot \emph{et al.} 2015). This assumes that there
-are no associations in species co-occurrence due to an interaction
-(perhaps because this interaction is ``important'' for both species)
-(Cazelles \emph{et al.} 2016), but here we show increasing strength of
+amalgamation of data (across both study sites, time of year, and
+taxonomic scales) could lead any empirical set of observations to
+inadequately reflect the reality of how species interact
+{[}Paine1988RoaMap{]} or the structure of the network as a whole
+{[}McLeod2021SamAsy{]}. Martinez \emph{et al.} (1999) showed that in a
+plant-endophyte trophic network, network connectance is robust to
+sampling effort, but this was done in the context of a system for which
+observation of 62,000 total interactions derived from 164,000
+plant-stems was feasible. In some systems (e.g.~megafauna food-webs)
+this many observations is either impractical or infeasible due to the
+absolute abundance of the species in question.
+
+We cannot feasibly observe all (or even most) of the direct interactions
+that occur in an ecosystem. This means we can be confident two species
+actually interact if we have a record of it (given an estimate of
+species misidentification probability), but not at all confident that a
+pair of species do not interact if we have no record of those species
+observed together. In other words, it is difficult to distinguish
+true-negatives (two species never interact) from false-negatives (two
+species interact in some capacity, but we do not have a record of it).
+For a concrete example of this phenomenon, see Figure Concept. Because
+even the most highly sampled systems will still contain missing
+interactions, there is increasing interest in combining species-level
+data (e.g. traits, abundance, range, phylogenetic relatedness, etc.) to
+build predictive models of interactions (Strydom \emph{et al.} 2021).
+However, the noise of false-negatives could impact the efficacy of our
+predictive models and have practical consequences for answering
+questions about interactions (de Aguiar \emph{et al.} 2019). This data
+constraint is amplified as the interaction data we have is
+geographically biased toward the usual suspects (Poisot \emph{et al.}
+2021). We therefore need a systematic approach to assessing these biases
+in the observation process and the consequences this has for our
+understanding of interaction networks
+
+The intrinsic properties of ecological communities create several
+challenges for sampling: first, species are not observed with equal
+probability---we are much more likely to observe a species of high
+abundance than one of very low abundance (Poisot \emph{et al.} 2015).
+Canard \emph{et al.} (2012) presents a null model of food-web structure
+where species encounter one-another directly in proportion to each
+species' relative-abundance. This assumes that there are no associations
+in species co-occurrence due to an interaction (perhaps because this
+interaction is ``important'' for both species; Cazelles \emph{et al.}
+(2016)), but in this paper we later show increasing strength of
 associations leads to increasing probability of false-negatives in
-interaction data. Further observed co-occurrence is often equated with
-meaningful interaction strength, but this is not necessarily the case
-(Blanchet \emph{et al.} 2020; Strydom \emph{et al.} 2021). Bears and
-salmon \emph{interact}---a bear and the microbes in the soil of a dens
-interact, but less so.
-
-Here, we show that the probability of observing a actual
-``non-interaction'' between species depends on sampling effort, and
-suggest that surveys of species interactions can benefit from simulation
-modeling of detection probability (Jordano 2016b). We demonstrate that
-the realized false-negative rate of interactions is directly related the
-relative abundance of a particular species, relationship between total
-sampling effort (the total count of all individuals of all species seen)
-and false-negative rate. questions we pose and attempt to answer are: 1)
-How many times do you have to observe a non-interaction between two
-species to be confident in saying that is a true negative? 2) How
-``wrong'' are the measurements of network structure as a function of
-false-negative probability? and lastly 3) How do false-negatives impact
-our ability to make reliable predictions about interactions? We show
-that positive associations in co-occurrence data can increase realized
-probability of false negatives, and demonstrate these positive
-associations are present in two spatially-replicated systems. We
-conclude by suggesting that simulation of sampling effort and species
+interaction data, and that these positive associations are rampant in
+existing network data. Second, observed co-occurrence is often equated
+with meaningful interaction strength, but this is not necessarily the
+case Blanchet \emph{et al.} (2020)---a true ``non-interaction'' would
+require that neither of two species, regardless of whether they
+co-occur, exhibit any meaningful effect on the fitness of the other. So,
+although co-occurrence is not directly indicative of an interaction, it
+is a precondition for interactions, and therefore observations of
+``non-interactions'' between pairs of species that are outside of the
+union of both species ranges do not provide any information about that
+interaction, i.e.~they should be excluded from consideration.
+
+Here, we illustrate how our confidence that a pair of species we believe
+to not interact highly depends on sampling effort, and suggest that
+surveys of species interactions can benefit from simulation modeling of
+detection probability. We demonstrate that the realized false-negative
+rate of interactions is directly related to the relative abundance of
+the species involved, and demonstrate how simulation can be used to
+produce a null estimate of the false-negative rate as a function of
+total sampling effort (the total count of all individuals of all species
+seen). We show that positive associations in co-occurrence data can
+increase realized probability of false negatives, and demonstrate these
+positive associations are ubiquitous in network datasets. We conclude by
+recommending that the simulation of sampling effort and species
 occurrence can and should be used to help design surveys of species
-diversity (Moore \& McCarthy 2016), and by advocating use of null models
-like those presented here as a tool for guiding design of surveys of
-species interactions, and for modeling detection error in predictive
-ecological models.
-
-\hypertarget{how-many-observations-of-a-non-interaction-do-we-need-to-classify-it-as-a-true-negative}{%
-\section{How many observations of a non-interaction do we need to
-classify it as a true
-negative?}\label{how-many-observations-of-a-non-interaction-do-we-need-to-classify-it-as-a-true-negative}}
-
-To answer the titular question of this section, we present a naive model
-of interaction detection: we assume that every interacting pair of
-species is incorrectly observed as a not-interacting with an independent
-and fixed probability, which we denote \(p_{fn}\) and subsequently refer
-to as the False-Negative Rate (FNR). If we observe the same species
-not-interacting \(N\) times, then the probability of a true-negative
-(denoted \(p_{tn}\)) is given by \(p_{tn} = 1 - (p_{fn})^N\). This
-relation (callend the geometric distribution, a special case of the
-negative-binomial distribution) is shown in fig.~\ref{fig:negativebinom}
-for varying values of the false negative rate \(p_{fn}\). This
-illustrates a fundamental link between our ability to reliably say an
-interaction doesn't exist---\(p_{tn}\)---and the number of times we have
-observed a given species. In addition, note that there also is no
-non-zero \(p_{fn}\) for which we can ever \emph{prove} that an
-interaction does not exist---no matter how many observations of
-non-interaction \(N\) we have, \(p_{tn} < 1\).
-
-From fig.~\ref{fig:fig1} (A) (and general intuition) it is clear that
-the more times we see two species \emph{occurring}, but \emph{not}
-interacting, the more likely the interaction is a true negative. But how
-does one decide what this threshold of number of observations should be
-when planning to sample a given system? If false-negative rates
-presented in fig.~\ref{fig:fig1} seem unrealistically high, consider
-that species are not observed independent of their relative abundance.
-In the next section we demonstrate that distribution of abundance in
-ecosystems can lead to realized values of \(p_{fn}\) similar to those in
-fig.~\ref{fig:negativebinom} for species with low relative abundance,
-simply as a artifact of sampling effort.
-
-\hypertarget{false-negatives-as-a-product-of-relative-abundance}{%
-\subsection{False-negatives as a product of relative
-abundance}\label{false-negatives-as-a-product-of-relative-abundance}}
-
-Here we show the realized false-negative rate of species interactions
-changes drastically with sampling effort, largely due to the intrinsic
-variation of abundances within a community. We do this by simulating the
-process of observation of species interactions, applied both to 243
-empirical food webs from the Mangal database (Banville \emph{et al.}
-2021) as well as random food-webs generated using the niche model
-(Williams \& Martinez 2000). Our neutral model of observation assumes
-each observed species is drawn from the distribution of those species'
-abundances at that place and time. Although there is no shortage of
-debate as to the processes the govern this distribution of abundances
-within a community, this abundance distribution can be reasonably-well
-described by a log-normal distribution (Volkov \emph{et al.} 2003) (Note
-that in addition to the log-normal distribution, we also tested the case
-where the abundance distribution is derived from power-law scaling
-\(Z^{(T_i-1)}\) where \(T_i\) is the trophic level of species \(i\) and
-\(Z\) is a scaling coefficient. (Savage \emph{et al.} 2004), which
-yields the same qualitative behavior, \emph{supplement figure 1}). The
-practical consequence of abundance distributions spanning many order of
-magnitude is seeing two ``rare'' species interacting requires two low
-probability events: observing two rare species \emph{at the same time}.
-
-To simulate the process of observation, for an ecological network \(A\)
-with \(S\) species, we sample abundances for each species from a
-standard-log-normal distribution. For each true interaction in \(A\)
-(i.e.~\(A_{ij} = 1\)) we estimate the probability of observing both
-species \(i\) and \(j\) at given place and time by simulating \(n\)
-observations of individuals, where the species of the individual
-observed at the \(1,2,\dots,n\)-th observation is drawn from the
-generated log-normal distribution of abundances. For each pair of
-species \((i,j)\), if both \(i\) and \(j\) are observed within the \(n\)
-observations, the interaction is tallied as a true positive if
-\(A_{ij}=1\) and a false positive otherwise. Similarly, if only one of
-\(i\) and \(j\) are observed---\emph{but not both}---in these \(n\)
-observations, but \(A_{ij}=1\), this is counted as a false-negative, and
-a true-negative otherwise.
-
-In fig.~\ref{fig:fig1} (C) and (D) we see this model of observation
-applied to networks generated using the niche model (Williams \&
-Martinez 2000) across varying levels of species richness, and in (b)
-applied to 243 food-webs from the Mangal database. For all niche model
-simulations in this manuscript, for a given number of species \(S\) the
-number of interactions is drawn from the flexible-links model fit to
-Mangal data (MacDonald \emph{et al.} 2020), effectively drawing the
-number of interactions \(L\) for a random niche model food-web as
-\(L \sim \text{BetaBinomial}(S^2-S+1, \mu \phi, (1-\mu)\phi)\), where
-the MAP estimate of (\(\mu\), \(\phi\)) applied to Mangal data from
-MacDonald \emph{et al.} (2020) is \((\mu = 0.086, \phi =24.3)\). All
-simulations were done with 500 independent replicates per unique number
-of observations \(n\). All analyses presented here are done in Julia
-v1.6 (Bezanson \emph{et al.} 2015) using both EcologicalNetworks.jl v0.5
-and Mangal.jl v0.4 {[}Banville \emph{et al.} (2021); ZENODO link
-TODO{]}. Note that the empirical data also is, due to the phenomena
-described here, very likely to \emph{already} have many false negatives,
-which is why we are interested in prediction of networks in the first
-place---we'll revisit this in the final section.
+interaction diversity (Moore \& McCarthy 2016), and by advocating use of
+null models like those presented here as a tool for both guiding design
+of surveys of species interactions and for modeling detection error in
+predictive models.
 
 \begin{figure}
-\hypertarget{fig:fig1}{%
+\hypertarget{fig:concept}{%
+\centering
+\includegraphics{./figures/concept.png}
+\caption{This conceptual example considers a sample of the trophic
+community of bears, wolves, salmon (pink fish), pike (yellow fish),
+berry trees, and aspen trees. The true metaweb (all realized
+interactions across the entire spatial extent) is shown on the left. In
+the center is what a hypothetical ecologist samples at each site. Notice
+that although bears are observed co-occurring with both salmon and pike,
+there was never a direct observation of bears eating pike, even though
+they actually do. Therefore, this interaction between bears and pike is
+a false negative.}\label{fig:concept}
+}
+\end{figure}
+
+\hypertarget{how-many-observations-of-a-non-interaction-do-we-need-to-be-confident-its-a-true-negative}{%
+\section{How many observations of a non-interaction do we need to be
+confident it's a true
+negative?}\label{how-many-observations-of-a-non-interaction-do-we-need-to-be-confident-its-a-true-negative}}
+
+We start with a naive model of interaction detection: we assume that
+every interacting pair of species is incorrectly observed as a
+not-interacting with an independent and fixed probability, which we
+denote pfn and subsequently refer to as the False-Negative Rate (FNR).
+If we observe the same species not-interacting N times, then the
+probability of a true-negative (denoted \(p_{tn}\)) is given by
+\(p_{tn}=1-(p_{fn})^N\). This relation (the probability-mass-function of
+geometric distribution, a special case of the negative-binomial
+distribution) is shown in Figure 1(A) for varying values of \(p_{fn}\)
+and illustrates a fundamental link between our ability to reliably say
+an interaction doesn't exist---\(p_{tn}\)---and the number of times we
+have observed a given species. In addition, note that also there is no
+non-zero \(p_{fn}\) for which we can ever prove that an interaction does
+not exist---no matter how many observations of non-interactions \(N\) we
+have, \(p_{tn}<1\).
+
+From Figure 1(A) it is clear that the more often we see two species
+co-occurring, but not interacting, the more likely the interaction is a
+true negative. This has several practical consequences: first it means
+negatives taken outside the overlap of the range of each species aren't
+informative. Second, we can use this relation to compute the expected
+number of total observations needed to obtain a ``goal'' number of
+observations of a particular pair of species (Figure 1(B)). As an
+example, if we hypothesize that \(A\) and \(B\) do not interact, and we
+want to see species \(A\) and \(B\) both co-occurring and not
+interacting 10 times to be confident this is a true negative, then we
+need an expected 1000 observations of all species if the relative
+abundances of \(A\) and \(B\) are both \(0.1\).
+
+Because the true FNR is latent, we can never actually be sure what the
+actual number of false negatives in our data---however, we can use
+simulation to estimate it for datasets of a given size using neutral
+models of observation. If some of the ``worst-case'' FNRs presented in
+fig.~\ref{fig:geometric}(A) seem unrealistically high, consider that
+species are observed in proportion to their relative abundance. In the
+next section we demonstrate that the distribution of abundance in
+ecosystems can lead to very high realized values of FNR (\(p_{fn}\))
+simply as an artifact of sampling effort.
+
+\begin{figure}
+\hypertarget{fig:geometric}{%
 \centering
 \includegraphics{./figures/fig1.png}
-\caption{A) The probability an observed interaction is a true negative
-(y-axis) given how many times it has been sampled as a non-interaction
-(x-axis). Each color reflects a different value of \(p_{fn}\), the
-false-negative rate (FNR). this is effectively the cdf of the
-negative-binomial distribution with \(r=1\). (B) The expected needed
-observations of all individuals of all species (y-axis) required to
-obtain a goal number of observations (colors) of a particular species,
-and a function of the relative abundance of that focal species (x-axis).
-(C) and (D): False negative rate (y-axis) as a function of total
-sampling effort (x-axis) and network size, computed using the method
-described above. For 500 independent draws from the niche model
-Williams2000SimRul at varying levels of species richness (colors) with
-connectance drawn according to the flexible-links model
-MacDonald2020RevLin as described in the main text. For each draw from
-the niche model, 200 sets of 1500 observations are simulated, for which
-each the mean false negative rate at each observation-step is computed.
-Means denoted with points, with \(1\sigma\) in the first shade and
-\(2\sigma\) in the second. B: empirical food webs from Mangal database
-in teal, applied to the same process as the A. The outlier on panel B is
-a 714 species food-web}\label{fig:fig1}
+\caption{(A) The probability that an observed interaction is a true
+negative (y-axis) given how many times it has been sampled as a
+non-interaction (x-axis). Each color reflects a different value of
+\(p_{fn}\), the false-negative rate (FNR)---this is effectively the cdf
+of the geometric distribution. (B): The expected needed observations of
+all individuals of all species (y-axis) required to obtain a goal number
+of observations (colors) of a particular species, and a function of the
+relative abundance of that focal species (x-axis). (C): False negative
+rate (y-axis) as a function of total sampling effort (x-axis) and
+network size, computed using the method described above. For 500
+independent draws from the niche model (Williams \& Martinez (2000)) at
+varying levels of species richness (colors) with connectance drawn
+according to the flexible-links model (MacDonald \emph{et al.} (2020))
+as described in the main text. For each draw from the niche model, 200
+sets of 1500 observations are simulated, for which each the mean false
+negative rate at each observation-step is computed. Means denoted with
+points, with 1 in the first shade and 2 in the second. (D): Same as (C),
+except using empirical food webs from Mangal database, where richness.
+The outlier on (D) is a 714 species food-web.}\label{fig:geometric}
 }
@@
 
-In panel (c) of fig.~\ref{fig:totalobs}, we show the expected number of
-total observations needed to obtain a ``goal'' number of observations
-(colors) of a particular ``focal'' species. As an example, if we
-hypothesize that \(A\) and \(B\) do not interact, and we want to see
-species \(A\) and \(B\) both co-occurring and not-interacting 10 times
-to be confident this is a negative (a la fig.~\ref{fig:negativebinom}),
-then we need an expected 10,000 observations of all species if the
-relative abundance of \(A\) is 0.00125.
-
-Empirical data on interactions are subject to the practical limitations
-of funding and human-work hours, and therefore existing data tend to
-fall on the order on 100s or 1000s observations of individuals per site
-(Nielsen \& Bascompte 2007; Schwarz \emph{et al.} 2020; Resasco \emph{et
-al.} 2021). Clear aggregation of this data has proven difficult to find
-and a meta-analysis of network data and sampling effort seems both
-pertinent and necessary, in addition to the effects of aggregation of
-interactions across taxonomic scales (Gauzens \emph{et al.} 2013;
-Giacomuzzo \& Jordán 2021). Further, from fig.~\ref{fig:totalobs} it is
-evident that the number of species considered in a study is inseparable
-from the false-negative rate in that study, and this effect should be
-taken into account when designing samples of ecological networks in the
-future.
+\hypertarget{false-negatives-as-a-product-of-relative-abundance}{%
+\section{False-negatives as a product of relative
+abundance}\label{false-negatives-as-a-product-of-relative-abundance}}
+
+We now show that the realized false-negative rate of species
+interactions changes drastically with sampling effort due to the
+intrinsic variation of the abundance of individuals of each species
+within a community. We do this by simulating the process of observation
+of species interactions, applied both to 243 empirical food webs from
+the Mangal database (Banville \emph{et al.} 2021) as well as random
+food-webs generated using the niche model (Williams \& Martinez 2000), a
+simple generative model of food-web structure. Our neutral model of
+observation assumes each observed species is drawn from the distribution
+in proportion to each species' abundance at that place and time.
+
+The abundance distribution of a community can be reasonably-well
+described by a log-normal distribution (Volkov \emph{et al.} 2003). In
+addition to the log-normal distribution, we also tested the case where
+the abundance distribution is derived from power-law scaling
+\(Z^{(log(T_i)-1)}\) where \(T_i\) is the trophic level of species \(i\)
+and \(Z\) is a scaling coefficient (Savage \emph{et al.} 2004), which
+yields the same qualitative behavior. The practical consequence of
+abundance distributions spanning many orders of magnitude of abundance
+is that observing two ``rare'' species interacting requires two low
+probability events: observing two rare species at the same time.
+
+To simulate the process of observation, for an ecological network \(M\)
+with \(S\) species, we sample abundances for each species from a
+standard-log-normal distribution. For each true interaction in the
+adjacency matrix \(M\) (i.e. \(M_{ij}=1\)) we estimate the probability
+of observing both species \(i\) and \(j\) at a given place and time by
+simulating \(n\) observations of all individuals of any species, where
+the species of the individual observed at the \(\{1,2,\dots,n\}\)-th
+observation is drawn from the generated log-normal distribution of
+abundances. For each pair of species \((i,j)\), if both \(i\) and \(j\)
+are observed within the n-observations, the interaction is tallied as a
+true positive if \(M_{ij}=1\). If only one of \(i\) or \(j\) are
+observed---but not both---in these \(n\) observations, but \(M_{ij}=1\),
+this is counted as a false-negative, and a true-negative otherwise.
+
+In fig.~\ref{fig:geometric}(C) we see this model of observation applied
+to niche model networks across varying levels of species richness, and
+in fig.~\ref{fig:geometric}(D) the observation model applied to Mangal
+food webs. For all niche model simulations in this manuscript, for a
+given number of species \(S\) the number of interactions is drawn from
+the flexible-links model fit to Mangal data (MacDonald \emph{et al.}
+2020), effectively drawing the number of interactions \(L\) for a random
+niche model food-web as
+
+\[L \sim  \text{BetaBinomial}(S^2-S+1,\mu\phi, 1-\mu\phi)\]
+
+where the MAP estimate of \((\mu, \phi)\) applied to Mangal data from
+{[}{]} MacDonald et al.~2020 is \((\mu=0.086, \phi=24.3)\). All
+simulations were done with 500 independent replicates per unique number
+of observations n.~All analyses presented here are done in Julia v1.8
+(Bezanson \emph{et al.} 2015) using both EcologicalNetworks.jl v0.5 and
+Mangal.jl v0.4 (Banville \emph{et al.} 2021) and are hosted at
+(GITHUB\_LINK\_TODO). Note that the empirical data, for the reasons
+described above, very likely already contains many false negatives,
+we'll revisit this issue in the final section.
+
+From fig.~\ref{fig:geometric}(C) it is evident that the number of
+species considered in a study is inseparable from the false-negative
+rate in that study, and this effect should be taken into account when
+designing samples of ecological networks in the future. We see a similar
+qualitative pattern in fig.~\ref{fig:geometric}(D) where the FNR drops
+off quickly as a function of observation effort, mediated by total
+richness. The practical consequence of the bottom row of Figure 1 is
+whether the total number of observations of all species (the x-axis) for
+the range of possible FNR we deem acceptable (the y-axis) is feasible.
+This raises two points: first, empirical data on interactions are
+subject to the practical limitations of funding and human-work hours,
+and therefore existing data tend to fall on the order of hundreds or
+thousands observations of individuals per site. Clear aggregation of
+data on sampling effort has proven difficult to find and a meta-analysis
+of network data and sampling effort seems both pertinent and necessary,
+in addition to the effects of aggregation of interactions across
+taxonomic scales (Gauzens \emph{et al.} 2013; Giacomuzzo \& Jordán
+2021). This inherent limitation on in-situ sampling means we should
+optimize where we sample across space so that for a given number of
+samples, we obtain the maximum information possible. Second, what is
+meant by ``acceptable'' FNR? This raises the question: does a shifting
+FNR lead to rapid transitions in the our ability inference and
+predictions about the structure and dynamics of networks, or does it
+produce a roughly linear decay in model efficacy? We explore this in the
+next section.
 
@@
 false-negatives in a data set of a given size. This could prove fruitful
-both for designing surveys of interactions (Canard \emph{et al.} 2012),
-but also because we may want to incorporate models of observation error
-into predictive models (Joseph 2020). Additionally, one must consider
-the context for sampling---is the goal to detect a particular species
-\(A\) (as in fig.~\ref{fig:totalobs} (c)), or to get a representative
-sample of interactions across the species pool? This argument is
-well-considered when sampling species (Willott 2001), but has not yet
-been internalized for designing samples of communities.
-
-\hypertarget{positive-associations-can-increase-the-probability-of-false-negatives}{%
-\subsection{Positive associations can increase the probability of
-false-negatives}\label{positive-associations-can-increase-the-probability-of-false-negatives}}
+both for designing surveys of interactions but also because we may want
+to incorporate models of imperfect detection error into predictive
+interactions models, as Joseph (2020) does for species occurrence
+modeling. Additionally, we emphasize that one must consider the context
+for sampling---is the goal to detect a particular species (as in
+fig.~\ref{fig:geometric}(C)), or to get a representative sample of
+interactions across the species pool? This argument is well-considered
+when sampling individual species (Willott 2001), but has not yet been
+adopted for designing samples of communities.
+
+\hypertarget{positive-associations-increase-the-false-negative-rate}{%
+\section{Positive associations increase the false-negative
+rate}\label{positive-associations-increase-the-false-negative-rate}}
 
@@
 \emph{et al.} 2016). However, here we demonstrate that the probability
-of observing a false negative can be \emph{higher} if there is some
-positive association between occurrence of species \(A\) and \(B\).
-
-If we denote the probability that we observe an interaction we know
-exists between \(A\) and \(B\) as \(P(AB)\), and if there is \emph{no}
+of observing a false negative can be higher if there is some positive
+association in the occurrence of species \(A\) and \(B\).If we denote
+the probability that we observe the co-occurrence of two species \(A\)
+and \(B\) that we know interact as \(P(AB)\) and if there is no
 association between the marginal probabilities of observing \(A\) and
 observing \(B\), denoted \(P(A)\) and \(P(B)\) respectively, then the
-probability of observing the interaction \(P(AB) = P(A)P(B)\). In the
-other case where there \emph{is} some positive strength of association
+probability of observing their co-occurrence \(P(AB) = P(A)P(B)\). In
+the other case where there is some positive strength of association
 between observing both \(A\) and \(B\) because this interaction is
@@
 \(P(B)\) are not independent and instead are positively correlated,
-\emph{i.e.} \(P(AB) > P(A)P(B)\). In this case, the probability of
-observing a false negative in our naive model from
-fig.~\ref{fig:negativebinom} is \(p_{fn} = 1 - P(AB)\) which due to the
-above inequality implies \(p_{fn} \geq 1 - P(A)P(B)\) which indicates
-increasingly greater probability of a false negative as
-\(P(AB) \to P(AB) \gg P(A)P(B)\).
-
-However this does not consider variation in species abundance in space
-and time, (Poisot \emph{et al.} 2015). If positive or negative
+i.e.~\(P(AB)> P(A)P(B)\). In this case, the probability of observing a
+false negative in our naive model from fig.~\ref{fig:geometric}(A) is
+\(p_{fn}= 1-P(AB)\), which due to the above inequality implies
+\(p_{fn} >1-P(A)P(B)\). This indicates an increasingly greater
+probability of a false negative as \(P(AB) \to P(AB) \gg P(A)P(B)\).
+However, this still does not consider variation in species abundancein
+space and time (Poisot \emph{et al.} 2015). If positive or negative
 associations between species structure variation in the distribution of
@@
 as the probability of false negative would not be constant for each pair
-of species across sites. To test for this association empirical data, we
-use two datasets: a set of host-parasite interactions sampled across 51
-sites with 327 total taxa (Hadfield \emph{et al.} 2014) and a set of 18
-New Zealand freshwater stream food webs with 566 total taxa (Thompson \&
-Townsend 2000). We simply compute the empirical marginal distribution of
-species occurrence, and compare the product of the marginals,
-\(P(A)P(B)\), to the empirical joint distribution \(P(AB)\).
+of species across sites.
+
+To test for this association in data we scoured Mangal for datasets with
+many spatial or temporal replicates of the same system. For each
+dataset, we compute the marginal probability \(P(A)\) of occurrence of
+each species \(A\) across all networks in the dataset. For each pair of
+interacting species \(A\) and \(B\), we then compute and compare the
+probability of co-occurrence if each species occurs independently,
+\(P(A)P(B)\), to the empirical joint probability of co-occurrence,
+\(P(AB)\). Following our analysis above, if \(P(AB)\) is greater than
+\(P(A)P(B)\), then we expect our neutral estimates of the FNR above to
+underestimate the realized FNR. In fig.~\ref{fig:mangal}, we see the
+difference between \(P(AB)\) and \(P(A)P(B)\) for the seven suitable
+datasets with enough spatio-temporal replicates and a shared taxonomic
+backbone (meaning all individual networks use common species
+identifiers) found on Mangal to perform this analysis. Further details
+about each dataset are reported in tbl.~\ref{tbl:id}.
 
 \begin{figure}
-\hypertarget{fig:associations}{%
+\hypertarget{fig:mangal}{%
 \centering
-\includegraphics{./figures/positiveassociations.png}
-\caption{Top: Hadfield, Bottom: NZ Stream Foodwebs. Effectively a
-version of Cazelles \emph{et al.} (2016) figure 1 panel A. Both
-distributions have \(\mu \neq 0\) with
-\(p < 10^{-50}\)}\label{fig:associations}
+\includegraphics{./figures/fig2.png}
+\caption{The difference between joint-probability of co-occurrence
+(P(AB)) and expected probability of co-occurrence under independence
+(P(A)P(B)) for interacting species for each dataset. The red-dashed line
+indicates 0. Each histogram represents a density, meaning the area of
+the entire curve sums to 1. The continuous density estimate (computed
+using local smoothing) is shown in grey. The p-value on each plot is the
+result of a one-sided T-test comparing the mean of each distribution to
+0.}\label{fig:mangal}
 }
@@
 
-In fig.~\ref{fig:associations}, both host-parasite system (top) and
-food-web (bottom) exhibit these positive associations. There is no
-reason to expect the strength of this association to be the same in
-different systems. At the moment, computing this metric for all of the
-networks in the Mangal database proves challenging as most data sets use
-different taxonmic identifiers, often at different resolutions. These
-particular datasets (Thompson \& Townsend 2000; Hadfield \emph{et al.}
-2014) were usable because they already have been sorted to have a fixed
-taxonomic backbone (as part of EcologicalNetworks.jl (Banville \emph{et
-al.} 2021)). Applying this in bulk to Mangal food-webs presents the
-difficulty of resolving different taxon identifiers across spatial
-samples of species with to different resolutions, which is why we can't
-simply apply this to the whole Mangal database---this highlights a
-general problem of resolving taxonomic indentifiers which use different
-names and different resolutions in different ecological datasets, which
-is a problem that needs to be addressed for computational approaches to
-scale up to the world of big-ecological-data we hope to build, although
-this is a task that may be aided via natural-language-processing
-methods.
-
-\hypertarget{the-impact-of-false-negatives-on-network-analysis-and-prediction}{%
-\section{The impact of false-negatives on network analysis and
-prediction}\label{the-impact-of-false-negatives-on-network-analysis-and-prediction}}
-
-We now transition toward assessing the effects of false negatives in
-data on the properties of the networks which we derive from this
-interaction data, and their effect on models for predicting interactions
-in the future.
-
-\hypertarget{effects-of-false-negatives-on-network-properties}{%
-\subsection{Effects of false-negatives on network
-properties}\label{effects-of-false-negatives-on-network-properties}}
-
-Here we simulate the process of observation with error to generate
-synthetic data with a known proportion of false negatives, and compare
-the computed network properties of the original ``true'' network to the
-computed properties of the ``observed'' network with added
-false-negatives. In fig.~\ref{fig:properties} we see the mean-squared
-error of connectance, mean degree-centrality, and spectral radius,
-computed across 2000, 2000, and 300 replicates respectively at each
-value of the false negative rate \(p_{fn}\). All replicates use random
-food-webs simulated using the niche model (Williams \& Martinez 2000)
-with \(100\) species and connectance drawn from the flexible-links model
-(MacDonald \emph{et al.} 2020) as before.
+\hypertarget{tbl:id}{}
+\begin{longtable}[]{@{}
+  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.3182}}
+  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1705}}
+  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0568}}
+  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0568}}
+  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}
+  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}
+  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}
+  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}
+  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}@{}}
+\caption{\label{tbl:id}This table describes the datasets used in the
+above analysis (Fig 2). The table reports the type of each dataset, the
+total number of networks in each dataset \((N)\), the total species
+richness in each dataset \((S)\), the connectance of each metaweb (all
+interactions across the entire spatial-temporal extent) \((C)\), the
+mean species richness across each local network \(S\), the mean
+connectance of each local network \(C\), the mean \(\beta\)-diversity
+among overlapping species across all pairs of network species
+(\(\bar{\beta}_{OS}\)), and the mean \(\beta\)-diversity among all
+species in the metaweb (\(\bar{\beta}_{WN}\)). Both metrics are computed
+using KGL \(\beta\)-diversity (Koleff \emph{et al.}
+2003)}\tabularnewline
+\toprule()
+\begin{minipage}[b]{\linewidth}\centering
+Network
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Type
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\(N\)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\(S\)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\(C\)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\(\bar{S}\)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\(\bar{C}\)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\(\bar{\beta}_{OS}\)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\(\bar{\beta}_{WN}\)
+\end{minipage} \\
+\midrule()
+\endfirsthead
+\toprule()
+\begin{minipage}[b]{\linewidth}\centering
+Network
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+Type
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\(N\)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\(S\)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\(C\)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\(\bar{S}\)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\(\bar{C}\)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\(\bar{\beta}_{OS}\)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
+\(\bar{\beta}_{WN}\)
+\end{minipage} \\
+\midrule()
+\endhead
+Kopelke \emph{et al.} (2017) & Food Web & 100 & 98 & 0.037 & 7.87 &
+0.142 & 1.383 & 1.972 \\
+Thompson \& Townsend (2000) & Food Web & 18 & 566 & 0.014 & 80.67 &
+0.049 & 1.617 & 1.594 \\
+Havens (1992) & Food Web & 50 & 188 & 0.065 & 33.58 & 0.099 & 1.468 &
+1.881 \\
+Ponisio \emph{et al.} (2017) & Pollinator & 100 & 226 & 0.079 & 23.0 &
+0.056 & 1.436 & 1.870 \\
+Hadfield \emph{et al.} (2014) & Host-Parasite & 51 & 327 & 0.085 & 32.71
+& 0.337 & 1.477 & 1.952 \\
+Closs \& Lake (1994) & Food Web & 12 & 61 & 0.14 & 29.09 & 0.080 & 1.736
+& 1.864 \\
+CaraDonna \emph{et al.} (2017) & Pollinator & 86 & 122 & 0.18 & 21.42 &
+0.312 & 1.527 & 1.907 \\
+\bottomrule()
+\end{longtable}
+
+In each of these datasets, the joint probably of co-occurrence \(P(AB)\)
+is decisively greater than our expectation if species co-occur in
+proportion to their relative abundance \(P(A)P(B)\). This suggests that
+there may not be as many ``neutrally forbidden links'' (Canard \emph{et
+al.} 2012) as we might think, and that the reason we do not have records
+of interactions between rare species is probably due to observation
+error. This has serious ramifications for the widely observed property
+of nestedness seen in bipartite networks (Bascompte \& Jordano
+2007)---perhaps the reason we have lots of observations between
+generalists is because they are more abundant, and this is particularly
+relevant as we have strong evidence that generalism drives abundance
+(Song \emph{et al.} 2022), not vice-versa.
+
+\hypertarget{the-impact-of-false-negatives-on-network-properties-and-prediction}{%
+\section{The impact of false-negatives on network properties and
+prediction}\label{the-impact-of-false-negatives-on-network-properties-and-prediction}}
+
+Here, we assess the effect of false negatives on our ability to make
+predictions about interactions, as well as their effect on network
+structure. The prevalence of false-negatives in our data is the catalyst
+for interaction prediction in the first place, and as a result methods
+have been proposed to counteract this bias Poisot \emph{et al.} (2022).
+However, it is feasible that the FNR is so high that it could induce too
+much noise for an interaction prediction model to detect the signal of
+possible interaction between species.
+
+To test this we use the dataset from Hadfield \emph{et al.} (2014) that
+describes host-parasite interaction networks sampled across 51 sites,
+and the same method as Strydom \emph{et al.} (2021) to extract latent
+features for each species in this dataset based on co-occurrence. We
+then predict a metaweb (equivalent to predicting true or false for an
+interaction for each species pair, effectively a binary classification
+problem) from these species-level features using four candidate models
+for binary classification---three often used machine-learning (ML)
+methods (Boosted Regression Tree (BRT), Random Forest (RF), Decision
+Tree (DT)), and one naive model from classic statistics (Logistic
+Regression (LR)). Each of the ML models are bootstrap aggregated (or
+bagged) with 100 replicates each. We partition the data into 80-20
+training-test split, and then seed the training data with false
+negatives at varying rates, but crucially do nothing to the test data.
+We fit all of these models using MLJ.jl, a high-level Julia framework
+for a wide-variety of ML models (Blaom \emph{et al.} 2020). We evaluate
+the efficacy of these models using two common measures of binary
+classifier performance: the area under the receiver-operator curve
+(ROC-AUC) and the area under the precision-recall curve (PR-AUC), for
+more details see (Poisot 2022) Here, PR-AUC is slightly more relevant as
+it is a better indicator of prediction of false-negatives. The results
+of these simulations are shown in fig.~\ref{fig:addedfnr}(A) and (B).
 
 \begin{figure}
-\hypertarget{fig:properties}{%
+\hypertarget{fig:addedfnr}{%
 \centering
-\includegraphics{./figures/props_specrad.png}
-\caption{The mean-squared error (y-axis) of various network properties
-(different colors) across various simulated false-negative rates
-(x-axis). Means denoted with points, with \(1\sigma\) in the first shade
-and \(2\sigma\) in the second.}\label{fig:properties}
+\includegraphics{./figures/fig3.png}
+\caption{(A) The area-under the receiver-operator curve (ROC-AUC). (B)
+The area-under the precision-recall curve (PR-AUC; right) for each
+different predictive model (colors/shapes) across a spectrum of the
+proportion of added false negatives (x-axis). (C) The mean trophic-level
+of all species in a network generated with the niche model across
+different species richnesses (colors). For each value of the FNR, the
+mean trophic level was computed across 50 replicates. The shaded region
+for each line is one standard-deviation across those
+replicates.}\label{fig:addedfnr}
 }
@@
 
-We consider three properties: connectance, mean-degree-centrality, and
-spectral radius, indicative of local, meso, and global structure.
-Connectance is effectively a node-level property, a proxy for the degree
-distribution. Degree-centrality captures a different aspect of network
-structure than connectance, more indicative of meso-level properties
-that describe local `regions' of nodes interact. Spectral radius
-(equivalent to the magnitude of the largest eigenvalue of \(A\)) is a
-measure of global structure, and demonstrates the most variability in
-response to false-negatives. For example, if a false-negative splits a
-metaweb into two components, spectral-radius becomes the largest
-eigenvalue of each of those two components. Also note that the form of
-this error function varies little as species richness changes
-(\emph{supplemental figure 2}). Practically, fig.~\ref{fig:properties}
-shows us that different scales of measuring network structure vary in
-their response to false negatives---connectance responds roughly
-linearly to false negatives, whereas mean-degree-centrality decisively
-does not. This implies that false-negatives adversely could effect
-indirect interactions (Williams \emph{et al.} 2002).
-
-\hypertarget{effects-of-false-negatives-on-ability-to-make-predictions}{%
-\subsection{Effects of false negatives on ability to make
-predictions}\label{effects-of-false-negatives-on-ability-to-make-predictions}}
-
-Here, we assess the effect of false negatives in data on our ability to
-make predictions about interactions. The prevalence of false-negatives
-in data is the catalyst for interaction prediction in the first place,
-and as a result methods have been proposed to counteract this bias
-(Stock \emph{et al.} 2017; Poisot \emph{et al.} 2021b). However, it is
-feasible this could induce too much noise for a interaction prediction
-model to detect the signal of interaction chance from to the latent
-properties of each species derived from the empirical network if the
-number of false-negatives in a dataset becomes too overwhelming.
-
-To test this, we use the same predictive model and dataset as in Strydom
-\emph{et al.} (2021) to predict a metaweb from various empirical slices
-of the species pool observed across space. This dataset from Hadfield
-\emph{et al.} (2014) describes host-parasite interaction networks
-sampled across 51 sites. We partition the data into 80-20 training-test
-split, and then seed the training data with false negatives varying
-rates, but crucially do nothing to the test data. We use the same model,
-a neural-network with 3 feed-forward layers to predict outputs based on
-features extracted from co-occurence (see Strydom \emph{et al.} (2021)
-for more details). The single modification we make to the model is not
-enforcing a number of positives in the training data as this constraint
-is eventually impossible for increasing FNR. In fig.~\ref{fig:rocpr}, we
-show receiving-operating-characteristic (ROC) and precision-recall (PR)
-curves for the model with varying levels of synthetic false-negatives
-added to the data.
-
-\begin{figure}
-\hypertarget{fig:rocpr}{%
-\centering
-\includegraphics{./figures/rocpr_falsenegatives.png}
-\caption{Receiver-operating-characteristic (left) and precision-recall
-(right) curves for the model on varying levels of false-negatives in the
-data (colors). For each value of FNR, we run 30 random training/test
-splits on 80/20 percent of the data. Replica of figure 1 in Strydom
-\emph{et al.} (2021)}\label{fig:rocpr}
-}
-\end{figure}
-
-Interestingly, the performance of the model from Strydom \emph{et al.}
-(2021) changes little with many added false-negatives, which is good
-evidence in favor neural-networks as a class of model for interaction
-detection. Again, similar to our caveat in the previous section, this
-dazta is \emph{already} likely to have many false-negatives, so the
-effects of adding more as we do in this illustration might be mitigated
-because there are already non-simulated false-negatives in the original
-data which impact the models performance, even in the \(p_{fn} = 0\)
-case.
-
-We conclude be proposing that simulating the effects of false negatives
-in this way can serve as an additional validation tool when aiming to
-detect structural properties of networks using generative null models
-(Connor \emph{et al.} 2017), or when evaluating the robustness of a
-predictive model.
+One interesting result seen in fig.~\ref{fig:addedfnr}(A) and (B) is
+that the ROC-AUC value does not approach random in the same way the
+PR-AUC curve does as we increase the added FNR. The reason for this is
+that ROC-AUC is fundamentally not as useful a metric in assessing
+predictive capacity as PR-AUC. As we keep adding more false-negatives,
+the network eventually becomes a zeros matrix, and these models can
+still learn to predict ``no-interaction'' for all possible species
+pairs, which does far better than random guessing (ROC-AUC
+\textgreater{} 0.5) in terms of the true and false positive rates (the
+components of ROC-AUC). This highlights a more broad issue of label
+class imbalance, meaning there are far more non-interactions than
+interactions in data. A full treatment of the importance of
+class-balance is outside the scope of this paper, but is explored
+in-depth in (Poisot 2022).
+
+Although these ML models are surprisingly performant at link prediction
+given their simplicity, there have been several major developments in
+the field applying deep-learning methods to many tasks in network
+inference and prediction---namely graph-representation learning (GRL,
+Khoshraftar \& An (2022)) and graph convolutional networks (Zhang
+\emph{et al.} 2019). At this time, these advances can not yet be applied
+to ecological networks because they require far more data than we
+currently have. We already have lots of features that could be used as
+inputs into these models (i.e.~species level data about occurrence,
+genomes, abundance, etc.), but our network datasets barely get into the
+hundreds of local networks sampled across space and time
+tbl.~\ref{tbl:id}. Once we start to get into the thousands, these models
+will become more useful, but this can only be done with systematic
+monitoring of interactions. This again highlights the need to optimize
+our sampling effort to maximize the amount of information contained in
+our data given the expensive nature of sampling interactions.
+
+We also consider how the FNR affects network properties. In
+fig.~\ref{fig:addedfnr}(C) we see the mean trophic level across networks
+simulated using the niche model (as above), across a spectrum of FNR
+values. In addition to the clear dependence on richness, we see that
+mean trophic level, despite varying widely between niche model
+simulations, tends to be relatively robust to false negatives and does
+not deviate widely from the true value until very large FNRs,
+i.e.~\(p_{fn} > 0.7\).
 
@@
 
-Here, we have demonstrated that we expect false-negatives in species
-interaction datasets purely due to the distribution of abundances within
-a community. Positive associations between species occurrence (Cazelles
-\emph{et al.} 2016) can increase the realized false-negative rate if the
-sampling effort is limited, and we have presented evidence of this
-non-random structure of co-occurrence in two sets of
-spatially-replicated ecological network samples. We have also shown that
-false-negatives can cause varying responses in our measurements of
-network properties and further could impact our ability to reliably
-predict interactions, which highlights the need for further research
-into methods for correcting this bias in existing data (Stock \emph{et
-al.} 2017). A brief caveat here is that we do not consider the rate of
+Species interactions enable the persistence and functioning of
+ecosystems, but our understanding of interactions is limited due to the
+intrinsic difficulty of sampling. Here we have provided a null model for
+the expected number of false-negatives in an interaction dataset. We
+demonstrated that we expect many false-negatives in species interaction
+datasets purely due to the intrinsic variation of abundances within a
+community. We also, for the first time to our knowledge, measured the
+strength of association between co-occurrence and interactions (Cazelles
+\emph{et al.} 2016) across many empirical systems for the first time,
+and found that these positive associations are both very common, and
+showed algebraically that they increase the realized FNR. We have also
+shown that false-negatives could further impact our ability to both
+predict interactions and infer properties of the networks, which
+highlights the need for further research into methods for correcting
+this bias in existing data.
+
+A better understanding of how false-negatives impact our inference of
+network structure and dynamics is prediction of ecological networks by
+both using information about individual species interactions and the
+structure of metawebs on large scales is a practical necessity.
+False-negatives could pose a problem for many forms of inference in
+network ecology. For example, inferring the structural or dynamic
+stability of a network could be prone to error if the observed network
+is not sampled ``enough''. What exactly ``enough'' means is then
+specific to the application, and should be assessed via methods like
+those here when designing samples. Further, predictions about network
+rewiring (Thompson \& Gonzalez 2017) due to range shifts in response to
+climate change could be error-prone without accounting for interactions
+that have not been observed but that still may become climatically
+infeasible. As is evident from Figure 1(A), we can never guarantee there
+are no false-negatives in data. In recent years, there has been interest
+toward explicitly accounting for false-negatives in models (Stock
+\emph{et al.} 2017; Young \emph{et al.} 2021), and a predictive approach
+to networks---rather than expecting our samples to fully capture all
+interactions (Strydom \emph{et al.} 2021). As a result, better models
+for predicting interactions are needed for interaction networks. This
+includes explicitly accounting for observation error (Johnson \&
+Larremore 2021)---certain classes of models have been used to reflect
+hidden states which account for detection error in occupancy modeling
+(Joseph 2020), and could be integrated in the predictive models of
+interactions in the future.
+
+A brief caveat here is that we do not consider the rate of
 false-positives---in large part false-positives can be explained by
 misidentification of species, although this could be a relevant
-consideration in some cases.
-
-What does the future hold for this research? A better understanding of
-how false-negatives impact our analyses and prediction of ecological
-networks is a practical necessity. False-negatives could pose a problem
-for many forms of inference in network ecology. For example, if we aim
-to measure structural or dynamic stability of a network, or to infer
-indirect interactions (Williams \emph{et al.} 2002), these estimates
-could be prone to error if the observed network is not sampled
-``enough''. What exactly ``enough'' means is then specific to the
-application, and should be assessed via methods like those here when
-designing samples. Further, predictions about network rewiring (Thompson
-\& Gonzalez 2017) due to a changing climate could be error-prone without
-accounting for interactions that have not been observed but that still
-may become climatically infeasible.
-
-This highlights the need for a quantitatively robust approach samples
-design: for interactions (Jordano 2016b) and otherwise (Carlson \emph{et
-al.} 2020). The primary takeaway is that when planning the sampling
-effort across sites, it is necessary to take both the size of the
-species pool into account. Further, simulating the process of
-observation could be a powerful tool for planing study design which
-takes relative abundance into account, and provide a null baseline for
-detection of interaction strength. A model similar to that here can and
-should be used to provide a neutral expectation of true-negative
-probability given a number of observations of individuals at a given
-place and time.
-
-As we derive from fig.~\ref{fig:negativebinom}, we can never guarantee
-there are no false-negatives in data. In recent years, there has been
-interest toward explicitly accounting for false-negatives in models
-(Stock \emph{et al.} 2017; Young \emph{et al.} 2021), and toward a
-predictive approach toward interactions ---rather than expect that our
-samples can fully capture all interactions, we know that some
-interactions between species will not be observed due to finite sampling
-capacity, and instead we must impute the true metaweb of interactions
-given a set of samples (Strydom \emph{et al.} 2021). As a result, better
-predictive approaches are needed for interaction networks (Strydom
-\emph{et al.} 2021), and building models that explicitly account for
-observation error is a necessary step forward for predictive ecological
-models (Johnson \& Larremore 2021; Young \emph{et al.} 2021). Neural
-networks, like the one used to predict interactions in the above
-section, have been used to reflect hidden states which account for
-detection error in occupancy modeling (Joseph 2020), and could be
-integrated in the predictive models of the future.
-
-A better conceptual framework for designing surveys and monitoring
-networks, and incorporating sequential observations over time is clearly
-needed (Carlson \emph{et al.} 2020), combined with a meta-analysis of
-sampling effort and taxonomic resolution in existing data. Incorporating
-a better understanding of sampling effects and bias on both the future
-design of biodiversity monitoring systems, and the predictive models we
-wish to apply to this data, is imperative in making actionable
-predictions about the future of ecological interactions on our planet.
+consideration in some cases. The same logic that we apply to
+false-negatives could easily be applied to false-positives, e.g.~that we
+can be much more confident that an interaction is a true positive if we
+have observed it 50 times rather than only once, and we could similarly
+model this using the geometric distribution as in
+fig.~\ref{fig:geometric}(A). However, because ecological networks are so
+sparse, there are far more negatives than positives in the dataset, and
+therefore likely to be far more false-negatives than false-positives in
+absolute terms.
+
+This work has several practical consequences for the design of
+interaction samples. Simulating the process of observation could be a
+powerful tool for estimating the sampling effort required by a study
+that takes relative abundance into account, and provides a null baseline
+for expected FNR. It is necessary to take the size of the species pool
+into account when deciding how many total samples is sufficient for an
+``acceptable'' FNR (fig.~\ref{fig:geometric}(C \& D)). Further the
+spatial and temporal turnover of interactions means any approach to
+sampling prioritization must be spatiotemporal. We demonstrated earlier
+that observed negatives outside of the range of both species aren't
+informative, and therefore using species distribution models could aid
+in this spatial prioritization of sampling sites.
+
+Our work highlights the need for a quantitatively robust approach to
+sampling design, both for interactions (Jordano 2016) and all other
+aspects of biodiversity (Carlson \emph{et al.} 2020). As anthropogenic
+forces create rapid shifts in our planet's climate and biosphere, this
+is an imperative to maximize the amount of ecological information we get
+in our finite samples, and make our inferences and decisions based on
+this data as robust as possible. Where we choose to sample, and how
+often we choose to sample there, has strong impacts on the inferences we
+make from data. Incorporating a better understanding of sampling effort
+and bias to the design of biodiversity monitoring systems, and the
+inference and predictive models we apply to this data, is imperative in
+understanding how biodiversity is changing, and making actionable
+forecasts about the future of ecological interactions on our planet.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Bascompte2007PlaMut}{}}%
+Bascompte, J. \& Jordano, P. (2007).
+\href{https://doi.org/10.1146/annurev.ecolsys.38.091206.095818}{Plant-Animal
+Mutualistic Networks: The Architecture of Biodiversity}. \emph{Annual
+Review of Ecology, Evolution, and Systematics}, 38, 567--593.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Becker2021OptPre}{}}%
@@
 models to prioritize viral discovery in zoonotic reservoirs}.
-\emph{bioRxiv}, 2020.05.22.111344.
 
@@
 Bezanson, J., Edelman, A., Karpinski, S. \& Shah, V.B. (2015).
-\href{https://arxiv.org/abs/1411.1607}{Julia: A Fresh Approach to
-Numerical Computing}. \emph{arXiv:1411.1607 {[}cs{]}}.
+\href{https://doi.org/10.48550/arXiv.1411.1607}{Julia: A Fresh Approach
+to Numerical Computing}.
 
@@
 of ecological interactions}. \emph{Ecology Letters}, 23, 1050--1063.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Blaom2020MljJul}{}}%
+Blaom, A.D., Kiraly, F., Lienart, T., Simillides, Y., Arenas, D. \&
+Vollmer, S.J. (2020). \href{https://doi.org/10.21105/joss.02704}{MLJ: A
+Julia package for composable machine learning}. \emph{Journal of Open
+Source Software}, 5, 2704.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-CaraDonna2017IntRew}{}}%
+CaraDonna, P.J., Petry, W.K., Brennan, R.M., Cunningham, J.L.,
+Bronstein, J.L., Waser, N.M., \emph{et al.} (2017).
+\href{https://doi.org/10.1111/ele.12740}{Interaction rewiring and the
+rapid turnover of plantpollinator networks}. \emph{Ecology Letters}, 20,
+385--394.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Carlson2020WhaWou}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Connor2017UsiNul}{}}%
-Connor, N., Barberán, A. \& Clauset, A. (2017).
-\href{https://doi.org/10.1371/journal.pone.0176751}{Using null models to
-infer microbial co-occurrence networks}. \emph{PLOS ONE}, 12, e0176751.
+\leavevmode\vadjust pre{\hypertarget{ref-Closs1994SpaTem}{}}%
+Closs, G.P. \& Lake, P.S. (1994).
+\href{https://doi.org/10.2307/2937053}{Spatial and Temporal Variation in
+the Structure of an Intermittent-Stream Food Web}. \emph{Ecological
+Monographs}, 64, 1--21.
 
@@
 Giacomuzzo, E. \& Jordán, F. (2021).
-\emph{\href{https://doi.org/10.1101/2021.04.18.440319}{Food web
-aggregation: Effects on key positions}} (Preprint). Ecology.
+\href{https://doi.org/10.1111/oik.08541}{Food web aggregation: Effects
+on key positions}. \emph{Oikos}, 130, 2170--2181.
 
@@
 \href{https://doi.org/10.1086/674445}{A Tale of Two Phylogenies:
-Comparative Analyses of Ecological Interactions}. \emph{The American
+Comparative Analyses of Ecological Interactions.} \emph{The American
 Naturalist}, 183, 174--187.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Havens1992ScaStr}{}}%
+Havens, K. (1992).
+\href{https://doi.org/10.1126/science.257.5073.1107}{Scale and Structure
+in Natural Food Webs}. \emph{Science}, 257, 1107--1109.
 
@@
 \href{https://doi.org/10.1101/2021.07.06.451319}{Bayesian estimation of
-population size and overlap from random subsamples}. \emph{bioRxiv},
-2021.07.06.451319.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jordano2016ChaEco}{}}%
-Jordano, P. (2016a).
-\href{https://doi.org/10.1371/journal.pbio.1002559}{Chasing Ecological
-Interactions}. \emph{PLOS Biology}, 14, e1002559.
+population size and overlap from random subsamples}.
 
 \leavevmode\vadjust pre{\hypertarget{ref-Jordano2016SamNet}{}}%
-Jordano, P. (2016b).
+Jordano, P. (2016).
 \href{https://doi.org/10.1111/1365-2435.12763}{Sampling networks of
-ecological interactions}. \emph{Functional Ecology}.
+ecological interactions}. \emph{Functional Ecology}, 30, 1883--1893.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Khoshraftar2022SurGra}{}}%
+Khoshraftar, S. \& An, A. (2022).
+\href{https://doi.org/10.48550/arXiv.2204.01855}{A Survey on Graph
+Representation Learning Methods}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Koleff2003MeaBet}{}}%
+Koleff, P., Gaston, K.J. \& Lennon, J.J. (2003).
+\href{https://doi.org/10.1046/j.1365-2656.2003.00710.x}{Measuring beta
+diversity for presenceabsence data}. \emph{Journal of Animal Ecology},
+72, 367--382.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kopelke2017FooStr}{}}%
+Kopelke, J.-P., Nyman, T., Cazelles, K., Gravel, D., Vissault, S. \&
+Roslin, T. (2017). \href{https://doi.org/10.1002/ecy.1832}{Food-web
+structure of willow-galling sawflies and their natural enemies across
+Europe}. \emph{Ecology}, 98, 1730--1730.
+
 \leavevmode\vadjust pre{\hypertarget{ref-MacDonald2020RevLin}{}}%
@@
 Makiola, A., Compson, Z.G., Baird, D.J., Barnes, M.A., Boerlijst, S.P.,
-Bouchez, A., \emph{et al.} (2020).
-\href{https://doi.org/10.3389/fenvs.2019.00197}{Key Questions for
-Next-Generation Biomonitoring}. \emph{Frontiers in Environmental
-Science}, 7.
+Bouchez, A., \emph{et al.} (2020). Key Questions for Next-Generation
+Biomonitoring. \emph{Frontiers in Environmental Science}, 7.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Nielsen2007EcoNet}{}}%
-Nielsen, A. \& Bascompte, J. (2007).
-\href{https://doi.org/10.1111/j.1365-2745.2007.01271.x}{Ecological
-networks, nestedness and sampling effort}. \emph{Journal of Ecology},
-95, 1134--1141.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Paine1988RoaMap}{}}%
-Paine, R.T. (1988). \href{https://doi.org/10.2307/1941141}{Road Maps of
-Interactions or Grist for Theoretical Development?} \emph{Ecology}, 69,
-1648--1654.
+\leavevmode\vadjust pre{\hypertarget{ref-Niedballa2019AssAna}{}}%
+Niedballa, J., Wilting, A., Sollmann, R., Hofer, H. \& Courtiol, A.
+(2019). \href{https://doi.org/10.1002/rse2.107}{Assessing analytical
+methods for detecting spatiotemporal interactions between species from
+camera trapping data}. \emph{Remote Sensing in Ecology and
+Conservation}, 5, 272--285.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Poisot2022GuiPre}{}}%
+Poisot, T. (2022).
+\href{https://doi.org/10.32942/osf.io/aty7n}{Guidelines for the
+prediction of species interactions through binary classification}.
 
@@
 Poisot, T., Bergeron, G., Cazelles, K., Dallas, T., Gravel, D.,
-MacDonald, A., \emph{et al.} (2021a).
+MacDonald, A., \emph{et al.} (2021).
 \href{https://doi.org/10.1111/jbi.14127}{Global knowledge gaps in
-species interaction networks data}. \emph{Journal of Biogeography},
-jbi.14127.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Poisot2021ImpMam}{}}%
+species interaction networks data}. \emph{Journal of Biogeography}, 48,
+1552--1563.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Poisot2022NetEmb}{}}%
 Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M.J., Becker, D.J.,
-Albery, G.F., \emph{et al.} (2021b).
-\href{https://arxiv.org/abs/2105.14973}{Imputing the mammalian virome
-with linear filtering and singular value decomposition}.
-\emph{arXiv:2105.14973 {[}q-bio{]}}.
+Brierly, L., \emph{et al.} (2022).
+\href{https://doi.org/10.48550/arXiv.2105.14973}{Network embedding
+unveils the hidden interactions in the mammalian virome}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Resasco2021PlaPol}{}}%
-Resasco, J., Chacoff, N.P. \& Vázquez, D.P. (2021).
-\href{https://doi.org/10.1002/ecy.3359}{Plantpollinator interactions
-between generalists persist over time and space}. \emph{Ecology}, 102,
-e03359.
+\leavevmode\vadjust pre{\hypertarget{ref-Ponisio2017OppAtt}{}}%
+Ponisio, L.C., Gaiarsa, M.P. \& Kremen, C. (2017).
+\href{https://doi.org/10.1111/ele.12821}{Opportunistic attachment
+assembles plantpollinator networks}. \emph{Ecology Letters}, 20,
+1261--1272.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Schwarz2020TemSca}{}}%
-Schwarz, B., Vázquez, D.P., CaraDonna, P.J., Knight, T.M., Benadi, G.,
-Dormann, C.F., \emph{et al.} (2020).
-\href{https://doi.org/10.1111/oik.07303}{Temporal scale-dependence of
-plantpollinator networks}. \emph{Oikos}, 129, 1289--1302.
+\leavevmode\vadjust pre{\hypertarget{ref-Song2022GenDri}{}}%
+Song, C., Simmons, B.I., Fortin, M.-J. \& Gonzalez, A. (2022).
+\href{https://doi.org/10.1371/journal.pcbi.1010302}{Generalism drives
+abundance: A computational causal discovery approach}. \emph{PLOS
+Computational Biology}, 18, e1010302.
 
@@
 advances in biodiversity monitoring: Applicability, opportunities and
-challenges}. \emph{Current Opinion in Environmental Sustainability}, 45,
-36--41.
+challenges}. \emph{Current Opinion in Environmental Sustainability},
+Open Issue 2020 Part A: Technology Innovations and Environmental
+Sustainability in the Anthropocene, 45, 36--41.
 
@@
 Desjardins-Proulx, P., \emph{et al.} (2021).
-\emph{\href{https://doi.org/10.32942/osf.io/eu7k3}{A Roadmap Toward
-Predicting Species Interaction Networks (Across Space and Time)}}
-(Preprint). EcoEvoRxiv.
+\href{https://doi.org/10.1098/rstb.2021.0063}{A roadmap towards
+predicting species interaction networks (across space and time)}.
+\emph{Philosophical Transactions of the Royal Society B: Biological
+Sciences}, 376, 20210063.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Williams2002TwoDeg}{}}%
-Williams, R.J., Berlow, E.L., Dunne, J.A., Barabasi, A.-L. \& Martinez,
-N.D. (2002). \href{https://doi.org/10.1073/pnas.192448799}{Two degrees
-of separation in complex food webs}. \emph{Proceedings of the National
-Academy of Sciences}, 99, 12913--12916.
-
 \leavevmode\vadjust pre{\hypertarget{ref-Williams2000SimRul}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Willott2001SpeAcc}{}}%
-Willott, S.J. (2001).
+Willott, S.j. (2001).
 \href{https://doi.org/10.1046/j.1365-2664.2001.00589.x}{Species
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Zhang2019GraCon}{}}%
+Zhang, S., Tong, H., Xu, J. \& Maciejewski, R. (2019).
+\href{https://doi.org/10.1186/s40649-019-0069-y}{Graph convolutional
+networks: A comprehensive review}. \emph{Computational Social Networks},
+6, 11.
+
 \end{CSLReferences}

### 2022-10-14 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@230beaa0261730b22ad4cadb32c74b1331cb84d4 🚀

@@
 {\small{\bfseries Keywords}:\par
-pandoc\\pandoc-crossref\\github actions\\}
+community ecology\\network ecology\\computational ecology\\species
+interactions\\spatial sampling\\simulation\\}
 }

### 2022-10-15 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@c15bddd0648f41e9bd3fbfdd2cd45cbc6bf5b682 🚀

@@
 \textbf{Correspondance to:}\\
-Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\
+Michael D. Catchen --- \texttt{michael.catchen@mcgill.ca}\\
 
@@
 (Jordano 2016). Over the past few decades biodiversity data has become
-increasingly available--for example, remote-sensing has enabled
+increasingly available---for example, remote-sensing has enabled
 collection of data on spatial scales and resolutions previously
-unimaginable, and improved in-situ sensing (Stephenson 2020), while the
-adoption of open data practices (Kenall \emph{et al.} 2014) have
-substantially increased the amount of data available to ecologists.
-Still, widespread data about species interactions remains elusive
-(Poisot \emph{et al.} 2021). Observing an interaction between two
-species often requires human observation because remote sampling methods
-can primarily detect co-occurrence (Niedballa \emph{et al.} 2019), and
-this itself is not necessarily indicative of an interaction (Blanchet
-\emph{et al.} 2020). This constraint induces biases on species
-interaction data subject to the spatial and temporal scales that current
-observation methods can feasibly sample. This is further compounded by
-semantic confusion around the word ``interaction''---for example one
-could consider competition a form of species interaction, even though
-this is marked by a lack of co-occurrence between species, unlike other
-types of interactions, like trophism or pollination, which require both
-species to be together at the same place and time. Here we define
-interaction in the latter sense, where two species have fitness
-consequences on one-another if they are in the sample place at the same
-time. Further we only consider direct (not higher-order) interactions.
-
-The importance of sampling effort and its impact on resulting ecological
-data has produced a rich body of literature. The recorded number of
-species in a dataset or sample depends on the total number of
+unimaginable (Stephenson 2020), while the adoption of open data
+practices (Kenall \emph{et al.} 2014) have substantially increased the
+amount of data available to ecologists. Still, widespread data about
+species interactions remains elusive (Poisot \emph{et al.} 2021).
+Observing an interaction between two species often requires human
+observation because remote sampling methods can primarily detect
+co-occurrence (but see Niedballa \emph{et al.} (2019)), and this itself
+is not necessarily indicative of an interaction (Blanchet \emph{et al.}
+2020). This constraint induces biases on species interaction data
+subject to the spatial and temporal scales that current observation
+methods can feasibly sample. This is further compounded by semantic
+confusion around the word ``interaction''---for example one might
+consider competition a type of species interaction, even though it is
+marked by a lack of co-occurrence between species, unlike other types of
+interactions, like trophism or pollination, which require both species
+to be together at the same place and time. We define interaction in the
+latter sense, where two species have fitness consequences on one-another
+if they are in the sample place at the same time. In addition, here we
+only consider direct (not higher-order) interactions.
+
+The importance of \emph{sampling effort} and its impact on resulting
+ecological data has produced a rich body of literature. The recorded
+number of species in a dataset or sample depends on the total number of
 observations (Walther \emph{et al.} 1995; Willott 2001)---as do
@@
 taxonomic scales) could lead any empirical set of observations to
-inadequately reflect the reality of how species interact
-{[}Paine1988RoaMap{]} or the structure of the network as a whole
-{[}McLeod2021SamAsy{]}. Martinez \emph{et al.} (1999) showed that in a
-plant-endophyte trophic network, network connectance is robust to
-sampling effort, but this was done in the context of a system for which
-observation of 62,000 total interactions derived from 164,000
-plant-stems was feasible. In some systems (e.g.~megafauna food-webs)
-this many observations is either impractical or infeasible due to the
-absolute abundance of the species in question.
+inadequately reflect the reality of how species interact (Paine 1988) or
+the structure of the network as a whole (McLeod \emph{et al.} 2021).
+Martinez \emph{et al.} (1999) showed that in a plant-endophyte trophic
+network, network connectance is robust to sampling effort, but this was
+done in the context of a system for which observation of 62,000 total
+interactions derived from 164,000 plant-stems was feasible. In some
+systems (e.g.~megafauna food-webs) this many observations is either
+impractical or infeasible due to the absolute abundance of the species
+in question.
 
@@
 species misidentification probability), but not at all confident that a
-pair of species do not interact if we have no record of those species
-observed together. In other words, it is difficult to distinguish
-true-negatives (two species never interact) from false-negatives (two
-species interact in some capacity, but we do not have a record of it).
-For a concrete example of this phenomenon, see Figure Concept. Because
-even the most highly sampled systems will still contain missing
-interactions, there is increasing interest in combining species-level
-data (e.g. traits, abundance, range, phylogenetic relatedness, etc.) to
-build predictive models of interactions (Strydom \emph{et al.} 2021).
-However, the noise of false-negatives could impact the efficacy of our
-predictive models and have practical consequences for answering
-questions about interactions (de Aguiar \emph{et al.} 2019). This data
-constraint is amplified as the interaction data we have is
-geographically biased toward the usual suspects (Poisot \emph{et al.}
-2021). We therefore need a systematic approach to assessing these biases
-in the observation process and the consequences this has for our
-understanding of interaction networks
+pair of species \emph{do not} interact if we have no record of those
+species observed together. In other words, it is difficult to
+distinguish \emph{true-negatives} (two species never interact) from
+\emph{false-negatives} (two species interact sometimes, but we do not
+have a record of it). For a concrete example of a false-negative in a
+food web, see fig.~\ref{fig:concept}. Because even the most highly
+sampled systems will still contain missing interactions, there is
+increasing interest in combining species-level data (e.g.~traits,
+abundance, range, phylogenetic relatedness, etc.) to build models to
+predict interactions between species we haven't observed together before
+(Strydom \emph{et al.} 2021). However, the noise of false-negatives
+could impact the efficacy of our predictive models and have practical
+consequences for answering questions about interactions (de Aguiar
+\emph{et al.} 2019). This data constraint is amplified as the
+interaction data we have is geographically biased toward the usual
+suspects (Poisot \emph{et al.} 2021). We therefore need a systematic
+approach to assessing these biases in the observation process and the
+consequences this has for our understanding of interaction networks.
 
@@
 with meaningful interaction strength, but this is not necessarily the
-case Blanchet \emph{et al.} (2020)---a true ``non-interaction'' would
+case (Blanchet \emph{et al.} 2020)---a true ``non-interaction'' would
 require that neither of two species, regardless of whether they
@@
 although co-occurrence is not directly indicative of an interaction, it
-is a precondition for interactions, and therefore observations of
+is a precondition for an interaction. Therefore observations of
 ``non-interactions'' between pairs of species that are outside of the
@@
 seen). We show that positive associations in co-occurrence data can
-increase realized probability of false negatives, and demonstrate these
+increase realized probability of false-negatives, and demonstrate these
 positive associations are ubiquitous in network datasets. We conclude by
@@
 We start with a naive model of interaction detection: we assume that
-every interacting pair of species is incorrectly observed as a
+every interacting pair of species is incorrectly observed as
 not-interacting with an independent and fixed probability, which we
 denote pfn and subsequently refer to as the False-Negative Rate (FNR).
-If we observe the same species not-interacting N times, then the
+If we observe the same species not-interacting \(N\) times, then the
 probability of a true-negative (denoted \(p_{tn}\)) is given by
@@
 
-From Figure 1(A) it is clear that the more often we see two species
-co-occurring, but not interacting, the more likely the interaction is a
-true negative. This has several practical consequences: first it means
-negatives taken outside the overlap of the range of each species aren't
-informative. Second, we can use this relation to compute the expected
-number of total observations needed to obtain a ``goal'' number of
-observations of a particular pair of species (Figure 1(B)). As an
-example, if we hypothesize that \(A\) and \(B\) do not interact, and we
-want to see species \(A\) and \(B\) both co-occurring and not
-interacting 10 times to be confident this is a true negative, then we
-need an expected 1000 observations of all species if the relative
-abundances of \(A\) and \(B\) are both \(0.1\).
+From fig.~\ref{fig:geometric}(A) it is clear that the more often we see
+two species co-occurring, but not interacting, the more likely the
+interaction is a true negative. This has several practical consequences:
+first it means negatives taken outside the overlap of the range of each
+species aren't informative. Second, we can use this relation to compute
+the expected number of total observations needed to obtain a ``goal''
+number of observations of a particular pair of species
+(fig.~\ref{fig:geometric}(B)). As an example, if we hypothesize that
+\(A\) and \(B\) do not interact, and we want to see species \(A\) and
+\(B\) both co-occurring and not interacting 10 times to be confident
+this is a true negative, then we need an expected 1000 observations of
+all species if the relative abundances of \(A\) and \(B\) are both
+\(0.1\).
 
@@
 
-We now show that the realized false-negative rate of species
-interactions changes drastically with sampling effort due to the
-intrinsic variation of the abundance of individuals of each species
-within a community. We do this by simulating the process of observation
-of species interactions, applied both to 243 empirical food webs from
-the Mangal database (Banville \emph{et al.} 2021) as well as random
+We now show that the realized FNR changes drastically with sampling
+effort due to the intrinsic variation of the abundance of individuals of
+each species within a community. We do this by simulating the process of
+observation of species interactions, applied both to 243 empirical food
+webs from the Mangal database (Banville \emph{et al.} 2021) and random
 food-webs generated using the niche model (Williams \& Martinez 2000), a
@@
 observation assumes each observed species is drawn from the distribution
-in proportion to each species' abundance at that place and time.
-
-The abundance distribution of a community can be reasonably-well
-described by a log-normal distribution (Volkov \emph{et al.} 2003). In
-addition to the log-normal distribution, we also tested the case where
-the abundance distribution is derived from power-law scaling
-\(Z^{(log(T_i)-1)}\) where \(T_i\) is the trophic level of species \(i\)
-and \(Z\) is a scaling coefficient (Savage \emph{et al.} 2004), which
-yields the same qualitative behavior. The practical consequence of
-abundance distributions spanning many orders of magnitude of abundance
-is that observing two ``rare'' species interacting requires two low
-probability events: observing two rare species at the same time.
+in proportion to each species' abundance at that place and time. The
+abundance distribution of a community can be reasonably-well described
+by a log-normal distribution (Volkov \emph{et al.} 2003). In addition to
+the log-normal distribution, we also tested the case where the abundance
+distribution is derived from power-law scaling \(Z^{(log(T_i)-1)}\)
+where \(T_i\) is the trophic level of species \(i\) and \(Z\) is a
+scaling coefficient (Savage \emph{et al.} 2004), which yields the same
+qualitative behavior. The practical consequence of abundance
+distributions spanning many orders of magnitude of abundance is that
+observing two ``rare'' species interacting requires two low probability
+events: observing two rare species at the same time.
 
@@
 where the MAP estimate of \((\mu, \phi)\) applied to Mangal data from
-{[}{]} MacDonald et al.~2020 is \((\mu=0.086, \phi=24.3)\). All
+(MacDonald \emph{et al.} 2020) is \((\mu=0.086, \phi=24.3)\). All
 simulations were done with 500 independent replicates per unique number
-of observations n.~All analyses presented here are done in Julia v1.8
-(Bezanson \emph{et al.} 2015) using both EcologicalNetworks.jl v0.5 and
-Mangal.jl v0.4 (Banville \emph{et al.} 2021) and are hosted at
+of observations \(n\). All analyses presented here are done in Julia
+v1.8 (Bezanson \emph{et al.} 2015) using both EcologicalNetworks.jl v0.5
+and Mangal.jl v0.4 (Banville \emph{et al.} 2021) and are hosted at
 (GITHUB\_LINK\_TODO). Note that the empirical data, for the reasons
@@
 meant by ``acceptable'' FNR? This raises the question: does a shifting
-FNR lead to rapid transitions in the our ability inference and
-predictions about the structure and dynamics of networks, or does it
-produce a roughly linear decay in model efficacy? We explore this in the
-next section.
+FNR lead to rapid transitions in our ability inference and predictions
+about the structure and dynamics of networks, or does it produce a
+roughly linear decay in model efficacy? We explore this in the next
+section.
 
@@
 of observing a false negative can be higher if there is some positive
-association in the occurrence of species \(A\) and \(B\).If we denote
+association in the occurrence of species \(A\) and \(B\). If we denote
 the probability that we observe the co-occurrence of two species \(A\)
@@
 probability of a false negative as \(P(AB) \to P(AB) \gg P(A)P(B)\).
-However, this still does not consider variation in species abundancein
+However, this still does not consider variation in species abundance in
 space and time (Poisot \emph{et al.} 2015). If positive or negative
@@
 \caption{The difference between joint-probability of co-occurrence
-(P(AB)) and expected probability of co-occurrence under independence
-(P(A)P(B)) for interacting species for each dataset. The red-dashed line
-indicates 0. Each histogram represents a density, meaning the area of
-the entire curve sums to 1. The continuous density estimate (computed
+(\(P(AB)\)) and expected probability of co-occurrence under independence
+(\(P(A)P(B)\)) for interacting species for each dataset. The red-dashed
+line indicates 0. Each histogram represents a density, meaning the area
+of the entire curve sums to 1. The continuous density estimate (computed
 using local smoothing) is shown in grey. The p-value on each plot is the
-result of a one-sided T-test comparing the mean of each distribution to
+result of a one-sided t-test comparing the mean of each distribution to
 0.}\label{fig:mangal}
@@
 \includegraphics{./figures/fig3.png}
-\caption{(A) The area-under the receiver-operator curve (ROC-AUC). (B)
-The area-under the precision-recall curve (PR-AUC; right) for each
+\caption{(A) The area-under the receiver-operator curve (ROC-AUC) and
+(B) The area-under the precision-recall curve (PR-AUC; right) for each
 different predictive model (colors/shapes) across a spectrum of the
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-McLeod2021SamAsy}{}}%
+McLeod, A., Leroux, S.J., Gravel, D., Chu, C., Cirtwill, A.R., Fortin,
+M.-J., \emph{et al.} (2021).
+\href{https://doi.org/10.1111/oik.08650}{Sampling and asymptotic network
+properties of spatial multi-trophic networks}. \emph{Oikos}, 130,
+2250--2259.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Moore2016OptEco}{}}%
@@
 Conservation}, 5, 272--285.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Paine1988RoaMap}{}}%
+Paine, R.T. (1988). \href{https://doi.org/10.2307/1941141}{Road Maps of
+Interactions or Grist for Theoretical Development?} \emph{Ecology}, 69,
+1648--1654.
 

### 2022-10-15 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@c15bddd0648f41e9bd3fbfdd2cd45cbc6bf5b682 🚀

@@
 \textbf{Correspondance to:}\\
-Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\
+Michael D. Catchen --- \texttt{michael.catchen@mcgill.ca}\\
 }

### 2022-10-15 .assets/scripts/affiliations.jl
🧪

@@ -1,67 +1,0 @@
-import JSON
-
-# Read the metadata
-metadata = JSON.parsefile(joinpath(pwd(), "metadata.json"))
-
-authors = metadata["authors"]
-affiliation_to_number = Dict{String, String}()
-
-for author in authors
-    affiliations = author["affiliations"]
-    for affiliation in affiliations
-        if ~haskey(affiliation_to_number, affiliation)
-            affiliation_to_number[affiliation] = "$(length(affiliation_to_number) + 1)"
-        end
-    end
-end
-
-for author in authors
-    author["affilcode"] =
-        sort(
-            String[
-                "$(affiliation_to_number[affiliation])" for affiliation in author["affiliations"]
-            ],
-        )
-    delete!(author, "affiliations")
-end
-
-affiliations = Dict{String, Any}()
-affiliations["authors"] = authors
-affiliations["institutions"] = []
-while ~isempty(affiliation_to_number)
-    id, idx = findmin(collect(values(affiliation_to_number)))
-    name = collect(keys(affiliation_to_number))[idx]
-    delete!(affiliation_to_number, name)
-    push!(affiliations["institutions"], Dict(["id" => id, "name" => name]))
-end
-
-affiliations["metadata"] = Dict()
-affiliations["metadata"]["corresponding"] = []
-
-add_equal_sign = true
-for author in affiliations["authors"]
-    if haskey(author, "status")
-        if "equal" in author["status"]
-            push!(author["affilcode"], "‡")
-            if add_equal_sign
-                affiliations["metadata"]["equalcontributions"] =
-                    Dict(["id" => "‡", "name" => "Equal contributions"])
-                global add_equal_sign = false
-            end
-        end
-        if "corresponding" in author["status"]
-            push!(affiliations["metadata"]["corresponding"],
-                Dict([
-                    "given" => author["givennames"],
-                    "family" => author["familyname"],
-                    "email" => author["email"],
-                ]),
-            )
-        end
-    end
-end
-
-# Write the file
-open("affiliations.json", "w") do json_file
-    return JSON.print(json_file, affiliations, 4)
-end

### 2022-10-15 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@80920980ebd5187ab667cfd01f41e41cfcdd9132 🚀

@@
 %
-\,\textsuperscript{,}\quad %
+\,\textsuperscript{1,2}\quad %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
 %
-\,\textsuperscript{,}\quad %
+\,\textsuperscript{3,2}\quad %
 \href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
 %
-\,\textsuperscript{,}\quad %
+\,\textsuperscript{1,2}\quad %
 \href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
 %
-\,\textsuperscript{,}
+\,\textsuperscript{1,2}
 
@@
 \vfill
+Ecosystems are composed of networks of interacting species. These
+interactions allow communities of species to persist through time
+through both neutral and adaptive processes. Still a robust
+understanding of, and ability to predict and forecast interactions among
+species and their consequences for network structure remains elusive.
+This knowledge-gap is largely driven by a shortfall of data---although
+species occurrence data has rapidly increased in the last decade,
+species interaction data has not kept pace, largely due to the intrinsic
+difficulty and effort required to sample interactions. These sampling
+challenges bias data and hinder inferences about the structure and
+dynamics of interactions networks. Here, we demonstrate the realized
+false-negative rate (the percentage of species that actually interact
+but for which we do not yet have a record) can be quite high, even in
+thoroughly sampled systems, due to the intrinsic variation in abundances
+across species in a community. We demonstrate how a null model of
+occurrence detection can be used to estimate the false-negative rate in
+a given dataset. One hypothesis is that interactions between ``rare''
+species are themselves rare because these species are less likely to
+encounter one-another than species of higher relative abundance.
+However, we demonstrate that across several datasets of spatial or
+temporally replicated networks, there are positive associations that
+suggest these interactions actually exist but just are not observed.
+Finally, we assess how false negatives influence various models of
+network prediction, and recommend directly accounting for observation
+error in predictive models. We conclude by discussing how the
+understanding of false-negatives can inform how we design monitoring
+schemes for species interactions.
 
@@
 \hypertarget{tbl:id}{}
-\begin{longtable}[]{@{}
-  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.3182}}
-  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.1705}}
-  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0568}}
-  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0568}}
-  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}
-  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}
-  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}
-  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}
-  >{\centering\arraybackslash}p{(\columnwidth - 16\tabcolsep) * \real{0.0795}}@{}}
+\begin{longtable}[]{@{}ccccccccc@{}}
 \caption{\label{tbl:id}This table describes the datasets used in the
@@
 2003)}\tabularnewline
-\toprule()
-\begin{minipage}[b]{\linewidth}\centering
-Network
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Type
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\(N\)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\(S\)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\(C\)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\(\bar{S}\)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\(\bar{C}\)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\(\bar{\beta}_{OS}\)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\(\bar{\beta}_{WN}\)
-\end{minipage} \\
-\midrule()
+\toprule
+Network & Type & \(N\) & \(S\) & \(C\) & \(\bar{S}\) & \(\bar{C}\) &
+\(\bar{\beta}_{OS}\) & \(\bar{\beta}_{WN}\)\tabularnewline
+\midrule
 \endfirsthead
-\toprule()
-\begin{minipage}[b]{\linewidth}\centering
-Network
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-Type
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\(N\)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\(S\)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\(C\)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\(\bar{S}\)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\(\bar{C}\)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\(\bar{\beta}_{OS}\)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\(\bar{\beta}_{WN}\)
-\end{minipage} \\
-\midrule()
+\toprule
+Network & Type & \(N\) & \(S\) & \(C\) & \(\bar{S}\) & \(\bar{C}\) &
+\(\bar{\beta}_{OS}\) & \(\bar{\beta}_{WN}\)\tabularnewline
+\midrule
 \endhead
 Kopelke \emph{et al.} (2017) & Food Web & 100 & 98 & 0.037 & 7.87 &
-0.142 & 1.383 & 1.972 \\
+0.142 & 1.383 & 1.972\tabularnewline
 Thompson \& Townsend (2000) & Food Web & 18 & 566 & 0.014 & 80.67 &
-0.049 & 1.617 & 1.594 \\
+0.049 & 1.617 & 1.594\tabularnewline
 Havens (1992) & Food Web & 50 & 188 & 0.065 & 33.58 & 0.099 & 1.468 &
-1.881 \\
+1.881\tabularnewline
 Ponisio \emph{et al.} (2017) & Pollinator & 100 & 226 & 0.079 & 23.0 &
-0.056 & 1.436 & 1.870 \\
+0.056 & 1.436 & 1.870\tabularnewline
 Hadfield \emph{et al.} (2014) & Host-Parasite & 51 & 327 & 0.085 & 32.71
-& 0.337 & 1.477 & 1.952 \\
+& 0.337 & 1.477 & 1.952\tabularnewline
 Closs \& Lake (1994) & Food Web & 12 & 61 & 0.14 & 29.09 & 0.080 & 1.736
-& 1.864 \\
+& 1.864\tabularnewline
 CaraDonna \emph{et al.} (2017) & Pollinator & 86 & 122 & 0.18 & 21.42 &
-0.312 & 1.527 & 1.907 \\
-\bottomrule()
+0.312 & 1.527 & 1.907\tabularnewline
+\bottomrule
 \end{longtable}
@@
 stability of a network could be prone to error if the observed network
-is not sampled ``enough''. What exactly ``enough'' means is then
+is not sampled ``enough.'' What exactly ``enough'' means is then
 specific to the application, and should be assessed via methods like
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Banville2021ManJl}{}}%
-Banville, F., Vissault, S. \& Poisot, T. (2021).
-\href{https://doi.org/10.21105/joss.02721}{Mangal.jl and
+\leavevmode\hypertarget{ref-Banville2021ManJl}{}%
+Banville, F., Vissault, S. \& Poisot, T. (2021). Mangal.jl and
 EcologicalNetworks.jl: Two complementary packages for analyzing
-ecological networks in Julia}. \emph{Journal of Open Source Software},
-6, 2721.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bascompte2007PlaMut}{}}%
-Bascompte, J. \& Jordano, P. (2007).
-\href{https://doi.org/10.1146/annurev.ecolsys.38.091206.095818}{Plant-Animal
-Mutualistic Networks: The Architecture of Biodiversity}. \emph{Annual
-Review of Ecology, Evolution, and Systematics}, 38, 567--593.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Becker2021OptPre}{}}%
+ecological networks in Julia. \emph{Journal of Open Source Software}, 6,
+2721.
+
+\leavevmode\hypertarget{ref-Bascompte2007PlaMut}{}%
+Bascompte, J. \& Jordano, P. (2007). Plant-Animal Mutualistic Networks:
+The Architecture of Biodiversity. \emph{Annual Review of Ecology,
+Evolution, and Systematics}, 38, 567--593.
+
+\leavevmode\hypertarget{ref-Becker2021OptPre}{}%
 Becker, D.J., Albery, G.F., Sjodin, A.R., Poisot, T., Bergner, L.M.,
-Dallas, T.A., \emph{et al.} (2021).
-\href{https://doi.org/10.1101/2020.05.22.111344}{Optimizing predictive
-models to prioritize viral discovery in zoonotic reservoirs}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Bezanson2015JulFre}{}}%
-Bezanson, J., Edelman, A., Karpinski, S. \& Shah, V.B. (2015).
-\href{https://doi.org/10.48550/arXiv.1411.1607}{Julia: A Fresh Approach
-to Numerical Computing}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Blanchet2020CooNot}{}}%
-Blanchet, F.G., Cazelles, K. \& Gravel, D. (2020).
-\href{https://doi.org/10.1111/ele.13525}{Co-occurrence is not evidence
-of ecological interactions}. \emph{Ecology Letters}, 23, 1050--1063.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Blaom2020MljJul}{}}%
+Dallas, T.A., \emph{et al.} (2021). Optimizing predictive models to
+prioritize viral discovery in zoonotic reservoirs.
+
+\leavevmode\hypertarget{ref-Bezanson2015JulFre}{}%
+Bezanson, J., Edelman, A., Karpinski, S. \& Shah, V.B. (2015). Julia: A
+Fresh Approach to Numerical Computing.
+
+\leavevmode\hypertarget{ref-Blanchet2020CooNot}{}%
+Blanchet, F.G., Cazelles, K. \& Gravel, D. (2020). Co-occurrence is not
+evidence of ecological interactions. \emph{Ecology Letters}, 23,
+1050--1063.
+
+\leavevmode\hypertarget{ref-Blaom2020MljJul}{}%
 Blaom, A.D., Kiraly, F., Lienart, T., Simillides, Y., Arenas, D. \&
-Vollmer, S.J. (2020). \href{https://doi.org/10.21105/joss.02704}{MLJ: A
-Julia package for composable machine learning}. \emph{Journal of Open
-Source Software}, 5, 2704.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Boakes2015InfSpe}{}}%
-Boakes, E.H., Rout, T.M. \& Collen, B. (2015).
-\href{https://doi.org/10.1111/2041-210X.12365}{Inferring species
-extinction: The use of sighting records}. \emph{Methods in Ecology and
+Vollmer, S.J. (2020). MLJ: A Julia package for composable machine
+learning. \emph{Journal of Open Source Software}, 5, 2704.
+
+\leavevmode\hypertarget{ref-Boakes2015InfSpe}{}%
+Boakes, E.H., Rout, T.M. \& Collen, B. (2015). Inferring species
+extinction: The use of sighting records. \emph{Methods in Ecology and
 Evolution}, 6, 678--687.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Canard2012EmeStr}{}}%
+\leavevmode\hypertarget{ref-Canard2012EmeStr}{}%
 Canard, E., Mouquet, N., Marescot, L., Gaston, K.J., Gravel, D. \&
-Mouillot, D. (2012).
-\href{https://doi.org/10.1371/journal.pone.0038295}{Emergence of
-Structural Patterns in Neutral Trophic Networks}. \emph{PLOS ONE}, 7,
-e38295.
-
-\leavevmode\vadjust pre{\hypertarget{ref-CaraDonna2017IntRew}{}}%
+Mouillot, D. (2012). Emergence of Structural Patterns in Neutral Trophic
+Networks. \emph{PLOS ONE}, 7, e38295.
+
+\leavevmode\hypertarget{ref-CaraDonna2017IntRew}{}%
 CaraDonna, P.J., Petry, W.K., Brennan, R.M., Cunningham, J.L.,
-Bronstein, J.L., Waser, N.M., \emph{et al.} (2017).
-\href{https://doi.org/10.1111/ele.12740}{Interaction rewiring and the
-rapid turnover of plantpollinator networks}. \emph{Ecology Letters}, 20,
-385--394.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Carlson2020WhaWou}{}}%
+Bronstein, J.L., Waser, N.M., \emph{et al.} (2017). Interaction rewiring
+and the rapid turnover of plantpollinator networks. \emph{Ecology
+Letters}, 20, 385--394.
+
+\leavevmode\hypertarget{ref-Carlson2020WhaWou}{}%
 Carlson, C.J., Dallas, T.A., Alexander, L.W., Phelan, A.L. \& Phillips,
-A.J. (2020). \href{https://doi.org/10.1098/rspb.2020.1841}{What would it
-take to describe the global diversity of parasites?} \emph{Proceedings
-of the Royal Society B: Biological Sciences}, 287, 20201841.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Cazelles2016TheSpe}{}}%
-Cazelles, K., Araújo, M.B., Mouquet, N. \& Gravel, D. (2016).
-\href{https://doi.org/10.1007/s12080-015-0281-9}{A theory for species
-co-occurrence in interaction networks}. \emph{Theoretical Ecology}, 9,
-39--48.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Closs1994SpaTem}{}}%
-Closs, G.P. \& Lake, P.S. (1994).
-\href{https://doi.org/10.2307/2937053}{Spatial and Temporal Variation in
-the Structure of an Intermittent-Stream Food Web}. \emph{Ecological
+A.J. (2020). What would it take to describe the global diversity of
+parasites? \emph{Proceedings of the Royal Society B: Biological
+Sciences}, 287, 20201841.
+
+\leavevmode\hypertarget{ref-Cazelles2016TheSpe}{}%
+Cazelles, K., Araújo, M.B., Mouquet, N. \& Gravel, D. (2016). A theory
+for species co-occurrence in interaction networks. \emph{Theoretical
+Ecology}, 9, 39--48.
+
+\leavevmode\hypertarget{ref-Closs1994SpaTem}{}%
+Closs, G.P. \& Lake, P.S. (1994). Spatial and Temporal Variation in the
+Structure of an Intermittent-Stream Food Web. \emph{Ecological
 Monographs}, 64, 1--21.
 
-\leavevmode\vadjust pre{\hypertarget{ref-deAguiar2019RevBia}{}}%
+\leavevmode\hypertarget{ref-deAguiar2019RevBia}{}%
 de Aguiar, M.A.M., Newman, E.A., Pires, M.M., Yeakel, J.D., Boettiger,
-C., Burkle, L.A., \emph{et al.} (2019).
-\href{https://doi.org/10.7717/peerj.7566}{Revealing biases in the
-sampling of ecological interaction networks}. \emph{PeerJ}, 7, e7566.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gauzens2013FooAgg}{}}%
+C., Burkle, L.A., \emph{et al.} (2019). Revealing biases in the sampling
+of ecological interaction networks. \emph{PeerJ}, 7, e7566.
+
+\leavevmode\hypertarget{ref-Gauzens2013FooAgg}{}%
 Gauzens, B., Legendre, S., Lazzaro, X. \& Lacroix, G. (2013). Food-web
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Giacomuzzo2021FooWeb}{}}%
-Giacomuzzo, E. \& Jordán, F. (2021).
-\href{https://doi.org/10.1111/oik.08541}{Food web aggregation: Effects
-on key positions}. \emph{Oikos}, 130, 2170--2181.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Griffiths1998SamEff}{}}%
-Griffiths, D. (1998).
-\href{https://doi.org/10.1046/j.1365-2656.1998.00244.x}{Sampling effort,
-regression method, and the shape and slope of sizeabundance relations}.
-\emph{Journal of Animal Ecology}, 67, 795--804.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Hadfield2014TalTwo}{}}%
-Hadfield, J.D., Krasnov, B.R., Poulin, R. \& Nakagawa, S. (2014).
-\href{https://doi.org/10.1086/674445}{A Tale of Two Phylogenies:
-Comparative Analyses of Ecological Interactions.} \emph{The American
-Naturalist}, 183, 174--187.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Havens1992ScaStr}{}}%
-Havens, K. (1992).
-\href{https://doi.org/10.1126/science.257.5073.1107}{Scale and Structure
-in Natural Food Webs}. \emph{Science}, 257, 1107--1109.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Johnson2021BayEst}{}}%
-Johnson, E.K. \& Larremore, D.B. (2021).
-\href{https://doi.org/10.1101/2021.07.06.451319}{Bayesian estimation of
-population size and overlap from random subsamples}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Jordano2016SamNet}{}}%
-Jordano, P. (2016).
-\href{https://doi.org/10.1111/1365-2435.12763}{Sampling networks of
-ecological interactions}. \emph{Functional Ecology}, 30, 1883--1893.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Joseph2020NeuHie}{}}%
-Joseph, M.B. (2020). \href{https://doi.org/10.1111/ele.13462}{Neural
-hierarchical models of ecological populations}. \emph{Ecology Letters},
-23, 734--747.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Kenall2014OpeFut}{}}%
-Kenall, A., Harold, S. \& Foote, C. (2014).
-\href{https://doi.org/10.1186/1471-2148-14-66}{An open future for
-ecological and evolutionary data?} \emph{BMC Evolutionary Biology}, 14,
+\leavevmode\hypertarget{ref-Giacomuzzo2021FooWeb}{}%
+Giacomuzzo, E. \& Jordán, F. (2021). Food web aggregation: Effects on
+key positions. \emph{Oikos}, 130, 2170--2181.
+
+\leavevmode\hypertarget{ref-Griffiths1998SamEff}{}%
+Griffiths, D. (1998). Sampling effort, regression method, and the shape
+and slope of sizeabundance relations. \emph{Journal of Animal Ecology},
+67, 795--804.
+
+\leavevmode\hypertarget{ref-Hadfield2014TalTwo}{}%
+Hadfield, J.D., Krasnov, B.R., Poulin, R. \& Nakagawa, S. (2014). A Tale
+of Two Phylogenies: Comparative Analyses of Ecological Interactions.
+\emph{The American Naturalist}, 183, 174--187.
+
+\leavevmode\hypertarget{ref-Havens1992ScaStr}{}%
+Havens, K. (1992). Scale and Structure in Natural Food Webs.
+\emph{Science}, 257, 1107--1109.
+
+\leavevmode\hypertarget{ref-Johnson2021BayEst}{}%
+Johnson, E.K. \& Larremore, D.B. (2021). Bayesian estimation of
+population size and overlap from random subsamples.
+
+\leavevmode\hypertarget{ref-Jordano2016SamNet}{}%
+Jordano, P. (2016). Sampling networks of ecological interactions.
+\emph{Functional Ecology}, 30, 1883--1893.
+
+\leavevmode\hypertarget{ref-Joseph2020NeuHie}{}%
+Joseph, M.B. (2020). Neural hierarchical models of ecological
+populations. \emph{Ecology Letters}, 23, 734--747.
+
+\leavevmode\hypertarget{ref-Kenall2014OpeFut}{}%
+Kenall, A., Harold, S. \& Foote, C. (2014). An open future for
+ecological and evolutionary data? \emph{BMC Evolutionary Biology}, 14,
 66.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Khoshraftar2022SurGra}{}}%
-Khoshraftar, S. \& An, A. (2022).
-\href{https://doi.org/10.48550/arXiv.2204.01855}{A Survey on Graph
-Representation Learning Methods}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Koleff2003MeaBet}{}}%
-Koleff, P., Gaston, K.J. \& Lennon, J.J. (2003).
-\href{https://doi.org/10.1046/j.1365-2656.2003.00710.x}{Measuring beta
-diversity for presenceabsence data}. \emph{Journal of Animal Ecology},
+\leavevmode\hypertarget{ref-Khoshraftar2022SurGra}{}%
+Khoshraftar, S. \& An, A. (2022). A Survey on Graph Representation
+Learning Methods.
+
+\leavevmode\hypertarget{ref-Koleff2003MeaBet}{}%
+Koleff, P., Gaston, K.J. \& Lennon, J.J. (2003). Measuring beta
+diversity for presenceabsence data. \emph{Journal of Animal Ecology},
 72, 367--382.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kopelke2017FooStr}{}}%
+\leavevmode\hypertarget{ref-Kopelke2017FooStr}{}%
 Kopelke, J.-P., Nyman, T., Cazelles, K., Gravel, D., Vissault, S. \&
-Roslin, T. (2017). \href{https://doi.org/10.1002/ecy.1832}{Food-web
-structure of willow-galling sawflies and their natural enemies across
-Europe}. \emph{Ecology}, 98, 1730--1730.
-
-\leavevmode\vadjust pre{\hypertarget{ref-MacDonald2020RevLin}{}}%
-MacDonald, A.A.M., Banville, F. \& Poisot, T. (2020).
-\href{https://doi.org/10.1016/j.patter.2020.100079}{Revisiting the
-Links-Species Scaling Relationship in Food Webs}. \emph{Patterns}, 1.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Makiola2020KeyQue}{}}%
+Roslin, T. (2017). Food-web structure of willow-galling sawflies and
+their natural enemies across Europe. \emph{Ecology}, 98, 1730--1730.
+
+\leavevmode\hypertarget{ref-MacDonald2020RevLin}{}%
+MacDonald, A.A.M., Banville, F. \& Poisot, T. (2020). Revisiting the
+Links-Species Scaling Relationship in Food Webs. \emph{Patterns}, 1.
+
+\leavevmode\hypertarget{ref-Makiola2020KeyQue}{}%
 Makiola, A., Compson, Z.G., Baird, D.J., Barnes, M.A., Boerlijst, S.P.,
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Martinez1999EffSam}{}}%
+\leavevmode\hypertarget{ref-Martinez1999EffSam}{}%
 Martinez, N.D., Hawkins, B.A., Dawah, H.A. \& Feifarek, B.P. (1999).
-\href{https://doi.org/10.1890/0012-9658(1999)080\%5B1044:EOSEOC\%5D2.0.CO;2}{Effects
-of Sampling Effort on Characterization of Food-Web Structure}.
+Effects of Sampling Effort on Characterization of Food-Web Structure.
 \emph{Ecology}, 80, 1044--1055.
 
-\leavevmode\vadjust pre{\hypertarget{ref-McLeod2021SamAsy}{}}%
+\leavevmode\hypertarget{ref-McLeod2021SamAsy}{}%
 McLeod, A., Leroux, S.J., Gravel, D., Chu, C., Cirtwill, A.R., Fortin,
-M.-J., \emph{et al.} (2021).
-\href{https://doi.org/10.1111/oik.08650}{Sampling and asymptotic network
-properties of spatial multi-trophic networks}. \emph{Oikos}, 130,
-2250--2259.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Moore2016OptEco}{}}%
-Moore, A.L. \& McCarthy, M.A. (2016).
-\href{https://doi.org/10.1111/2041-210X.12564}{Optimizing ecological
-survey effort over space and time}. \emph{Methods in Ecology and
-Evolution}, 7, 891--899.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Niedballa2019AssAna}{}}%
+M.-J., \emph{et al.} (2021). Sampling and asymptotic network properties
+of spatial multi-trophic networks. \emph{Oikos}, 130, 2250--2259.
+
+\leavevmode\hypertarget{ref-Moore2016OptEco}{}%
+Moore, A.L. \& McCarthy, M.A. (2016). Optimizing ecological survey
+effort over space and time. \emph{Methods in Ecology and Evolution}, 7,
+891--899.
+
+\leavevmode\hypertarget{ref-Niedballa2019AssAna}{}%
 Niedballa, J., Wilting, A., Sollmann, R., Hofer, H. \& Courtiol, A.
-(2019). \href{https://doi.org/10.1002/rse2.107}{Assessing analytical
-methods for detecting spatiotemporal interactions between species from
-camera trapping data}. \emph{Remote Sensing in Ecology and
-Conservation}, 5, 272--285.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Paine1988RoaMap}{}}%
-Paine, R.T. (1988). \href{https://doi.org/10.2307/1941141}{Road Maps of
-Interactions or Grist for Theoretical Development?} \emph{Ecology}, 69,
-1648--1654.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Poisot2022GuiPre}{}}%
-Poisot, T. (2022).
-\href{https://doi.org/10.32942/osf.io/aty7n}{Guidelines for the
-prediction of species interactions through binary classification}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Poisot2021GloKno}{}}%
+(2019). Assessing analytical methods for detecting spatiotemporal
+interactions between species from camera trapping data. \emph{Remote
+Sensing in Ecology and Conservation}, 5, 272--285.
+
+\leavevmode\hypertarget{ref-Paine1988RoaMap}{}%
+Paine, R.T. (1988). Road Maps of Interactions or Grist for Theoretical
+Development? \emph{Ecology}, 69, 1648--1654.
+
+\leavevmode\hypertarget{ref-Poisot2022GuiPre}{}%
+Poisot, T. (2022). Guidelines for the prediction of species interactions
+through binary classification.
+
+\leavevmode\hypertarget{ref-Poisot2021GloKno}{}%
 Poisot, T., Bergeron, G., Cazelles, K., Dallas, T., Gravel, D.,
-MacDonald, A., \emph{et al.} (2021).
-\href{https://doi.org/10.1111/jbi.14127}{Global knowledge gaps in
-species interaction networks data}. \emph{Journal of Biogeography}, 48,
+MacDonald, A., \emph{et al.} (2021). Global knowledge gaps in species
+interaction networks data. \emph{Journal of Biogeography}, 48,
 1552--1563.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Poisot2022NetEmb}{}}%
+\leavevmode\hypertarget{ref-Poisot2022NetEmb}{}%
 Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M.J., Becker, D.J.,
-Brierly, L., \emph{et al.} (2022).
-\href{https://doi.org/10.48550/arXiv.2105.14973}{Network embedding
-unveils the hidden interactions in the mammalian virome}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Poisot2015SpeWhy}{}}%
-Poisot, T., Stouffer, D.B. \& Gravel, D. (2015).
-\href{https://doi.org/10.1111/oik.01719}{Beyond species: Why ecological
-interaction networks vary through space and time}. \emph{Oikos}, 124,
-243--251.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Ponisio2017OppAtt}{}}%
-Ponisio, L.C., Gaiarsa, M.P. \& Kremen, C. (2017).
-\href{https://doi.org/10.1111/ele.12821}{Opportunistic attachment
-assembles plantpollinator networks}. \emph{Ecology Letters}, 20,
-1261--1272.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Savage2004EffBod}{}}%
+Brierly, L., \emph{et al.} (2022). Network embedding unveils the hidden
+interactions in the mammalian virome.
+
+\leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%
+Poisot, T., Stouffer, D.B. \& Gravel, D. (2015). Beyond species: Why
+ecological interaction networks vary through space and time.
+\emph{Oikos}, 124, 243--251.
+
+\leavevmode\hypertarget{ref-Ponisio2017OppAtt}{}%
+Ponisio, L.C., Gaiarsa, M.P. \& Kremen, C. (2017). Opportunistic
+attachment assembles plantpollinator networks. \emph{Ecology Letters},
+20, 1261--1272.
+
+\leavevmode\hypertarget{ref-Savage2004EffBod}{}%
 Savage, V.M., Gillooly, J.F., Brown, J.H., West, G.B. \& Charnov, E.L.
-(2004). \href{https://doi.org/10.1086/381872}{Effects of Body Size and
-Temperature on Population Growth.} \emph{The American Naturalist}, 163,
-429--441.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Song2022GenDri}{}}%
+(2004). Effects of Body Size and Temperature on Population Growth.
+\emph{The American Naturalist}, 163, 429--441.
+
+\leavevmode\hypertarget{ref-Song2022GenDri}{}%
 Song, C., Simmons, B.I., Fortin, M.-J. \& Gonzalez, A. (2022).
-\href{https://doi.org/10.1371/journal.pcbi.1010302}{Generalism drives
-abundance: A computational causal discovery approach}. \emph{PLOS
-Computational Biology}, 18, e1010302.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Stephenson2020TecAdv}{}}%
-Stephenson, P. (2020).
-\href{https://doi.org/10.1016/j.cosust.2020.08.005}{Technological
-advances in biodiversity monitoring: Applicability, opportunities and
-challenges}. \emph{Current Opinion in Environmental Sustainability},
-Open Issue 2020 Part A: Technology Innovations and Environmental
-Sustainability in the Anthropocene, 45, 36--41.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Stock2017LinFil}{}}%
-Stock, M., Poisot, T., Waegeman, W. \& De Baets, B. (2017).
-\href{https://doi.org/10.1038/srep45908}{Linear filtering reveals false
-negatives in species interaction data}. \emph{Scientific Reports}, 7,
-45908.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Strydom2021RoaPre}{}}%
+Generalism drives abundance: A computational causal discovery approach.
+\emph{PLOS Computational Biology}, 18, e1010302.
+
+\leavevmode\hypertarget{ref-Stephenson2020TecAdv}{}%
+Stephenson, P. (2020). Technological advances in biodiversity
+monitoring: Applicability, opportunities and challenges. \emph{Current
+Opinion in Environmental Sustainability}, Open issue 2020 part A:
+Technology Innovations and Environmental Sustainability in the
+Anthropocene, 45, 36--41.
+
+\leavevmode\hypertarget{ref-Stock2017LinFil}{}%
+Stock, M., Poisot, T., Waegeman, W. \& De Baets, B. (2017). Linear
+filtering reveals false negatives in species interaction data.
+\emph{Scientific Reports}, 7, 45908.
+
+\leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
 Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
-Desjardins-Proulx, P., \emph{et al.} (2021).
-\href{https://doi.org/10.1098/rstb.2021.0063}{A roadmap towards
-predicting species interaction networks (across space and time)}.
+Desjardins-Proulx, P., \emph{et al.} (2021). A roadmap towards
+predicting species interaction networks (across space and time).
 \emph{Philosophical Transactions of the Royal Society B: Biological
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Thompson2017DisGov}{}}%
-Thompson, P.L. \& Gonzalez, A. (2017).
-\href{https://doi.org/10.1038/s41559-017-0162}{Dispersal governs the
-reorganization of ecological networks under environmental change}.
+\leavevmode\hypertarget{ref-Thompson2017DisGov}{}%
+Thompson, P.L. \& Gonzalez, A. (2017). Dispersal governs the
+reorganization of ecological networks under environmental change.
 \emph{Nature Ecology \& Evolution}, 1, 1--8.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Thompson2000ResSol}{}}%
-Thompson, R.M. \& Townsend, C.R. (2000).
-\href{https://doi.org/10.1046/j.1365-2427.2000.00579.x}{Is resolution
-the solution?: The effect of taxonomic resolution on the calculated
-properties of three stream food webs}. \emph{Freshwater Biology}, 44,
-413--422.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Volkov2003NeuThe}{}}%
-Volkov, I., Banavar, J.R., Hubbell, S.P. \& Maritan, A. (2003).
-\href{https://doi.org/10.1038/nature01883}{Neutral theory and relative
-species abundance in ecology}. \emph{Nature}, 424, 1035--1037.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Walther1995SamEff}{}}%
+\leavevmode\hypertarget{ref-Thompson2000ResSol}{}%
+Thompson, R.M. \& Townsend, C.R. (2000). Is resolution the solution?:
+The effect of taxonomic resolution on the calculated properties of three
+stream food webs. \emph{Freshwater Biology}, 44, 413--422.
+
+\leavevmode\hypertarget{ref-Volkov2003NeuThe}{}%
+Volkov, I., Banavar, J.R., Hubbell, S.P. \& Maritan, A. (2003). Neutral
+theory and relative species abundance in ecology. \emph{Nature}, 424,
+1035--1037.
+
+\leavevmode\hypertarget{ref-Walther1995SamEff}{}%
 Walther, B.A., Cotgreave, P., Price, R.D., Gregory, R.D. \& Clayton,
-D.H. (1995).
-\href{https://doi.org/10.1016/0169-4758(95)80047-6}{Sampling Effort and
-Parasite Species Richness}. \emph{Parasitology Today}, 11, 306--310.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Williams2000SimRul}{}}%
-Williams, R.J. \& Martinez, N.D. (2000).
-\href{https://doi.org/10.1038/35004572}{Simple rules yield complex food
-webs}. \emph{Nature}, 404, 180--183.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Willott2001SpeAcc}{}}%
-Willott, S.j. (2001).
-\href{https://doi.org/10.1046/j.1365-2664.2001.00589.x}{Species
-accumulation curves and the measure of sampling effort}. \emph{Journal
-of Applied Ecology}, 38, 484--486.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Young2021RecPla}{}}%
-Young, J.-G., Valdovinos, F.S. \& Newman, M.E.J. (2021).
-\href{https://doi.org/10.1038/s41467-021-24149-x}{Reconstruction of
-plantpollinator networks from observational data}. \emph{Nature
+D.H. (1995). Sampling Effort and Parasite Species Richness.
+\emph{Parasitology Today}, 11, 306--310.
+
+\leavevmode\hypertarget{ref-Williams2000SimRul}{}%
+Williams, R.J. \& Martinez, N.D. (2000). Simple rules yield complex food
+webs. \emph{Nature}, 404, 180--183.
+
+\leavevmode\hypertarget{ref-Willott2001SpeAcc}{}%
+Willott, S.j. (2001). Species accumulation curves and the measure of
+sampling effort. \emph{Journal of Applied Ecology}, 38, 484--486.
+
+\leavevmode\hypertarget{ref-Young2021RecPla}{}%
+Young, J.-G., Valdovinos, F.S. \& Newman, M.E.J. (2021). Reconstruction
+of plantpollinator networks from observational data. \emph{Nature
 Communications}, 12, 3911.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Zhang2019GraCon}{}}%
-Zhang, S., Tong, H., Xu, J. \& Maciejewski, R. (2019).
-\href{https://doi.org/10.1186/s40649-019-0069-y}{Graph convolutional
-networks: A comprehensive review}. \emph{Computational Social Networks},
-6, 11.
+\leavevmode\hypertarget{ref-Zhang2019GraCon}{}%
+Zhang, S., Tong, H., Xu, J. \& Maciejewski, R. (2019). Graph
+convolutional networks: A comprehensive review. \emph{Computational
+Social Networks}, 6, 11.
 

### 2022-10-15 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@80920980ebd5187ab667cfd01f41e41cfcdd9132 🚀

@@
 %
-\,\textsuperscript{,}, %
+\,\textsuperscript{1,2}, %
 \href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
 %
-\,\textsuperscript{,}, %
+\,\textsuperscript{3,2}, %
 \href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
 %
-\,\textsuperscript{,}, %
+\,\textsuperscript{1,2}, %
 \href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
 %
-\,\textsuperscript{,}
+\,\textsuperscript{1,2}
 \vskip 1em
@@
 }
+
+Ecosystems are composed of networks of interacting species. These
+interactions allow communities of species to persist through time
+through both neutral and adaptive processes. Still a robust
+understanding of, and ability to predict and forecast interactions among
+species and their consequences for network structure remains elusive.
+This knowledge-gap is largely driven by a shortfall of data---although
+species occurrence data has rapidly increased in the last decade,
+species interaction data has not kept pace, largely due to the intrinsic
+difficulty and effort required to sample interactions. These sampling
+challenges bias data and hinder inferences about the structure and
+dynamics of interactions networks. Here, we demonstrate the realized
+false-negative rate (the percentage of species that actually interact
+but for which we do not yet have a record) can be quite high, even in
+thoroughly sampled systems, due to the intrinsic variation in abundances
+across species in a community. We demonstrate how a null model of
+occurrence detection can be used to estimate the false-negative rate in
+a given dataset. One hypothesis is that interactions between ``rare''
+species are themselves rare because these species are less likely to
+encounter one-another than species of higher relative abundance.
+However, we demonstrate that across several datasets of spatial or
+temporally replicated networks, there are positive associations that
+suggest these interactions actually exist but just are not observed.
+Finally, we assess how false negatives influence various models of
+network prediction, and recommend directly accounting for observation
+error in predictive models. We conclude by discussing how the
+understanding of false-negatives can inform how we design monitoring
+schemes for species interactions.
 

### 2022-10-15 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@2d3c915013683172c3822b260d54b299712a9a5e 🚀

@@
 \vfill
-Ecosystems are composed of networks of interacting species. These
-interactions allow communities of species to persist through time
-through both neutral and adaptive processes. Still a robust
-understanding of, and ability to predict and forecast interactions among
-species and their consequences for network structure remains elusive.
-This knowledge-gap is largely driven by a shortfall of data---although
-species occurrence data has rapidly increased in the last decade,
-species interaction data has not kept pace, largely due to the intrinsic
-difficulty and effort required to sample interactions. These sampling
-challenges bias data and hinder inferences about the structure and
-dynamics of interactions networks. Here, we demonstrate the realized
-false-negative rate (the percentage of species that actually interact
-but for which we do not yet have a record) can be quite high, even in
-thoroughly sampled systems, due to the intrinsic variation in abundances
-across species in a community. We demonstrate how a null model of
-occurrence detection can be used to estimate the false-negative rate in
-a given dataset. One hypothesis is that interactions between ``rare''
-species are themselves rare because these species are less likely to
-encounter one-another than species of higher relative abundance.
-However, we demonstrate that across several datasets of spatial or
-temporally replicated networks, there are positive associations that
-suggest these interactions actually exist but just are not observed.
-Finally, we assess how false negatives influence various models of
-network prediction, and recommend directly accounting for observation
-error in predictive models. We conclude by discussing how the
-understanding of false-negatives can inform how we design monitoring
-schemes for species interactions.
+
+        {\bfseries Abstract:}\,Ecosystems are composed of networks of
+interacting species. These interactions allow communities of species to
+persist through time through both neutral and adaptive processes. Still
+a robust understanding of, and ability to predict and forecast
+interactions among species and their consequences for network structure
+remains elusive. This knowledge-gap is largely driven by a shortfall of
+data---although species occurrence data has rapidly increased in the
+last decade, species interaction data has not kept pace, largely due to
+the intrinsic difficulty and effort required to sample interactions.
+These sampling challenges bias data and hinder inferences about the
+structure and dynamics of interactions networks. Here, we demonstrate
+the realized false-negative rate (the percentage of species that
+actually interact but for which we do not yet have a record) can be
+quite high, even in thoroughly sampled systems, due to the intrinsic
+variation in abundances across species in a community. We demonstrate
+how a null model of occurrence detection can be used to estimate the
+false-negative rate in a given dataset. One hypothesis is that
+interactions between ``rare'' species are themselves rare because these
+species are less likely to encounter one-another than species of higher
+relative abundance. However, we demonstrate that across several datasets
+of spatial or temporally replicated networks, there are positive
+associations that suggest these interactions actually exist but just are
+not observed. Finally, we assess how false negatives influence various
+models of network prediction, and recommend directly accounting for
+observation error in predictive models. We conclude by discussing how
+the understanding of false-negatives can inform how we design monitoring
+schemes for species interactions.\\%
 

### 2022-10-15 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@e4fd466051dbfde60cffbb8cd04dde4c658868d8 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@2d3c915013683172c3822b260d54b299712a9a5e 🚀

@@
 \tikz [remember picture, overlay] %
-\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
+\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.9] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
 \pagestyle{normal}
@@
 
-Ecosystems are composed of networks of interacting species. These
-interactions allow communities of species to persist through time
-through both neutral and adaptive processes. Still a robust
-understanding of, and ability to predict and forecast interactions among
-species and their consequences for network structure remains elusive.
-This knowledge-gap is largely driven by a shortfall of data---although
-species occurrence data has rapidly increased in the last decade,
-species interaction data has not kept pace, largely due to the intrinsic
-difficulty and effort required to sample interactions. These sampling
-challenges bias data and hinder inferences about the structure and
-dynamics of interactions networks. Here, we demonstrate the realized
-false-negative rate (the percentage of species that actually interact
-but for which we do not yet have a record) can be quite high, even in
-thoroughly sampled systems, due to the intrinsic variation in abundances
-across species in a community. We demonstrate how a null model of
-occurrence detection can be used to estimate the false-negative rate in
-a given dataset. One hypothesis is that interactions between ``rare''
-species are themselves rare because these species are less likely to
-encounter one-another than species of higher relative abundance.
-However, we demonstrate that across several datasets of spatial or
-temporally replicated networks, there are positive associations that
-suggest these interactions actually exist but just are not observed.
-Finally, we assess how false negatives influence various models of
-network prediction, and recommend directly accounting for observation
-error in predictive models. We conclude by discussing how the
-understanding of false-negatives can inform how we design monitoring
-schemes for species interactions.
+        {\bfseries Abstract:}\,Ecosystems are composed of networks of
+interacting species. These interactions allow communities of species to
+persist through time through both neutral and adaptive processes. Still
+a robust understanding of, and ability to predict and forecast
+interactions among species and their consequences for network structure
+remains elusive. This knowledge-gap is largely driven by a shortfall of
+data---although species occurrence data has rapidly increased in the
+last decade, species interaction data has not kept pace, largely due to
+the intrinsic difficulty and effort required to sample interactions.
+These sampling challenges bias data and hinder inferences about the
+structure and dynamics of interactions networks. Here, we demonstrate
+the realized false-negative rate (the percentage of species that
+actually interact but for which we do not yet have a record) can be
+quite high, even in thoroughly sampled systems, due to the intrinsic
+variation in abundances across species in a community. We demonstrate
+how a null model of occurrence detection can be used to estimate the
+false-negative rate in a given dataset. One hypothesis is that
+interactions between ``rare'' species are themselves rare because these
+species are less likely to encounter one-another than species of higher
+relative abundance. However, we demonstrate that across several datasets
+of spatial or temporally replicated networks, there are positive
+associations that suggest these interactions actually exist but just are
+not observed. Finally, we assess how false negatives influence various
+models of network prediction, and recommend directly accounting for
+observation error in predictive models. We conclude by discussing how
+the understanding of false-negatives can inform how we design monitoring
+schemes for species interactions.\\%
 

### 2022-10-16 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@e411d6fd2bc3a08964824a43ec81f379ae7c2be2 🚀

@@
 a robust understanding of, and ability to predict and forecast
-interactions among species and their consequences for network structure
-remains elusive. This knowledge-gap is largely driven by a shortfall of
-data---although species occurrence data has rapidly increased in the
-last decade, species interaction data has not kept pace, largely due to
-the intrinsic difficulty and effort required to sample interactions.
-These sampling challenges bias data and hinder inferences about the
-structure and dynamics of interactions networks. Here, we demonstrate
-the realized false-negative rate (the percentage of species that
-actually interact but for which we do not yet have a record) can be
-quite high, even in thoroughly sampled systems, due to the intrinsic
-variation in abundances across species in a community. We demonstrate
-how a null model of occurrence detection can be used to estimate the
-false-negative rate in a given dataset. One hypothesis is that
-interactions between ``rare'' species are themselves rare because these
-species are less likely to encounter one-another than species of higher
-relative abundance. However, we demonstrate that across several datasets
-of spatial or temporally replicated networks, there are positive
-associations that suggest these interactions actually exist but just are
-not observed. Finally, we assess how false negatives influence various
-models of network prediction, and recommend directly accounting for
-observation error in predictive models. We conclude by discussing how
-the understanding of false-negatives can inform how we design monitoring
-schemes for species interactions.\\%
+interactions among species remains elusive. This knowledge-gap is
+largely driven by a shortfall of data---although species occurrence data
+has rapidly increased in the last decade, species interaction data has
+not kept pace, largely due to the intrinsic difficulty and effort
+required to sample interactions. These sampling challenges bias data and
+hinder inferences about the structure and dynamics of interactions
+networks. Here, we demonstrate the realized false-negative rate (the
+percentage of species that actually interact but for which we do not yet
+have a record) can be quite high, even in thoroughly sampled systems,
+due to the intrinsic variation in abundances across species in a
+community. We illustrate how a null model of occurrence detection can be
+used to estimate the false-negative rate in a given dataset. One
+hypothesis is that interactions between ``rare'' species are themselves
+rare because these species are less likely to encounter one-another than
+species of higher relative abundance. However, we demonstrate that
+across several datasets of spatial or temporally replicated networks,
+there are positive associations that suggest these interactions actually
+exist but just are not observed. Finally, we assess how false negatives
+influence various models of network prediction, and recommend directly
+accounting for observation error in predictive models. We conclude by
+discussing how the understanding of false-negatives can inform how we
+design monitoring schemes for species interactions.\\%
 
@@
 \emph{et al.} 2015), to determine sampling design (Moore \& McCarthy
-2016),and to measure species richness across large scales (Carlson
+2016), and to measure species richness across large scales (Carlson
 \emph{et al.} 2020). In the context of interactions, an initial concern
@@
 inadequately reflect the reality of how species interact (Paine 1988) or
-the structure of the network as a whole (McLeod \emph{et al.} 2021).
-Martinez \emph{et al.} (1999) showed that in a plant-endophyte trophic
-network, network connectance is robust to sampling effort, but this was
-done in the context of a system for which observation of 62,000 total
-interactions derived from 164,000 plant-stems was feasible. In some
-systems (e.g.~megafauna food-webs) this many observations is either
-impractical or infeasible due to the absolute abundance of the species
-in question.
-
-We cannot feasibly observe all (or even most) of the direct interactions
-that occur in an ecosystem. This means we can be confident two species
+the structure of the network as a whole (Martinez \emph{et al.} 1999;
+McLeod \emph{et al.} 2021). Martinez \emph{et al.} (1999) showed that in
+a plant-endophyte trophic network, network connectance is robust to
+sampling effort, but this was done in the context of a system for which
+observation of 62,000 total interactions derived from 164,000
+plant-stems was feasible. In some systems (e.g.~megafauna food-webs)
+this many observations is either impractical or infeasible due to the
+absolute abundance of the species in question.
+
+We cannot feasibly observe all (or even most) of the interactions that
+occur in an ecosystem. This means we can be confident two species
 actually interact if we have a record of it (given an estimate of
 species misidentification probability), but not at all confident that a
-pair of species \emph{do not} interact if we have no record of those
-species observed together. In other words, it is difficult to
+pair of species \emph{do not} interact if we have \emph{no record} of
+those species observed together. In other words, it is difficult to
 distinguish \emph{true-negatives} (two species never interact) from
@@
 interaction data we have is geographically biased toward the usual
-suspects (Poisot \emph{et al.} 2021). We therefore need a systematic
-approach to assessing these biases in the observation process and the
-consequences this has for our understanding of interaction networks.
+suspects (Poisot \emph{et al.} 2021). We therefore need a statistical
+approach to assessing these biases in the observation process and their
+consequences for our understanding of interaction networks.
 
@@
 Canard \emph{et al.} (2012) presents a null model of food-web structure
-where species encounter one-another directly in proportion to each
-species' relative-abundance. This assumes that there are no associations
-in species co-occurrence due to an interaction (perhaps because this
+where species encounter one-another in proportion to each species'
+relative-abundance. This assumes that there are no associations in
+species co-occurrence due to an interaction (perhaps because this
 interaction is ``important'' for both species; Cazelles \emph{et al.}
@@
 require that neither of two species, regardless of whether they
-co-occur, exhibit any meaningful effect on the fitness of the other. So,
-although co-occurrence is not directly indicative of an interaction, it
-is a precondition for an interaction. Therefore observations of
-``non-interactions'' between pairs of species that are outside of the
-union of both species ranges do not provide any information about that
-interaction, i.e.~they should be excluded from consideration.
-
-Here, we illustrate how our confidence that a pair of species we believe
-to not interact highly depends on sampling effort, and suggest that
-surveys of species interactions can benefit from simulation modeling of
-detection probability. We demonstrate that the realized false-negative
-rate of interactions is directly related to the relative abundance of
-the species involved, and demonstrate how simulation can be used to
-produce a null estimate of the false-negative rate as a function of
-total sampling effort (the total count of all individuals of all species
-seen). We show that positive associations in co-occurrence data can
-increase realized probability of false-negatives, and demonstrate these
-positive associations are ubiquitous in network datasets. We conclude by
-recommending that the simulation of sampling effort and species
-occurrence can and should be used to help design surveys of species
-interaction diversity (Moore \& McCarthy 2016), and by advocating use of
-null models like those presented here as a tool for both guiding design
-of surveys of species interactions and for modeling detection error in
-predictive models.
+co-occur, ever exhibit any meaningful effect on the fitness of the
+other. So, although co-occurrence is not directly indicative of an
+interaction, it \emph{is} a precondition for an interaction.
+
+Here, we illustrate how our confidence that a pair of species never
+interacts highly depends on sampling effort, and suggest that surveys of
+species interactions can benefit from simulation modeling of the
+sampling process. We demonstrate that the realized false-negative rate
+of interactions is directly related to the relative abundance of the
+species pool, and demonstrate how simulation can be used to produce a
+null estimate of the false-negative rate given total sampling effort
+(the total count of all individuals of all species seen). We show that
+positive associations in co-occurrence data can increase the realized
+number of false-negatives, and demonstrate these positive associations
+are rampant in network datasets. We conclude by recommending that the
+simulation of sampling effort and species occurrence can and should be
+used to help design surveys of species interaction diversity (Moore \&
+McCarthy 2016), and by advocating use of null models like those
+presented here as a tool for both guiding design of surveys of species
+interactions and for modeling detection error in predictive models.
 
@@
 not-interacting with an independent and fixed probability, which we
-denote pfn and subsequently refer to as the False-Negative Rate (FNR).
-If we observe the same species not-interacting \(N\) times, then the
-probability of a true-negative (denoted \(p_{tn}\)) is given by
+denote \(p_fn\) and subsequently refer to as the False-Negative Rate
+(FNR). If we observe the same species not-interacting \(N\) times, then
+the probability of a true-negative (denoted \(p_{tn}\)) is given by
 \(p_{tn}=1-(p_{fn})^N\). This relation (the probability-mass-function of
 geometric distribution, a special case of the negative-binomial
-distribution) is shown in Figure 1(A) for varying values of \(p_{fn}\)
-and illustrates a fundamental link between our ability to reliably say
-an interaction doesn't exist---\(p_{tn}\)---and the number of times we
-have observed a given species. In addition, note that also there is no
-non-zero \(p_{fn}\) for which we can ever prove that an interaction does
-not exist---no matter how many observations of non-interactions \(N\) we
-have, \(p_{tn}<1\).
+distribution) is shown in fig.~\ref{fig:geometric}(A) for varying values
+of \(p_{fn}\) and illustrates a fundamental link between our ability to
+reliably say an interaction doesn't exist---\(p_{tn}\)---and the number
+of times \(N\) we have observed a given species. In addition, note that
+there is no non-zero \(p_{fn}\) for which we can ever \emph{prove} that
+an interaction does not exist---no matter how many observations of
+non-interactions \(N\) we have, \(p_{tn}<1\).
 
 From fig.~\ref{fig:geometric}(A) it is clear that the more often we see
-two species co-occurring, but not interacting, the more likely the
-interaction is a true negative. This has several practical consequences:
-first it means negatives taken outside the overlap of the range of each
-species aren't informative. Second, we can use this relation to compute
-the expected number of total observations needed to obtain a ``goal''
-number of observations of a particular pair of species
-(fig.~\ref{fig:geometric}(B)). As an example, if we hypothesize that
-\(A\) and \(B\) do not interact, and we want to see species \(A\) and
-\(B\) both co-occurring and not interacting 10 times to be confident
-this is a true negative, then we need an expected 1000 observations of
-all species if the relative abundances of \(A\) and \(B\) are both
-\(0.1\).
+two species co-occurring, but \emph{not interacting}, the more likely
+the interaction is a true-negative. This has several practical
+consequences: first it means negatives taken outside the overlap of the
+range of each species aren't informative because co-occurrence was not
+possible, and therefore neither was an interaction. Second, we can use
+this relation to compute the expected number of total observations
+needed to obtain a ``goal'' number of observations of a particular pair
+of species (fig.~\ref{fig:geometric}(B)). As an example, if we
+hypothesize that \(A\) and \(B\) do not interact, and we want to see
+species \(A\) and \(B\) both co-occurring and \emph{not interacting} 10
+times to be confident this is a true negative, then we need an expected
+1000 observations of all species if the relative abundances of \(A\) and
+\(B\) are both \(0.1\).
 
@@
 \includegraphics{./figures/fig1.png}
-\caption{(A) The probability that an observed interaction is a true
-negative (y-axis) given how many times it has been sampled as a
+\caption{\textbf{(A)} The probability that an observed interaction is a
+true negative (y-axis) given how many times it has been sampled as a
 non-interaction (x-axis). Each color reflects a different value of
 \(p_{fn}\), the false-negative rate (FNR)---this is effectively the cdf
-of the geometric distribution. (B): The expected needed observations of
-all individuals of all species (y-axis) required to obtain a goal number
-of observations (colors) of a particular species, and a function of the
-relative abundance of that focal species (x-axis). (C): False negative
-rate (y-axis) as a function of total sampling effort (x-axis) and
-network size, computed using the method described above. For 500
-independent draws from the niche model (Williams \& Martinez (2000)) at
-varying levels of species richness (colors) with connectance drawn
-according to the flexible-links model (MacDonald \emph{et al.} (2020))
-as described in the main text. For each draw from the niche model, 200
-sets of 1500 observations are simulated, for which each the mean false
-negative rate at each observation-step is computed. Means denoted with
-points, with 1 in the first shade and 2 in the second. (D): Same as (C),
-except using empirical food webs from Mangal database, where richness.
-The outlier on (D) is a 714 species food-web.}\label{fig:geometric}
+of the geometric distribution. \textbf{(B)} The expected number of total
+observations needed (colors) to observe 10 co-occurrences between a
+species with relative abundance \(P(A)\) (x-axis) and a second species
+with relative abundance \(P(Y)\). \textbf{(C)}: False negative rate
+(y-axis) as a function of total sampling effort (x-axis) and network
+size, computed using the method described above. For 500 independent
+draws from the niche model (Williams \& Martinez (2000)) at varying
+levels of species richness (colors) with connectance drawn according to
+the flexible-links model (MacDonald \emph{et al.} (2020)) as described
+in the main text. For each draw from the niche model, 200 sets of 1500
+observations are simulated, for which each the mean false negative rate
+at each observation-step is computed. Means denoted with points, with 1
+in the first shade and 2 in the second. \textbf{(D)}: Same as
+\textbf{(C)}, except using empirical food webs from Mangal database,
+where richness. The outlier on \textbf{(D)} is a 714 species
+food-web.}\label{fig:geometric}
 }
@@
 webs from the Mangal database (Banville \emph{et al.} 2021) and random
-food-webs generated using the niche model (Williams \& Martinez 2000), a
-simple generative model of food-web structure. Our neutral model of
-observation assumes each observed species is drawn from the distribution
-in proportion to each species' abundance at that place and time. The
-abundance distribution of a community can be reasonably-well described
-by a log-normal distribution (Volkov \emph{et al.} 2003). In addition to
-the log-normal distribution, we also tested the case where the abundance
-distribution is derived from power-law scaling \(Z^{(log(T_i)-1)}\)
-where \(T_i\) is the trophic level of species \(i\) and \(Z\) is a
-scaling coefficient (Savage \emph{et al.} 2004), which yields the same
-qualitative behavior. The practical consequence of abundance
-distributions spanning many orders of magnitude of abundance is that
-observing two ``rare'' species interacting requires two low probability
-events: observing two rare species at the same time.
+food-webs generated using the niche model, a simple generative model of
+food-web structure that accounts for allometric scaling (Williams \&
+Martinez 2000). Our neutral model of observation assumes each observed
+species is drawn in proportion to each species' abundance at that place
+and time. The abundance distribution of a community can be
+reasonably-well described by a log-normal distribution (Volkov \emph{et
+al.} 2003). In addition to the log-normal distribution, we also tested
+the case where the abundance distribution is derived from power-law
+scaling \(Z^{(log(T_i)-1)}\) where \(T_i\) is the trophic level of
+species \(i\) and \(Z\) is a scaling coefficient (Savage \emph{et al.}
+2004), which yields the same qualitative behavior. The practical
+consequence of abundance distributions spanning many orders of magnitude
+of abundance is that observing two ``rare'' species interacting requires
+two low probability events: observing two rare species \emph{at the same
+time}.
 
@@
 of observing both species \(i\) and \(j\) at a given place and time by
-simulating \(n\) observations of all individuals of any species, where
+simulating \(n\) observations of all individuals of any a species, where
 the species of the individual observed at the \(\{1,2,\dots,n\}\)-th
@@
 observed---but not both---in these \(n\) observations, but \(M_{ij}=1\),
-this is counted as a false-negative, and a true-negative otherwise.
+this is counted as a false-negative, and a true-negative otherwise. For
+each pair of species \((i,j)\), if both \(i\) and \(j\) are observed
+within the n-observations, the interaction is tallied as a true positive
+if \(M_{ij}=1\). If only one of \(i\) or \(j\) are observed---but not
+both---in these \(n\) observations, but \(M_{ij}=1\), this is counted as
+a false-negative, and a true-negative otherwise (\(M_{ij} = 0\)).
 
@@
 (MacDonald \emph{et al.} 2020) is \((\mu=0.086, \phi=24.3)\). All
-simulations were done with 500 independent replicates per unique number
-of observations \(n\). All analyses presented here are done in Julia
-v1.8 (Bezanson \emph{et al.} 2015) using both EcologicalNetworks.jl v0.5
-and Mangal.jl v0.4 (Banville \emph{et al.} 2021) and are hosted at
-(GITHUB\_LINK\_TODO). Note that the empirical data, for the reasons
-described above, very likely already contains many false negatives,
-we'll revisit this issue in the final section.
+simulations were done with 500 independent replicates of unique niche
+model networks per unique number of observations \(n\). All analyses
+presented here are done in Julia v1.8 (Bezanson \emph{et al.} 2015)
+using both EcologicalNetworks.jl v0.5 and Mangal.jl v0.4 (Banville
+\emph{et al.} 2021) and are hosted at (GITHUB\_LINK\_TODO). Note that
+the empirical data, for the reasons described above, very likely already
+contains many false negatives, we'll revisit this issue in the final
+section.
 
@@
 off quickly as a function of observation effort, mediated by total
-richness. The practical consequence of the bottom row of Figure 1 is
-whether the total number of observations of all species (the x-axis) for
-the range of possible FNR we deem acceptable (the y-axis) is feasible.
-This raises two points: first, empirical data on interactions are
-subject to the practical limitations of funding and human-work hours,
-and therefore existing data tend to fall on the order of hundreds or
-thousands observations of individuals per site. Clear aggregation of
-data on sampling effort has proven difficult to find and a meta-analysis
-of network data and sampling effort seems both pertinent and necessary,
-in addition to the effects of aggregation of interactions across
-taxonomic scales (Gauzens \emph{et al.} 2013; Giacomuzzo \& Jordán
-2021). This inherent limitation on in-situ sampling means we should
-optimize where we sample across space so that for a given number of
-samples, we obtain the maximum information possible. Second, what is
+richness. The practical consequence of the bottom row of
+fig.~\ref{fig:geometric} is whether the total number of observations of
+all species (the x-axis) for the threshold FNR we deem acceptable (the
+y-axis) is feasible. This raises two points: first, empirical data on
+interactions are subject to the practical limitations of funding and
+human-work hours, and therefore existing data tend to fall on the order
+of hundreds or thousands observations of individuals per site. Clear
+aggregation of data on sampling effort has proven difficult to find and
+a meta-analysis of network data and sampling effort seems both pertinent
+and necessary, in addition to the effects of aggregation of interactions
+across taxonomic scales (Gauzens \emph{et al.} 2013; Giacomuzzo \&
+Jordán 2021). This inherent limitation on in-situ sampling means we
+should optimize where we sample across space so that for a given number
+of samples, we obtain the maximum information possible. Second, what is
 meant by ``acceptable'' FNR? This raises the question: does a shifting
@@
 fig.~\ref{fig:geometric}(C)), or to get a representative sample of
-interactions across the species pool? This argument is well-considered
-when sampling individual species (Willott 2001), but has not yet been
-adopted for designing samples of communities.
+interactions across the species pool? These arguments are
+well-considered when sampling individual species (Willott 2001), but
+have not yet been adopted for designing samples of communities.
 
@@
 the probability that we observe the co-occurrence of two species \(A\)
-and \(B\) that we know interact as \(P(AB)\) and if there is no
-association between the marginal probabilities of observing \(A\) and
-observing \(B\), denoted \(P(A)\) and \(P(B)\) respectively, then the
-probability of observing their co-occurrence \(P(AB) = P(A)P(B)\). In
-the other case where there is some positive strength of association
-between observing both \(A\) and \(B\) because this interaction is
-``important'' for each species, then the probability of observation both
-\(A\) and \(B\), \(P(AB)\), is greater than \(P(A)P(B)\) as \(P(A)\) and
-\(P(B)\) are not independent and instead are positively correlated,
-i.e.~\(P(AB)> P(A)P(B)\). In this case, the probability of observing a
-false negative in our naive model from fig.~\ref{fig:geometric}(A) is
-\(p_{fn}= 1-P(AB)\), which due to the above inequality implies
-\(p_{fn} >1-P(A)P(B)\). This indicates an increasingly greater
-probability of a false negative as \(P(AB) \to P(AB) \gg P(A)P(B)\).
-However, this still does not consider variation in species abundance in
-space and time (Poisot \emph{et al.} 2015). If positive or negative
-associations between species structure variation in the distribution of
-\(P(AB)\) across space/time, then the spatial/temporal biases induced by
-data collection would further impact the realized false negative rate,
-as the probability of false negative would not be constant for each pair
-of species across sites.
-
-To test for this association in data we scoured Mangal for datasets with
-many spatial or temporal replicates of the same system. For each
-dataset, we compute the marginal probability \(P(A)\) of occurrence of
-each species \(A\) across all networks in the dataset. For each pair of
-interacting species \(A\) and \(B\), we then compute and compare the
-probability of co-occurrence if each species occurs independently,
-\(P(A)P(B)\), to the empirical joint probability of co-occurrence,
-\(P(AB)\). Following our analysis above, if \(P(AB)\) is greater than
-\(P(A)P(B)\), then we expect our neutral estimates of the FNR above to
-underestimate the realized FNR. In fig.~\ref{fig:mangal}, we see the
-difference between \(P(AB)\) and \(P(A)P(B)\) for the seven suitable
-datasets with enough spatio-temporal replicates and a shared taxonomic
-backbone (meaning all individual networks use common species
+and \(B\) as \(P(AB)\) and if there is no association between the
+marginal probabilities of observing \(A\) and observing \(B\), denoted
+\(P(A)\) and \(P(B)\) respectively, then the probability of observing
+their co-occurrence is the product of the marginal probabilities for
+each species, \(P(AB) = P(A)P(B)\). In the other case where there is
+some positive strength of association between observing both \(A\) and
+\(B\) because this interaction is ``important'' for each species, then
+the probability of observation both \(A\) and \(B\), \(P(AB)\), is
+greater than \(P(A)P(B)\) as \(P(A)\) and \(P(B)\) are not independent
+and instead are positively correlated, i.e.~\(P(AB)> P(A)P(B)\). In this
+case, the probability of observing a single false-negative in our naive
+model from fig.~\ref{fig:geometric}(A) is \(p_{fn}= 1-P(AB)\), which due
+to the above inequality implies \(p_{fn}>1-P(A)P(B)\). This indicates an
+increasingly greater probability of a false negative as the strength of
+association gets stronger, \(P(AB) \to P(AB) \gg P(A)P(B)\). However,
+this still does not consider variation in species abundance in space and
+time (Poisot \emph{et al.} 2015). If positive or negative associations
+between species structure variation in the distribution of \(P(AB)\)
+across space/time, then the spatial/temporal biases induced by data
+collection would further impact the realized false negative rate, as the
+probability of false negative would not be constant for each pair of
+species across sites.
+
+To test for these positive associations in data we scoured Mangal for
+datasets with many spatial or temporal replicates of the same system.
+For each dataset, we compute the marginal probability \(P(A)\) of
+occurrence of each species \(A\) across all networks in the dataset. For
+each pair of interacting species \(A\) and \(B\), we then compute and
+compare the probability of co-occurrence if each species occurs
+independently, \(P(A)P(B)\), to the empirical joint probability of
+co-occurrence, \(P(AB)\). Following our analysis above, if \(P(AB)\) is
+greater than \(P(A)P(B)\), then we expect our neutral estimates of the
+FNR above to underestimate the realized FNR. In fig.~\ref{fig:mangal},
+we see the difference between \(P(AB)\) and \(P(A)P(B)\) for the seven
+suitable datasets with enough spatio-temporal replicates and a shared
+taxonomic backbone (meaning all individual networks use common species
 identifiers) found on Mangal to perform this analysis. Further details
 about each dataset are reported in tbl.~\ref{tbl:id}.
+
+In each of these datasets, the joint probability of co-occurrence
+\(P(AB)\) is decisively greater than our expectation if species co-occur
+in proportion to their relative abundance \(P(A)P(B)\). This suggests
+that there may not be as many ``neutrally forbidden links'' (Canard
+\emph{et al.} 2012) as we might think, and that the reason we do not
+have records of interactions between rare species is probably due to
+observation error. This has serious ramifications for the widely
+observed property of nestedness seen in bipartite networks (Bascompte \&
+Jordano 2007)---perhaps the reason we have lots of observations between
+generalists is because they are more abundant, and this is particularly
+relevant as we have strong evidence that generalism drives abundance
+(Song \emph{et al.} 2022), not vice-versa.
 
@@
 (\(P(A)P(B)\)) for interacting species for each dataset. The red-dashed
-line indicates 0. Each histogram represents a density, meaning the area
-of the entire curve sums to 1. The continuous density estimate (computed
-using local smoothing) is shown in grey. The p-value on each plot is the
-result of a one-sided t-test comparing the mean of each distribution to
-0.}\label{fig:mangal}
+line indicates 0 (no association). Each histogram represents a density,
+meaning the area of the entire curve sums to 1. The continuous density
+estimate (computed using local smoothing) is shown in grey. The p-value
+on each plot is the result of a one-sided t-test comparing the mean of
+each distribution to 0.}\label{fig:mangal}
 }
@@
 interactions across the entire spatial-temporal extent) \((C)\), the
-mean species richness across each local network \(S\), the mean
-connectance of each local network \(C\), the mean \(\beta\)-diversity
-among overlapping species across all pairs of network species
-(\(\bar{\beta}_{OS}\)), and the mean \(\beta\)-diversity among all
-species in the metaweb (\(\bar{\beta}_{WN}\)). Both metrics are computed
-using KGL \(\beta\)-diversity (Koleff \emph{et al.}
+mean species richness across each local network \(\bar{S}\), the mean
+connectance of each local network \(\bar{C}\), the mean
+\(\beta\)-diversity among overlapping species across all pairs of
+network species (\(\bar{\beta}_{OS}\)), and the mean \(\beta\)-diversity
+among all species in the metaweb (\(\bar{\beta}_{WN}\)). Both metrics
+are computed using KGL \(\beta\)-diversity (Koleff \emph{et al.}
 2003)}\tabularnewline
@@
 
-In each of these datasets, the joint probably of co-occurrence \(P(AB)\)
-is decisively greater than our expectation if species co-occur in
-proportion to their relative abundance \(P(A)P(B)\). This suggests that
-there may not be as many ``neutrally forbidden links'' (Canard \emph{et
-al.} 2012) as we might think, and that the reason we do not have records
-of interactions between rare species is probably due to observation
-error. This has serious ramifications for the widely observed property
-of nestedness seen in bipartite networks (Bascompte \& Jordano
-2007)---perhaps the reason we have lots of observations between
-generalists is because they are more abundant, and this is particularly
-relevant as we have strong evidence that generalism drives abundance
-(Song \emph{et al.} 2022), not vice-versa.
-
 \hypertarget{the-impact-of-false-negatives-on-network-properties-and-prediction}{%
@@
 predictions about interactions, as well as their effect on network
-structure. The prevalence of false-negatives in our data is the catalyst
-for interaction prediction in the first place, and as a result methods
-have been proposed to counteract this bias Poisot \emph{et al.} (2022).
-However, it is feasible that the FNR is so high that it could induce too
-much noise for an interaction prediction model to detect the signal of
-possible interaction between species.
+structure. The prevalence of false-negatives in data is the catalyst for
+interaction prediction in the first place, and as a result methods have
+been proposed to counteract this bias (Stock \emph{et al.} 2017; Poisot
+\emph{et al.} 2022). However, it is feasible that the FNR in a given
+dataset is so high that it could induce too much noise for an
+interaction prediction model to detect the signal of possible
+interaction between species.
 
@@
 and the same method as Strydom \emph{et al.} (2021) to extract latent
-features for each species in this dataset based on co-occurrence. We
-then predict a metaweb (equivalent to predicting true or false for an
-interaction for each species pair, effectively a binary classification
-problem) from these species-level features using four candidate models
-for binary classification---three often used machine-learning (ML)
-methods (Boosted Regression Tree (BRT), Random Forest (RF), Decision
-Tree (DT)), and one naive model from classic statistics (Logistic
-Regression (LR)). Each of the ML models are bootstrap aggregated (or
-bagged) with 100 replicates each. We partition the data into 80-20
-training-test split, and then seed the training data with false
-negatives at varying rates, but crucially do nothing to the test data.
-We fit all of these models using MLJ.jl, a high-level Julia framework
-for a wide-variety of ML models (Blaom \emph{et al.} 2020). We evaluate
-the efficacy of these models using two common measures of binary
-classifier performance: the area under the receiver-operator curve
-(ROC-AUC) and the area under the precision-recall curve (PR-AUC), for
-more details see (Poisot 2022) Here, PR-AUC is slightly more relevant as
-it is a better indicator of prediction of false-negatives. The results
-of these simulations are shown in fig.~\ref{fig:addedfnr}(A) and (B).
+features for each species in this dataset based on applying PCA to the
+co-occurrence matrix. We then predict a metaweb (equivalent to
+predicting true or false for an interaction between each species pair,
+effectively a binary classification problem) from these species-level
+features using four candidate models for binary classification---three
+often used machine-learning (ML) methods (Boosted Regression Tree (BRT),
+Random Forest (RF), Decision Tree (DT)), and one naive model from
+classic statistics (Logistic Regression (LR)). Each of the ML models are
+bootstrap aggregated (or bagged) with 100 replicates each. We partition
+the data into 80-20 training-test split, and then seed the training data
+with false negatives at varying rates, but crucially do nothing to the
+test data. We fit all of these models using MLJ.jl, a high-level Julia
+framework for a wide-variety of ML models (Blaom \emph{et al.} 2020). We
+evaluate the efficacy of these models using two common measures of
+binary classifier performance: the area under the receiver-operator
+curve (ROC-AUC) and the area under the precision-recall curve (PR-AUC),
+for more details see Poisot (2022). Here, PR-AUC is slightly more
+relevant as it is a better indicator of prediction of false-negatives.
+The results of these simulations are shown in
+fig.~\ref{fig:addedfnr}(A\&B).
 
@@
 \includegraphics{./figures/fig3.png}
-\caption{(A) The area-under the receiver-operator curve (ROC-AUC) and
-(B) The area-under the precision-recall curve (PR-AUC; right) for each
-different predictive model (colors/shapes) across a spectrum of the
-proportion of added false negatives (x-axis). (C) The mean trophic-level
-of all species in a network generated with the niche model across
-different species richnesses (colors). For each value of the FNR, the
-mean trophic level was computed across 50 replicates. The shaded region
-for each line is one standard-deviation across those
-replicates.}\label{fig:addedfnr}
+\caption{\textbf{(A)} The area-under the receiver-operator curve
+(ROC-AUC) and \textbf{(B)} The area-under the precision-recall curve
+(PR-AUC; right) for each different predictive model (colors/shapes)
+across a spectrum of the proportion of added false negatives (x-axis).
+\textbf{(C)} The mean trophic-level of all species in a network
+generated with the niche model across different species richnesses
+(colors). For each value of the FNR, the mean trophic level was computed
+across 50 replicates. The shaded region for each line is one
+standard-deviation across those replicates.}\label{fig:addedfnr}
 }
@@
 
-One interesting result seen in fig.~\ref{fig:addedfnr}(A) and (B) is
-that the ROC-AUC value does not approach random in the same way the
-PR-AUC curve does as we increase the added FNR. The reason for this is
-that ROC-AUC is fundamentally not as useful a metric in assessing
-predictive capacity as PR-AUC. As we keep adding more false-negatives,
-the network eventually becomes a zeros matrix, and these models can
-still learn to predict ``no-interaction'' for all possible species
-pairs, which does far better than random guessing (ROC-AUC
-\textgreater{} 0.5) in terms of the true and false positive rates (the
-components of ROC-AUC). This highlights a more broad issue of label
-class imbalance, meaning there are far more non-interactions than
-interactions in data. A full treatment of the importance of
-class-balance is outside the scope of this paper, but is explored
-in-depth in (Poisot 2022).
+One interesting result seen in fig.~\ref{fig:addedfnr}(A\&B) is that the
+ROC-AUC value does not approach random in the same way the PR-AUC curve
+does as we increase the added FNR. The reason for this is that ROC-AUC
+is fundamentally not as useful a metric in assessing predictive capacity
+as PR-AUC. As we keep adding more false-negatives, the network
+eventually becomes a zeros matrix, and these models can still learn to
+predict ``no-interaction'' for all possible species pairs, which does
+far better than random guessing (ROC-AUC = 0.5) in terms the false
+positive rate (one of the components of ROC-AUC). This highlights a more
+broad issue of label class imbalance, meaning there are far more
+non-interactions than interactions in data. A full treatment of the
+importance of class-balance is outside the scope of this paper, but is
+explored in-depth in Poisot (2022).
 
@@
 given their simplicity, there have been several major developments in
-the field applying deep-learning methods to many tasks in network
-inference and prediction---namely graph-representation learning (GRL,
-Khoshraftar \& An (2022)) and graph convolutional networks (Zhang
-\emph{et al.} 2019). At this time, these advances can not yet be applied
-to ecological networks because they require far more data than we
-currently have. We already have lots of features that could be used as
-inputs into these models (i.e.~species level data about occurrence,
-genomes, abundance, etc.), but our network datasets barely get into the
-hundreds of local networks sampled across space and time
-tbl.~\ref{tbl:id}. Once we start to get into the thousands, these models
-will become more useful, but this can only be done with systematic
-monitoring of interactions. This again highlights the need to optimize
-our sampling effort to maximize the amount of information contained in
-our data given the expensive nature of sampling interactions.
+applying deep-learning methods to many tasks in network inference and
+prediction---namely graph-representation learning (GRL, Khoshraftar \&
+An (2022)) and graph convolutional networks (Zhang \emph{et al.} 2019).
+At this time, these advances can not yet be applied to ecological
+networks because they require far more data than we currently have. We
+already have lots of features that could be used as inputs into these
+models (i.e.~species level data about occurrence, genomes, abundance,
+etc.), but our network datasets barely get into the hundreds of local
+networks sampled across space and time (tbl.~\ref{tbl:id}). Once we
+start to get into the thousands, these models will become more useful,
+but this can only be done with systematic monitoring of interactions.
+This again highlights the need to optimize our sampling effort to
+maximize the amount of information contained in our data given the
+expensive nature of sampling interactions.
 
@@
 not deviate widely from the true value until very large FNRs,
-i.e.~\(p_{fn} > 0.7\).
+i.e.~\(p_{fn} > 0.7\). This is not entirely unsurprising. Removing links
+randomly from a food-web is effectively the inverse problem of the
+emergence of a giant component (more than half of the nodes are in a
+connected network) in random graphs (see Li \emph{et al.} (2021) for a
+thorough review). The primary difference being that we are removing
+edges, not adding them, and thus we are witnessing the dissolution of a
+giant component, rather than the emergence of one. Further applications
+of percolation theory to the topology of ecological networks could
+improve our understanding of how false-negatives impact the inferences
+about the structure and dynamics on these networks.
 
@@
 strength of association between co-occurrence and interactions (Cazelles
-\emph{et al.} 2016) across many empirical systems for the first time,
-and found that these positive associations are both very common, and
-showed algebraically that they increase the realized FNR. We have also
-shown that false-negatives could further impact our ability to both
-predict interactions and infer properties of the networks, which
-highlights the need for further research into methods for correcting
-this bias in existing data.
-
-A better understanding of how false-negatives impact our inference of
-network structure and dynamics is prediction of ecological networks by
-both using information about individual species interactions and the
-structure of metawebs on large scales is a practical necessity.
-False-negatives could pose a problem for many forms of inference in
-network ecology. For example, inferring the structural or dynamic
+\emph{et al.} 2016) across many empirical systems, and found that these
+positive associations are both very common, and showed algebraically
+that they increase the realized FNR. We have also shown that
+false-negatives could further impact our ability to both predict
+interactions and infer properties of the networks, which highlights the
+need for further research into methods for correcting this bias in
+existing data.
+
+A better understanding of how false-negatives impact species interaction
+data is a practical necessity---both for inference of network structure
+and dynamics, but also for prediction of interactions by using species
+level information. False-negatives could pose a problem for many forms
+of inference in network ecology. For example, inferring the dynamic
 stability of a network could be prone to error if the observed network
@@
 that have not been observed but that still may become climatically
-infeasible. As is evident from Figure 1(A), we can never guarantee there
-are no false-negatives in data. In recent years, there has been interest
-toward explicitly accounting for false-negatives in models (Stock
-\emph{et al.} 2017; Young \emph{et al.} 2021), and a predictive approach
-to networks---rather than expecting our samples to fully capture all
-interactions (Strydom \emph{et al.} 2021). As a result, better models
-for predicting interactions are needed for interaction networks. This
-includes explicitly accounting for observation error (Johnson \&
-Larremore 2021)---certain classes of models have been used to reflect
-hidden states which account for detection error in occupancy modeling
-(Joseph 2020), and could be integrated in the predictive models of
-interactions in the future.
-
-A brief caveat here is that we do not consider the rate of
-false-positives---in large part false-positives can be explained by
-misidentification of species, although this could be a relevant
-consideration in some cases. The same logic that we apply to
-false-negatives could easily be applied to false-positives, e.g.~that we
-can be much more confident that an interaction is a true positive if we
-have observed it 50 times rather than only once, and we could similarly
-model this using the geometric distribution as in
-fig.~\ref{fig:geometric}(A). However, because ecological networks are so
-sparse, there are far more negatives than positives in the dataset, and
-therefore likely to be far more false-negatives than false-positives in
-absolute terms.
+infeasible. As is evident from fig.~\ref{fig:geometric}(A), we can never
+guarantee there are no false-negatives in data. In recent years, there
+has been interest toward explicitly accounting for false-negatives in
+models (Stock \emph{et al.} 2017; Young \emph{et al.} 2021), and a
+predictive approach to networks---rather than expecting our samples to
+fully capture all interactions (Strydom \emph{et al.} 2021). As a
+result, better models for predicting interactions are needed for
+interaction networks. This includes explicitly accounting for
+observation error (Johnson \& Larremore 2021)---certain classes of
+models have been used to reflect hidden states which account for
+detection error in occupancy modeling (Joseph 2020), and could be
+integrated in the predictive models of interactions in the future.
+
+A brief caveat here is that we do not consider false-positives---in
+large part false-positives can be explained by misidentification of
+species, although this could be a relevant consideration in some cases.
+The same logic that we apply to false-negatives could easily be applied
+to false-positives, e.g.~that we can be much more confident that an
+interaction is a true positive if we have observed it 50 times rather
+than only once, and we could similarly model this using the geometric
+distribution as in fig.~\ref{fig:geometric}(A). However, because
+ecological networks are so sparse, there are far more negatives than
+positives in the dataset, and therefore likely to be far more
+false-negatives than false-positives in absolute terms.
 
@@
 
+\leavevmode\hypertarget{ref-Li2021PerCom}{}%
+Li, M., Liu, R.-R., Lü, L., Hu, M.-B., Xu, S. \& Zhang, Y.-C. (2021).
+Percolation on complex networks: Theory and application. \emph{Physics
+Reports}, Percolation on complex networks: Theory and application, 907,
+1--68.
+
 \leavevmode\hypertarget{ref-MacDonald2020RevLin}{}%

### 2022-10-16 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@31cfcfb679dec1bc17affbf09f32ce86b58a5646 🚀

@@
 {\small{\bfseries Keywords}:\par
-community ecology\\network ecology\\computational ecology\\species
+community ecology\\network ecology\\sampling effort\\species
 interactions\\spatial sampling\\simulation\\}

### 2022-10-16 src/make_fig01.jl
:art: label size change

@@ -85,7 +85,8 @@ for I in CartesianIndices(size(exp_obs))
 end
 
 function maketicks_1b(x)
-    latexstring.(["10^{$(i)}" for i in x])
+    x
+    #latexstring.(["10^{$(i)}" for i in x])
 end
 
 
@@ -218,17 +219,4 @@ end
 
 f
 
-
-ax3 = Axis(fig[2,1], 
-    xticks=0:0.1:1,
-    xlabel="Added FNR",
-    ylabel="Mean trophic level",
-    xminorgridvisible=true,
-    xminorticks=0:0.05:1,
-    yminorticksvisible=true,
-    yminorticks=0:0.5:1,
-    xlabelsize=22,
-    ylabelsize=22,
-)
-
-f |> save(joinpath("figures","fig1.png"))
+#f |> save(joinpath("figures","fig1.png"))

### 2022-10-16 src/make_fig01.jl
:pencil:

@@ -85,7 +85,7 @@ for I in CartesianIndices(size(exp_obs))
 end
 
 function maketicks_1b(x)
-    x
+    string.("1e", x)
     #latexstring.(["10^{$(i)}" for i in x])
 end
 
@@ -219,4 +219,4 @@ end
 
 f
 
-#f |> save(joinpath("figures","fig1.png"))
+f |> save(joinpath("figures","fig1.png"))

### 2022-12-18 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@4e7ced396e87a9962198ca904f1da228e8f3b6f9 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@914ef983225fde69236b315e675619d8238e904f 🚀

@@
 persist through time through both neutral and adaptive processes. Still
-a robust understanding of, and ability to predict and forecast
+a robust understanding of (and ability to predict and forecast)
 interactions among species remains elusive. This knowledge-gap is
@@
 have not yet been adopted for designing samples of communities.
+
+\hypertarget{resampling-interaction-probabilities-to-account-for-detection-error}{%
+\section{Resampling interaction probabilities to account for detection
+error}\label{resampling-interaction-probabilities-to-account-for-detection-error}}
+
+\begin{figure}
+\centering
+\includegraphics{./figures/uncertainty_sampler.png}
+\caption{todo}
+\end{figure}
 

### 2023-01-05 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@4877591b889630225f889edd6888ba8815a663e0 🚀

@@
 
-Species interactions drive many processes in evolutionary biology and
-community ecology. A better understanding of interactions among species
-is an imperative to both mitigate the potentially harmful impacts of
-anthropogenic change on Earth's biodiversity (Makiola \emph{et al.}
-2020) and to predict zoonotic spillover of disease to prevent future
-pandemics (Becker \emph{et al.} 2021). However, meeting these challenges
-is difficult because interactions are intrinsically hard to sample
-(Jordano 2016). Over the past few decades biodiversity data has become
-increasingly available---for example, remote-sensing has enabled
-collection of data on spatial scales and resolutions previously
-unimaginable (Stephenson 2020), while the adoption of open data
-practices (Kenall \emph{et al.} 2014) have substantially increased the
-amount of data available to ecologists. Still, widespread data about
-species interactions remains elusive (Poisot \emph{et al.} 2021).
-Observing an interaction between two species often requires human
-observation because remote sampling methods can primarily detect
-co-occurrence (but see Niedballa \emph{et al.} (2019)), and this itself
-is not necessarily indicative of an interaction (Blanchet \emph{et al.}
-2020). This constraint induces biases on species interaction data
-subject to the spatial and temporal scales that current observation
-methods can feasibly sample. This is further compounded by semantic
-confusion around the word ``interaction''---for example one might
-consider competition a type of species interaction, even though it is
-marked by a lack of co-occurrence between species, unlike other types of
-interactions, like trophism or pollination, which require both species
-to be together at the same place and time. We define interaction in the
-latter sense, where two species have fitness consequences on one-another
-if they are in the sample place at the same time. In addition, here we
-only consider direct (not higher-order) interactions.
-
-The importance of \emph{sampling effort} and its impact on resulting
-ecological data has produced a rich body of literature. The recorded
-number of species in a dataset or sample depends on the total number of
-observations (Walther \emph{et al.} 1995; Willott 2001)---as do
-estimates of population abundance (Griffiths 1998)---in addition to
-spatial coverage and species detectability. This has motivated more
-quantitatively robust approaches to account for error in sampling data
-in many contexts: to determine if a given species is extinct (Boakes
-\emph{et al.} 2015), to determine sampling design (Moore \& McCarthy
-2016), and to measure species richness across large scales (Carlson
-\emph{et al.} 2020). In the context of interactions, an initial concern
-was the compounding effects of limited sampling effort combined with the
-amalgamation of data (across both study sites, time of year, and
-taxonomic scales) could lead any empirical set of observations to
-inadequately reflect the reality of how species interact (Paine 1988) or
-the structure of the network as a whole (Martinez \emph{et al.} 1999;
-McLeod \emph{et al.} 2021). Martinez \emph{et al.} (1999) showed that in
-a plant-endophyte trophic network, network connectance is robust to
-sampling effort, but this was done in the context of a system for which
-observation of 62,000 total interactions derived from 164,000
-plant-stems was feasible. In some systems (e.g.~megafauna food-webs)
-this many observations is either impractical or infeasible due to the
-absolute abundance of the species in question.
+Species interactions drive many processes in evolution and ecology. A
+better understanding of species interactions is an imperative to
+understand the evolution of life on Earth, to mitigate the impacts of
+anthropogenic change on biodiversity (Makiola \emph{et al.} 2020), and
+for predicting zoonotic spillover of disease to prevent future pandemics
+(Becker \emph{et al.} 2021). At the moment we lack sufficient data to
+meet these challenges (Poisot \emph{et al.} 2021), largely because
+species interactions are hard to sample (Jordano 2016). Over the past
+few decades biodiversity data has become increasingly available through
+remotely collected data and adoption of open data practices (Kenall
+\emph{et al.} 2014; Stephenson 2020). Still, interaction data remains
+relatively scarce because sampling typically requires human observation.
+This induces a constraint on the amount, spatial scale, and temporal
+frequency of resulting data that it is feasible to collect by humans.
+Many crowdsourced methods for biodiversity data aggregation (e.g.~GBIF,
+eBird) still relies on automated identification of species, which does
+not easily generalize to interaction sampling. There is interest in
+using remote methods for interaction sampling, which primarily detect
+co-occurrence and derive properties like species avoidance from this
+data (Niedballa \emph{et al.} 2019). However, this itself is not
+necessarily indicative of an interaction (Blanchet \emph{et al.} 2020).
+This is an example of semantic confusion around the word
+``interaction''---for example one might consider competition a type of
+species interaction, even though it is marked by a lack of co-occurrence
+between species, unlike other types of interactions, like trophism or
+pollination, which require both species to be together at the same place
+and time. Here we consider interaction in the latter sense, where two
+species have fitness consequences on one-another if (and only if) they
+are in the sample place at the same time. In addition, here we only
+consider direct (not higher-order) interactions.
 
@@
 
+The importance of \emph{sampling effort} and its impact on resulting
+ecological data has produced a rich body of literature.The recorded
+number of species in a dataset or sample depends on the total number of
+observations (Walther \emph{et al.} 1995; Willott 2001), as do estimates
+of population abundance (Griffiths 1998). This relationship between
+sampling effort and spatial coverage and species detectability . This
+has motivated more quantitatively robust approaches to account for error
+in sampling data in many contexts: to determine if a given species is
+extinct (Boakes \emph{et al.} 2015), to determine sampling design (Moore
+\& McCarthy 2016), and to measure species richness across large scales
+(Carlson \emph{et al.} 2020). In the context of interactions, an initial
+concern was the compounding effects of limited sampling effort combined
+with the amalgamation of data (across both study sites, time of year,
+and taxonomic scales) could lead any empirical set of observations to
+inadequately reflect the reality of how species interact (Paine 1988) or
+the structure of the network as a whole (Martinez \emph{et al.} 1999;
+McLeod \emph{et al.} 2021). Martinez \emph{et al.} (1999) showed that in
+a plant-endophyte trophic network, network connectance is robust to
+sampling effort, but this was done in the context of a system for which
+observation of 62,000 total interactions derived from 164,000
+plant-stems was feasible. In some systems (e.g.~megafauna food-webs)
+this many observations is either impractical or infeasible due to the
+absolute abundance of the species in question.
+
 The intrinsic properties of ecological communities create several
@@
 Here, we illustrate how our confidence that a pair of species never
-interacts highly depends on sampling effort, and suggest that surveys of
+interacts highly depends on sampling effort. We suggest that surveys of
 species interactions can benefit from simulation modeling of the
@@
 null estimate of the false-negative rate given total sampling effort
-(the total count of all individuals of all species seen). We show that
-positive associations in co-occurrence data can increase the realized
-number of false-negatives, and demonstrate these positive associations
-are rampant in network datasets. We conclude by recommending that the
-simulation of sampling effort and species occurrence can and should be
-used to help design surveys of species interaction diversity (Moore \&
-McCarthy 2016), and by advocating use of null models like those
-presented here as a tool for both guiding design of surveys of species
-interactions and for modeling detection error in predictive models.
+(the total count of all individuals of all species seen). We also
+introduce a method for resampling of model predictions of interaction
+probability to account for observation error. We show that positive
+associations in co-occurrence data can increase the realized number of
+false-negatives, and demonstrate these positive associations are rampant
+in network datasets. We conclude by recommending that the simulation of
+sampling effort and species occurrence can and should be used to help
+design surveys of species interaction diversity (Moore \& McCarthy
+2016), and by advocating use of null models like those presented here as
+a tool for both guiding design of surveys of species interactions and
+for modeling detection error in predictive models.
 
@@
 
-\hypertarget{resampling-interaction-probabilities-to-account-for-detection-error}{%
-\section{Resampling interaction probabilities to account for detection
-error}\label{resampling-interaction-probabilities-to-account-for-detection-error}}
+\hypertarget{resampling-interaction-probabilities-to-account-for-uncertainty-in-detection-error}{%
+\section{Resampling interaction probabilities to account for uncertainty
+in detection
+error}\label{resampling-interaction-probabilities-to-account-for-uncertainty-in-detection-error}}
+
+Here we show how to incorporate imperfect detection (both
+false-negatives and false-positives) into model predictions of
+interaction probability. Models for interaction prediction typically
+yield a probability of interaction between each pair of species. When
+these are considered with uncertainty, it is usually model-uncertainty,
+e.g.~the variance in the interaction probability prediction across
+several cross-validation folds, where the data is split into training
+and test sets several times.Here we introduce a method for resampling
+interaction probabilities (outlined in figure fig.~\ref{fig:resampling})
+that simulates the observation process with prior estimates of both
+false-negative and false-positive probabilities to produce an output
+distribution of interaction probability that accounts for observation
+error. We implement this in the software package
+InteractionUncertaintySampler.jl.
 
@@
 \includegraphics{./figures/uncertainty_sampler.png}
-\caption{todo}
+\caption{FIG CAPTION}
 \end{figure}
+
+We do this by using the process for simulating a distribution of null
+false-negative rates for a given dataset as described above
+(fig.~\ref{fig:resampling_concept} (A)). We then consider the output
+prediction from an arbitrary prediction model, which is the probability
+\(p_{ij}\) that two species \(i\) and \(j\) interact. To get an estimate
+of \(p_{ij}\) that accounts for observation error, we resample the
+probability of each interaction \(p_{ij}\) by simulating a series of
+particles. Each particle is the product of the resampling algorithm
+(``Resampling'' within fig.~\ref{fig:resampling:concept} (B)), where the
+value of a particle is first drawn from a Bernoulli with weight
+\(p_{ij}\), and if that value is true, the value remains true with
+probability \(1-p_{fn}\), and if the first draw is false, the value
+remains false with probability \(1-p_{fp}\). Over many samples of
+particles, the resulting frequency of `true' outcomes is a single
+resample of the interaction probability \(p_{ij}^*\). Across many
+resamples, this forms a distribution of probabilities which are adjusted
+by the true and false negative rates.
+
+As an example case study, we use a boosted-regresssion-tree to predict
+interactions in a host-parasite network (Hadfield \emph{et al.} 2014)
+(with features derived in the same manner as Strydom \emph{et al.}
+(2021) derives features on this data) to produce a set of interaction
+predictions. We then applied this method to a set of a few resampled
+interaction probabilities between mammals and parasite species shown in
+figure fig.~\ref{fig:resampling_concept} (C). Here we implement a simple
+resampling algorithm, but this could be extended, for example by
+adjusting the expected FNR for each pair of species by the relative
+abundance of each species. We have implemented a general framework for
+this resampling methodology in the Julia package
+InteractionUncertaintySampler.jl, which enables flexible choices for
+priors on false-negative and false-positive rates.
+
+This method allows us to more effectively represent our uncertainty
+about observation error in predictions of species interactions. This
+also has implications for what we mean by `uncertainty' in interaction
+predictions. A model's prediction can be `uncertain' in two different
+ways: the model's predictions may have high variance, or the model's
+predictions may be centered around a probability of interaction of
+\(0.5\), where we are the most unsure about whether this interaction
+exists. A more statistically robust framework for accounting for
+different forms of uncertainty in probabilistic interaction predictions
+seems a necessary goal that the field must undertake.
 
@@
 
-This model above doesn't consider the possibility that there are
-positive or negative associations which shift the probability of
-observing two species together due to their interaction (Cazelles
-\emph{et al.} 2016). However, here we demonstrate that the probability
-of observing a false negative can be higher if there is some positive
-association in the occurrence of species \(A\) and \(B\). If we denote
-the probability that we observe the co-occurrence of two species \(A\)
-and \(B\) as \(P(AB)\) and if there is no association between the
-marginal probabilities of observing \(A\) and observing \(B\), denoted
-\(P(A)\) and \(P(B)\) respectively, then the probability of observing
-their co-occurrence is the product of the marginal probabilities for
-each species, \(P(AB) = P(A)P(B)\). In the other case where there is
-some positive strength of association between observing both \(A\) and
-\(B\) because this interaction is ``important'' for each species, then
-the probability of observation both \(A\) and \(B\), \(P(AB)\), is
-greater than \(P(A)P(B)\) as \(P(A)\) and \(P(B)\) are not independent
-and instead are positively correlated, i.e.~\(P(AB)> P(A)P(B)\). In this
+The model above doesn't consider the possibility that there are positive
+or negative associations which shift the probability of species
+cooccurrence together due to their interaction (Cazelles \emph{et al.}
+2016). However, here we demonstrate that the probability of observing a
+false negative can be higher if there is some positive association in
+the occurrence of species \(A\) and \(B\). If we denote the probability
+that we observe the co-occurrence of two species \(A\) and \(B\) as
+\(P(AB)\) and if there is no association between the marginal
+probabilities of observing \(A\) and observing \(B\), denoted \(P(A)\)
+and \(P(B)\) respectively, then the probability of observing their
+co-occurrence is the product of the marginal probabilities for each
+species, \(P(AB) = P(A)P(B)\). In the other case where there is some
+positive strength of association between observing both \(A\) and \(B\)
+because this interaction is ``important'' for each species, then the
+probability of observation both \(A\) and \(B\), \(P(AB)\), is greater
+than \(P(A)P(B)\) as \(P(A)\) and \(P(B)\) are not independent and
+instead are positively correlated, i.e.~\(P(AB)> P(A)P(B)\). In this
 case, the probability of observing a single false-negative in our naive
@@
 
-A brief caveat here is that we do not consider false-positives---in
-large part false-positives can be explained by misidentification of
-species, although this could be a relevant consideration in some cases.
-The same logic that we apply to false-negatives could easily be applied
-to false-positives, e.g.~that we can be much more confident that an
-interaction is a true positive if we have observed it 50 times rather
-than only once, and we could similarly model this using the geometric
-distribution as in fig.~\ref{fig:geometric}(A). However, because
-ecological networks are so sparse, there are far more negatives than
-positives in the dataset, and therefore likely to be far more
-false-negatives than false-positives in absolute terms.
-
 This work has several practical consequences for the design of
@@
 in this spatial prioritization of sampling sites.
+
+We also should address the impact of false-negatives on the inference of
+process and causity in community ecology. We demonstrated that in model
+food webs, false-negatives do not impact the measure of total trophic
+levels until very high FNR (figure fig.~\ref{fig:addedfnr}(C)), although
+we cannot generalize this further to other properties. This has
+immediate practical concern for how we design what taxa to sample---does
+it matter if the sampled network is fully connected? It has been shown
+that the stability of subnetworks can be used to infer the stability of
+the metaweb paper beyond a threshold of samples
+(\textbf{Song2022RapMon?}). But does this extend to other network
+properties? And how can we be sure we are at the threshold at which we
+can be confident our sample characterizes the whole system?
+
+To try and sample to avoid all false-negatives is a fool's errand.
+Species ranges overlap to form mosaics, which themselves are often
+changing in time. Communities and networks don't end in space, and the
+interactions that connect species on the `periphery' of a given network
+to species outside the spatial extent of a given sample will inevitably
+appear as false-negatives in practical samples. The goal should instead
+be to sample enough to have a statistically robust estimate of the
+current state and empirical change over time of an ecological community
+at a given spatial extent and temporal resolution, and to determine what
+the sampling effort required the describe the current state prior to
+sampling.
 

### 2023-01-05 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@38a9c1bcb3e8abf02dc58524703f3dda58235431 🚀

@@
 We also should address the impact of false-negatives on the inference of
-process and causity in community ecology. We demonstrated that in model
-food webs, false-negatives do not impact the measure of total trophic
-levels until very high FNR (figure fig.~\ref{fig:addedfnr}(C)), although
-we cannot generalize this further to other properties. This has
+process and causality in community ecology. We demonstrated that in
+model food webs, false-negatives do not impact the measure of total
+trophic levels until very high FNR (figure fig.~\ref{fig:addedfnr}(C)),
+although we cannot generalize this further to other properties. This has
 immediate practical concern for how we design what taxa to sample---does
@@
 properties? And how can we be sure we are at the threshold at which we
-can be confident our sample characterizes the whole system?
-
-To try and sample to avoid all false-negatives is a fool's errand.
-Species ranges overlap to form mosaics, which themselves are often
-changing in time. Communities and networks don't end in space, and the
-interactions that connect species on the `periphery' of a given network
-to species outside the spatial extent of a given sample will inevitably
-appear as false-negatives in practical samples. The goal should instead
-be to sample enough to have a statistically robust estimate of the
+can be confident our sample characterizes the whole system? We suggest
+that modeling observation error like we have done here can address these
+questions and aid in the design of samples of species interactions. To
+try and sample to avoid all false-negatives is a fool's errand. Species
+ranges overlap to form mosaics, which themselves are often changing in
+time. Communities and networks don't end in space, and the interactions
+that connect species on the `periphery' of a given network to species
+outside the spatial extent of a given sample will inevitably appear as
+false-negatives in practical samples. The goal should instead be to
+sample a system enough to have a statistically robust estimate of the
 current state and empirical change over time of an ecological community
 at a given spatial extent and temporal resolution, and to determine what
-the sampling effort required the describe the current state prior to
-sampling.
+the sampling effort required prior to sampling.
 

### 2023-01-05 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@12603ebc333b15dba0c32d0dd8223a4392f12f8f 🚀

@@
 \begin{figure}
+\hypertarget{fig:resampling_concept}{%
 \centering
 \includegraphics{./figures/uncertainty_sampler.png}
-\caption{FIG CAPTION}
+\caption{(A) The process for estimating the false-negative rate (FNR)
+for an interaction dataset consisting of \(N\) total observed
+interactions. (B) The method for resampling interaction probability
+based on estimates of false-negative and false-positive rates. (C) The
+method for interaction probability resampling applied to three mammals
+and three parasites from the Hadfield \emph{et al.} (2014)
+dataset.}\label{fig:resampling_concept}
+}
 \end{figure}
@@
 particles. Each particle is the product of the resampling algorithm
-(``Resampling'' within fig.~\ref{fig:resampling:concept} (B)), where the
+(``Resampling'' within fig.~\ref{fig:resampling_concept} (B)), where the
 value of a particle is first drawn from a Bernoulli with weight
@@
 relevant as we have strong evidence that generalism drives abundance
-(Song \emph{et al.} 2022), not vice-versa.
+(Song \emph{et al.} 2022a), not vice-versa.
 
@@
 that the stability of subnetworks can be used to infer the stability of
-the metaweb paper beyond a threshold of samples
-(\textbf{Song2022RapMon?}). But does this extend to other network
-properties? And how can we be sure we are at the threshold at which we
-can be confident our sample characterizes the whole system? We suggest
-that modeling observation error like we have done here can address these
-questions and aid in the design of samples of species interactions. To
-try and sample to avoid all false-negatives is a fool's errand. Species
-ranges overlap to form mosaics, which themselves are often changing in
-time. Communities and networks don't end in space, and the interactions
-that connect species on the `periphery' of a given network to species
-outside the spatial extent of a given sample will inevitably appear as
-false-negatives in practical samples. The goal should instead be to
-sample a system enough to have a statistically robust estimate of the
-current state and empirical change over time of an ecological community
-at a given spatial extent and temporal resolution, and to determine what
-the sampling effort required prior to sampling.
+the metaweb paper beyond a threshold of samples (Song \emph{et al.}
+2022b). But does this extend to other network properties? And how can we
+be sure we are at the threshold at which we can be confident our sample
+characterizes the whole system? We suggest that modeling observation
+error like we have done here can address these questions and aid in the
+design of samples of species interactions. To try and sample to avoid
+all false-negatives is a fool's errand. Species ranges overlap to form
+mosaics, which themselves are often changing in time. Communities and
+networks don't end in space, and the interactions that connect species
+on the `periphery' of a given network to species outside the spatial
+extent of a given sample will inevitably appear as false-negatives in
+practical samples. The goal should instead be to sample a system enough
+to have a statistically robust estimate of the current state and
+empirical change over time of an ecological community at a given spatial
+extent and temporal resolution, and to determine what the sampling
+effort required prior to sampling.
 
@@
 \leavevmode\hypertarget{ref-Song2022GenDri}{}%
-Song, C., Simmons, B.I., Fortin, M.-J. \& Gonzalez, A. (2022).
+Song, C., Simmons, B.I., Fortin, M.-J. \& Gonzalez, A. (2022a).
 Generalism drives abundance: A computational causal discovery approach.
 \emph{PLOS Computational Biology}, 18, e1010302.
+
+\leavevmode\hypertarget{ref-Song2022RapMon}{}%
+Song, C., Simmons, B.I., Fortin, M.-J., Gonzalez, A., Kaiser-Bunbury,
+C.N. \& Saavedra, S. (2022b). Rapid monitoring for ecological
+persistence.
 

### 2023-01-05 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@ab62cf600d034460d39948077a44200a6a67d657 🚀

@@
 species interactions can benefit from simulation modeling of the
-sampling process. We demonstrate that the realized false-negative rate
-of interactions is directly related to the relative abundance of the
-species pool, and demonstrate how simulation can be used to produce a
-null estimate of the false-negative rate given total sampling effort
-(the total count of all individuals of all species seen). We also
-introduce a method for resampling of model predictions of interaction
-probability to account for observation error. We show that positive
-associations in co-occurrence data can increase the realized number of
-false-negatives, and demonstrate these positive associations are rampant
-in network datasets. We conclude by recommending that the simulation of
-sampling effort and species occurrence can and should be used to help
-design surveys of species interaction diversity (Moore \& McCarthy
-2016), and by advocating use of null models like those presented here as
-a tool for both guiding design of surveys of species interactions and
-for modeling detection error in predictive models.
+sampling process. We demonstrate how the realized false-negative rate of
+interactions is related to the relative abundance of the species pool,
+and use simulation to produce a null estimate of the false-negative rate
+given total sampling effort (the total count of all individuals of all
+species seen), and to introduce a method for resampling of model
+predictions of interaction probability to account for observation error.
+We then show that positive associations in co-occurrence data can
+increase the realized number of false-negatives, and demonstrate these
+positive associations are rampant in network datasets, and conclude by
+recommending that the simulation of sampling effort and species
+occurrence can and should be used to help design surveys of species
+interaction diversity (Moore \& McCarthy 2016), and by advocating use of
+null models like those presented here as a tool for both guiding design
+of surveys of species interactions and for modeling detection error in
+predictive models.
 
@@
 not-interacting with an independent and fixed probability, which we
-denote \(p_fn\) and subsequently refer to as the False-Negative Rate
+denote \(p_{fn}\) and subsequently refer to as the False-Negative Rate
 (FNR). If we observe the same species not-interacting \(N\) times, then
@@
 
-\hypertarget{resampling-interaction-probabilities-to-account-for-uncertainty-in-detection-error}{%
+\hypertarget{resampling-interaction-probabilities-to-account-for-uncertainty-in-observation-error}{%
 \section{Resampling interaction probabilities to account for uncertainty
-in detection
-error}\label{resampling-interaction-probabilities-to-account-for-uncertainty-in-detection-error}}
-
-Here we show how to incorporate imperfect detection (both
+in observation
+error}\label{resampling-interaction-probabilities-to-account-for-uncertainty-in-observation-error}}
+
+Here we show how to incorporate imperfect observation (both
 false-negatives and false-positives) into model predictions of
@@
 several cross-validation folds, where the data is split into training
-and test sets several times.Here we introduce a method for resampling
-interaction probabilities (outlined in figure fig.~\ref{fig:resampling})
-that simulates the observation process with prior estimates of both
-false-negative and false-positive probabilities to produce an output
-distribution of interaction probability that accounts for observation
-error. We implement this in the software package
-InteractionUncertaintySampler.jl.
+and test sets several times. Here we introduce a method for resampling
+interaction probabilities (outlined in figure
+fig.~\ref{fig:resampling_concept}) that simulates the observation
+process with prior estimates of both false-negative and false-positive
+probabilities to produce an output distribution of interaction
+probabilities that accounts for observation error. We implement this in
+the software package InteractionUncertaintySampler.jl.
 
@@
 \(0.5\), where we are the most unsure about whether this interaction
-exists. A more statistically robust framework for accounting for
-different forms of uncertainty in probabilistic interaction predictions
-seems a necessary goal that the field must undertake.
+exists. Improving the incorporation of different forms of uncertainty in
+probabilistic interaction predictions seems a necessary next step toward
+understanding what pairs of species we know the least about, in order to
+prioritize sampling to provide the most new information possible.
 

### 2023-01-13 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@71f6201b5796e81becc17c4b88b6c3b0bb13905a 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@b0addac00a346b8ccd6a34ff1c11d4b9c9736697 🚀

@@
 given total sampling effort (the total count of all individuals of all
-species seen), and to introduce a method for resampling of model
-predictions of interaction probability to account for observation error.
-We then show that positive associations in co-occurrence data can
-increase the realized number of false-negatives, and demonstrate these
-positive associations are rampant in network datasets, and conclude by
-recommending that the simulation of sampling effort and species
-occurrence can and should be used to help design surveys of species
-interaction diversity (Moore \& McCarthy 2016), and by advocating use of
-null models like those presented here as a tool for both guiding design
-of surveys of species interactions and for modeling detection error in
-predictive models.
+species seen), and to introduce a method for introducing uncertainty
+into model predictions of interaction probability to account for
+observation error. We then show that positive associations in
+co-occurrence data can increase the realized number of false-negatives,
+and demonstrate these positive associations are rampant in network
+datasets, and conclude by recommending that the simulation of sampling
+effort and species occurrence can and should be used to help design
+surveys of species interaction diversity (Moore \& McCarthy 2016), and
+by advocating use of null models like those presented here as a tool for
+both guiding design of surveys of species interactions and for modeling
+detection error in predictive models.
 
@@
 
+\hypertarget{accounting-for-false-negatives-in-species-interactions}{%
+\section{Accounting for false-negatives in species
+interactions}\label{accounting-for-false-negatives-in-species-interactions}}
+
 \hypertarget{how-many-observations-of-a-non-interaction-do-we-need-to-be-confident-its-a-true-negative}{%
-\section{How many observations of a non-interaction do we need to be
+\subsection{How many observations of a non-interaction do we need to be
 confident it's a true
@@
 \hypertarget{false-negatives-as-a-product-of-relative-abundance}{%
-\section{False-negatives as a product of relative
+\subsection{False-negatives as a product of relative
 abundance}\label{false-negatives-as-a-product-of-relative-abundance}}
@@
 using both EcologicalNetworks.jl v0.5 and Mangal.jl v0.4 (Banville
-\emph{et al.} 2021) and are hosted at (GITHUB\_LINK\_TODO). Note that
-the empirical data, for the reasons described above, very likely already
-contains many false negatives, we'll revisit this issue in the final
-section.
+\emph{et al.} 2021) and are hosted on
+\href{https://github.com/gottacatchenall/ms_false_negatives/tree/main/src}{Github}).
+Note that the empirical data, for the reasons described above, very
+likely already contains many false negatives, we'll revisit this issue
+in the final section.
 
@@
 
-\hypertarget{resampling-interaction-probabilities-to-account-for-uncertainty-in-observation-error}{%
-\section{Resampling interaction probabilities to account for uncertainty
-in observation
-error}\label{resampling-interaction-probabilities-to-account-for-uncertainty-in-observation-error}}
+\hypertarget{including-observation-error-in-interaction-predictions}{%
+\subsection{Including observation-error in interaction
+predictions}\label{including-observation-error-in-interaction-predictions}}
 
@@
 
+There is also an analytic way to represent this.
+
+Normal approximation to binomial, as the total number of samples from
+\(n_p\) particles approaches infinity, the sum of total successes across
+all particles approaches a normal distribution with parameters
+
+\[\mathcal{N}\bigg(n_p p_{ij}, \sqrt{n_p p_{ij}(1-p_{ij})}\bigg)\]
+
+Corrected \(p_{ij}\) based on \(p_fn\) and \(p_tn\) as
+\(p_{ij}^* = p_{ij}(1+p_{fp})(1-p_{fn})\)
+\[\mathcal{N}\bigg(n_p p_{ij}^*, \sqrt{n_p p_{ij}^* (1-p_{ij}^*)}\bigg)\]
+
+and then by normalizing back to \((0,1)\).
+
+\[\mathcal{N}\bigg(p^*_{ij}, \sqrt{\frac{ p_{ij}(1-p_{ij})}{n_p}} \bigg)\]
+
+We can then further truncate this, although in practice probability mass
+outside (0,1) is exteremly loss.
+
+Number of particles \(n_p\) as a uncertainty width. Nautral analogue to
+number of observations of co-occurrence.
+
 As an example case study, we use a boosted-regresssion-tree to predict
@@
 
-\hypertarget{positive-associations-increase-the-false-negative-rate}{%
-\section{Positive associations increase the false-negative
-rate}\label{positive-associations-increase-the-false-negative-rate}}
+\hypertarget{positive-associations-in-co-occurrence-increase-the-false-negative-rate}{%
+\section{Positive associations in co-occurrence increase the
+false-negative
+rate}\label{positive-associations-in-co-occurrence-increase-the-false-negative-rate}}
 

### 2023-01-14 src/_possible_new_1b.jl
:pencil:

@@ -1,43 +1,0 @@
-using CairoMakie, Distributions
-using MathTeXEngine
-using MathTeXEngine: latexstring
-CairoMakie.activate!(; px_per_unit=2)
-
-
-p_a = 0.01:0.01:0.5
-p_b = 0.01:0.01:0.5
-
-
-exp_obs = zeros(length(p_a), length(p_b))
-
-expectednumobs(target_negatives, p_a, p_b) = target_negatives/(p_a*p_b)
-
-
-# p_a = 0.1, p_b = 0.2
-# how many of all species to see this pair 5 times?
-# 0.1  *  0.2
-
-# to see A and B once, you need an expected 1/(p_a*p_b) exp_obs
-
-targ = 10
-for I in CartesianIndices(size(exp_obs))
-    exp_obs[I] = expectednumobs(targ, p_a[I[1]], p_a[I[2]])
-end
-
-function maketicks(x)
-    latexstring.(["10^{$(i)}" for i in x])
-end
-
-fig = Figure(resolution=(800,700))
-ax = Axis(fig[1,1], xlabel=L"P(A)", ylabel=L"P(B)", xlabelsize=22,
-ylabelsize=22)
-limits!(ax,0.01,0.5,0.01,0.5)
-co = contourf!(ax, p_a, p_b, log10.(exp_obs), colorlimits=1:5, levels=range(1,5, length = 10))
-Colorbar(fig[1,2], co, ticksize=20, label="Expected number of observations of all individuals to see A and B together 10 times",ticks=[i for i in 1:0.5:5], tickformat=maketicks)
-
-
-
-
-fig
-
-fig |> save("new_1b.png")

### 2023-01-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@759db482cfa330994be4f0b8aaca418da6e11e4d 🚀

@@
 \hypertarget{including-observation-error-in-interaction-predictions}{%
-\subsection{Including observation-error in interaction
+\subsection{Including observation error in interaction
 predictions}\label{including-observation-error-in-interaction-predictions}}
@@
 
-There is also an analytic way to represent this.
-
-Normal approximation to binomial, as the total number of samples from
-\(n_p\) particles approaches infinity, the sum of total successes across
-all particles approaches a normal distribution with parameters
-
-\[\mathcal{N}\bigg(n_p p_{ij}, \sqrt{n_p p_{ij}(1-p_{ij})}\bigg)\]
-
-Corrected \(p_{ij}\) based on \(p_fn\) and \(p_tn\) as
-\(p_{ij}^* = p_{ij}(1+p_{fp})(1-p_{fn})\)
-\[\mathcal{N}\bigg(n_p p_{ij}^*, \sqrt{n_p p_{ij}^* (1-p_{ij}^*)}\bigg)\]
-
-and then by normalizing back to \((0,1)\).
-
-\[\mathcal{N}\bigg(p^*_{ij}, \sqrt{\frac{ p_{ij}(1-p_{ij})}{n_p}} \bigg)\]
-
-We can then further truncate this, although in practice probability mass
-outside (0,1) is exteremly loss.
-
-Number of particles \(n_p\) as a uncertainty width. Nautral analogue to
-number of observations of co-occurrence.
+There is also an analytic way to represent approximate this distribution
+using the normal approximation to binomial. As a reminder, as the total
+number of samples \(n\) from a binomial distribution with success
+probability \(p\) from approaches infinity, the sum of total successes
+across all samples approaches a normal distribution with mean \(np\) and
+variance \(np(1-p)\). We can use this to correct the estimate \(p_{ij}\)
+based on the expected false-negative-rate \(p_{fn}\) and false-positive
+rate \(p_{fp}\) to obtain the limiting distribution as the number of
+resamples approaches infinity for the resampled \(p_{ij}^*\) for a given
+number of particles \(n_p\). We do this by first adjusting for the rates
+of observation error to get the mean resampled probability,
+\(\bar{p_{ij}^*}\), as
+
+\[\bar{p_{ij}^*} = p_{ij}(1+p_{fp})(1-p_{fn})\]
+
+which yields the normal approximation
+
+\[\mathcal{N}\bigg(n_p \bar{p_{ij}^*}, \sqrt{n_p \bar{p_{ij}^*} (1-\bar{p_{ij}^*})}\bigg)\]
+
+which then can be converted back to a distribution of frequency of
+successes to yield the final approximation
+
+\begin{equation}\protect\hypertarget{eq:eq1}{}{\mathcal{N}\bigg(\bar{p^*_{ij}},
+\sqrt{\frac{\bar{p_{ij}^*}(1-\bar{p_{ij}^*})}{n_p}} \bigg)}\label{eq:eq1}\end{equation}
+
+We can then further truncate to remain on the interval \((0,1)\) (as the
+output is a probability, although in practice often the probability mass
+outside \((0,1)\) is exteremly low.
+
+Why is this useful? Less computation, number of particles \(n_p\) as a
+uncertainty width, nautral analogue to number of observations of
+co-occurrence. More about this here.
 

### 2023-01-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@248cde172ef469d2562cfb1e543110f64eef9496 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@fc540949f9b43d58c34c27f827e5607a20741112 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@7aa656d41d88975532ffd237498f5e8ea2810b9f 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@9b70121eb438d5e5abf30cfe4042a4c7f958fe22 🚀

@@
 %
-\,\textsuperscript{1,2}
+\,\textsuperscript{1,4}
 
@@
 Centre for Biodiversity Sciences\quad \textsuperscript{3}\,Université de
-Montréal
+Montréal\quad \textsuperscript{4}\,Québec Centre for Biodiversity
+Science
 
@@
 community. We illustrate how a null model of occurrence detection can be
-used to estimate the false-negative rate in a given dataset. One
-hypothesis is that interactions between ``rare'' species are themselves
-rare because these species are less likely to encounter one-another than
-species of higher relative abundance. However, we demonstrate that
-across several datasets of spatial or temporally replicated networks,
-there are positive associations that suggest these interactions actually
-exist but just are not observed. Finally, we assess how false negatives
-influence various models of network prediction, and recommend directly
-accounting for observation error in predictive models. We conclude by
-discussing how the understanding of false-negatives can inform how we
-design monitoring schemes for species interactions.\\%
+used to estimate the false-negative rate in a given dataset. We also
+show how to directly incorporate uncertainty due to observation error
+into model-based predictions of interaction probabilities between
+species. One hypothesis is that interactions between ``rare'' species
+are themselves rare because these species are less likely to encounter
+one-another than species of higher relative abundance. However, we
+demonstrate that across several datasets of spatial or temporally
+replicated networks, there are positive associations that suggest these
+interactions actually exist but just are not observed. Finally, we
+assess how false negatives influence various models of network
+prediction, and recommend directly accounting for observation error in
+predictive models. We conclude by discussing how the understanding of
+false-negatives can inform how we design monitoring schemes for species
+interactions.\\%
 
@@
 both---in these \(n\) observations, but \(M_{ij}=1\), this is counted as
-a false-negative, and a true-negative otherwise (\(M_{ij} = 0\)).
+a false-negative, and a true-negative otherwise (\(M_{ij} = 0\)). This
+process is illustrated conceptually in
+fig.~\ref{fig:resampling_concept}(A).
 
@@
 
-Here we show how to incorporate imperfect observation (both
-false-negatives and false-positives) into model predictions of
-interaction probability. Models for interaction prediction typically
-yield a probability of interaction between each pair of species. When
-these are considered with uncertainty, it is usually model-uncertainty,
-e.g.~the variance in the interaction probability prediction across
-several cross-validation folds, where the data is split into training
-and test sets several times. Here we introduce a method for resampling
-interaction probabilities (outlined in figure
-fig.~\ref{fig:resampling_concept}) that simulates the observation
-process with prior estimates of both false-negative and false-positive
-probabilities to produce an output distribution of interaction
-probabilities that accounts for observation error. We implement this in
-the software package InteractionUncertaintySampler.jl.
+Here we show how to incorporate uncertainty into model predictions of
+interaction probability to account for imperfect observation (both
+false-negatives and false-positives). Models for interaction prediction
+typically yield a probability of interaction between each pair of
+species, \(p_{ij}\). When these are considered with uncertainty, it is
+usually model-uncertainty, e.g.~the variance in the interaction
+probability prediction across several cross-validation folds, where the
+data is split into training and test sets several times. The method we
+introduce adjusts the value of a model's predictions to produce a
+distribution of interaction probabilities, which are adjusted by a given
+false-negative-rate \(p_{fn}\) and false-positive-rate \(p_{fp}\)
+(outlined in figure fig.~\ref{fig:resampling_concept}). We describe
+first how to sample from this distribution of adjusted interaction
+probabilities via simulation, and show that this distribution can be
+well-approximated analytically.
 
@@
 
-We do this by using the process for simulating a distribution of null
-false-negative rates for a given dataset as described above
-(fig.~\ref{fig:resampling_concept} (A)). We then consider the output
-prediction from an arbitrary prediction model, which is the probability
-\(p_{ij}\) that two species \(i\) and \(j\) interact. To get an estimate
-of \(p_{ij}\) that accounts for observation error, we resample the
-probability of each interaction \(p_{ij}\) by simulating a series of
-particles. Each particle is the product of the resampling algorithm
-(``Resampling'' within fig.~\ref{fig:resampling_concept} (B)), where the
-value of a particle is first drawn from a Bernoulli with weight
-\(p_{ij}\), and if that value is true, the value remains true with
-probability \(1-p_{fn}\), and if the first draw is false, the value
-remains false with probability \(1-p_{fp}\). Over many samples of
-particles, the resulting frequency of `true' outcomes is a single
-resample of the interaction probability \(p_{ij}^*\). Across many
-resamples, this forms a distribution of probabilities which are adjusted
-by the true and false negative rates.
-
-There is also an analytic way to represent approximate this distribution
-using the normal approximation to binomial. As a reminder, as the total
-number of samples \(n\) from a binomial distribution with success
-probability \(p\) from approaches infinity, the sum of total successes
-across all samples approaches a normal distribution with mean \(np\) and
-variance \(np(1-p)\). We can use this to correct the estimate \(p_{ij}\)
-based on the expected false-negative-rate \(p_{fn}\) and false-positive
-rate \(p_{fp}\) to obtain the limiting distribution as the number of
+We then consider the output prediction from an arbitrary prediction
+model, which is the probability \(p_{ij}\) that two species \(i\) and
+\(j\) interact. To get an estimate of \(p_{ij}\) that accounts for
+observation error, we resample the probability of each interaction
+\(p_{ij}\) by simulating a set of several `particles,' where each
+particle is a realization of an interaction occurring (either true or
+false with probabilities \(p_{ij}\) and \(1-p_{ij}\) respectively) and
+then being correctly observed with probabilities given by \(p_{fp}\) and
+\(p_{fn}\) to yield a single boolean outcome for each particle.
+(``Resampling'' within fig.~\ref{fig:resampling_concept} (B)). Over many
+samples of particles, the resulting frequency of `true' outcomes is a
+single resample of the interaction probability \(p_{ij}^*\). Across
+several samples each of several particles, this forms a distribution of
+probabilities which are adjusted by the true and false negative rates.
+
+There is also an analytic way to approximate this distribution using the
+normal approximation to binomial. As a reminder, as the total number of
+samples \(n\) from a binomial distribution with success probability
+\(p\) from approaches infinity, the sum of total successes across all
+samples approaches a normal distribution with mean \(np\) and variance
+\(np(1-p)\). We can use this to correct the estimate \(p_{ij}\) based on
+the expected false-negative-rate \(p_{fn}\) and false-positive rate
+\(p_{fp}\) to obtain the limiting distribution as the number of
 resamples approaches infinity for the resampled \(p_{ij}^*\) for a given
@@
 of observation error to get the mean resampled probability,
-\(\bar{p_{ij}^*}\), as
-
-\[\bar{p_{ij}^*} = p_{ij}(1+p_{fp})(1-p_{fn})\]
+\(\mathbb{E}[{p_{ij}^*}]\), as
+
+\[
+\mathbb{E}[{p_{ij}^*}] = p_{ij}(1-p_{fp})+ (1-p_{ij})p_{fn}
+\]
 
@@
 
-\[\mathcal{N}\bigg(n_p \bar{p_{ij}^*}, \sqrt{n_p \bar{p_{ij}^*} (1-\bar{p_{ij}^*})}\bigg)\]
+\[
+\sum_{i=1}^{n_p} p_{ij}^* \sim \mathcal{N}\bigg(n_p \cdot \mathbb{E}[p_{ij}^*], \sqrt{n_p\mathbb{E}[p_{ij}^*] (1- \mathbb{E}[p_{ij}^*])}\bigg)
+\]
 
@@
 
-\begin{equation}\protect\hypertarget{eq:eq1}{}{\mathcal{N}\bigg(\bar{p^*_{ij}},
-\sqrt{\frac{\bar{p_{ij}^*}(1-\bar{p_{ij}^*})}{n_p}} \bigg)}\label{eq:eq1}\end{equation}
+\begin{equation}\protect\hypertarget{eq:eq1}{}{p_{ij}^* \sim \mathcal{N}\bigg( \mathbb{E}[p_{ij}^*] , \sqrt{\frac{\mathbb{E}[p_{ij}^*]
+(1-\mathbb{E}[p_{ij}^*] )}{n_p}} \bigg)}\label{eq:eq1}\end{equation}
 
@@
 output is a probability, although in practice often the probability mass
-outside \((0,1)\) is exteremly low.
-
-Why is this useful? Less computation, number of particles \(n_p\) as a
-uncertainty width, nautral analogue to number of observations of
-co-occurrence. More about this here.
-
-As an example case study, we use a boosted-regresssion-tree to predict
-interactions in a host-parasite network (Hadfield \emph{et al.} 2014)
-(with features derived in the same manner as Strydom \emph{et al.}
-(2021) derives features on this data) to produce a set of interaction
-predictions. We then applied this method to a set of a few resampled
-interaction probabilities between mammals and parasite species shown in
-figure fig.~\ref{fig:resampling_concept} (C). Here we implement a simple
-resampling algorithm, but this could be extended, for example by
-adjusting the expected FNR for each pair of species by the relative
-abundance of each species. We have implemented a general framework for
-this resampling methodology in the Julia package
-InteractionUncertaintySampler.jl, which enables flexible choices for
-priors on false-negative and false-positive rates.
-
-This method allows us to more effectively represent our uncertainty
-about observation error in predictions of species interactions. This
-also has implications for what we mean by `uncertainty' in interaction
-predictions. A model's prediction can be `uncertain' in two different
-ways: the model's predictions may have high variance, or the model's
-predictions may be centered around a probability of interaction of
-\(0.5\), where we are the most unsure about whether this interaction
-exists. Improving the incorporation of different forms of uncertainty in
-probabilistic interaction predictions seems a necessary next step toward
-understanding what pairs of species we know the least about, in order to
-prioritize sampling to provide the most new information possible.
+outside \((0,1)\) is exteremly low. As an example case study, we use a
+boosted-regression-tree to predict interactions in a host-parasite
+network (Hadfield \emph{et al.} 2014) (with features derived in the same
+manner as Strydom \emph{et al.} (2021) derives features on this data) to
+produce a set of interaction predictions. We then applied this method to
+a set of a few resampled interaction probabilities between mammals and
+parasite species shown in figure fig.~\ref{fig:resampling_concept}(C).
+
+Why is this useful? For one, this analytic method avoids the extra
+computation required by simulating samples from this distribution
+directly. Further, it enables continuous exanination of the number of
+particles \(n_p\) as a uncertainty width. The natural analogue for the
+number of particles sampled is the number of observations of
+co-occurrence for a given pair of species---the fewer the particles, the
+higher the variance of the resulting approximation (see supplemental
+figure 1 for an example). Equation (\textbf{ref:eq:eq1?}) is undefined
+for 0 particles (i.e.~0 observations co-occurrence), although as \(n_p\)
+approaches \(0\) the approxated normal (once truncated) approaches a
+uniform distribution on the interval \((0,1)\), the maximum entropy
+distribution where we have no information about the possibility of an
+interaction.
+
+This also has implications for what we mean by `uncertainty' in
+interaction predictions. A model's prediction can be `uncertain' in two
+different ways: (1) the model's predictions may have high variance, or
+(2) the model's predictions may be centered around a probability of
+interaction of \(0.5\), where we are the most unsure about whether this
+interaction exists . For non-zero \(p_{fn}\) and \(p_{fp}\), the above
+model always moves the mean interaction probability toward 0.5
+(supplemental figure 2), siding toward higher uncertainty in the latter
+(higher entropy) sense. Improving the incorporation of different forms
+of uncertainty in probabilistic interaction predictions seems a
+necessary next step toward understanding what pairs of species we know
+the least about, in order to prioritize sampling to provide the most new
+information possible.
 
@@
 2016). However, here we demonstrate that the probability of observing a
-false negative can be higher if there is some positive association in
+false-negative can be higher if there is some positive association in
 the occurrence of species \(A\) and \(B\). If we denote the probability

### 2023-01-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@c62b1bbd14631093c54d29eb7c03d729d3efe513 🚀

@@
 \,\textsuperscript{3,2}\quad %
-\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
+\href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
 %
@@
 interacting species. These interactions allow communities of species to
-persist through time through both neutral and adaptive processes. Still
-a robust understanding of (and ability to predict and forecast)
-interactions among species remains elusive. This knowledge-gap is
-largely driven by a shortfall of data---although species occurrence data
-has rapidly increased in the last decade, species interaction data has
-not kept pace, largely due to the intrinsic difficulty and effort
-required to sample interactions. These sampling challenges bias data and
-hinder inferences about the structure and dynamics of interactions
-networks. Here, we demonstrate the realized false-negative rate (the
-percentage of species that actually interact but for which we do not yet
-have a record) can be quite high, even in thoroughly sampled systems,
-due to the intrinsic variation in abundances across species in a
-community. We illustrate how a null model of occurrence detection can be
-used to estimate the false-negative rate in a given dataset. We also
-show how to directly incorporate uncertainty due to observation error
-into model-based predictions of interaction probabilities between
-species. One hypothesis is that interactions between ``rare'' species
-are themselves rare because these species are less likely to encounter
-one-another than species of higher relative abundance. However, we
-demonstrate that across several datasets of spatial or temporally
-replicated networks, there are positive associations that suggest these
-interactions actually exist but just are not observed. Finally, we
-assess how false negatives influence various models of network
-prediction, and recommend directly accounting for observation error in
-predictive models. We conclude by discussing how the understanding of
+persist through time through both neutral and adaptive processes.
+Despite their importance, a robust understanding of (and ability to
+predict and forecast) interactions among species remains elusive. This
+knowledge-gap is largely driven by a shortfall of data---although
+species occurrence data has rapidly increased in the last decade,
+species interaction data has not kept pace, largely due to the intrinsic
+difficulty and effort required to sample interactions. This means there
+are many interactions between species that occur in nature, but we do
+not think this interaction occurs because we have no record of it. These
+so-called ``false-negatives'' bias data and hinder inference about the
+structure and dynamics of interaction networks. Here, we demonstrate the
+realized rate of false-negatives in data can be quite high, even in
+thoroughly sampled systems, due to the intrinsic variation in abundances
+across species in a community. We illustrate how a null model of
+occurrence detection can be used to estimate the false-negative rate in
+a given dataset. We also show how to directly incorporate uncertainty
+due to observation error into model-based predictions of interaction
+probabilities between species. One hypothesis is that interactions
+between ``rare'' species are themselves rare because these species are
+less likely to encounter one-another than species of higher relative
+abundance, and that this can (in part) explain the common pattern of
+nestedness in bipartite interaction networks. However, we demonstrate
+that across several datasets of spatial or temporally replicated
+networks, there are positive associations between species co-occurrence
+and interactions, which suggests these interactions among ``rare''
+species actually exist but simply are not observed. Finally, we assess
+how false negatives influence various models of network prediction, and
+recommend directly accounting for observation error in predictive
+models. We conclude by discussing how the understanding of
 false-negatives can inform how we design monitoring schemes for species
@@
 Many crowdsourced methods for biodiversity data aggregation (e.g.~GBIF,
-eBird) still relies on automated identification of species, which does
-not easily generalize to interaction sampling. There is interest in
-using remote methods for interaction sampling, which primarily detect
+eBird) still rely on automated identification of species, which does not
+easily generalize to interaction sampling. There is interest in using
+remote methods for interaction sampling, which primarily detect
 co-occurrence and derive properties like species avoidance from this
-data (Niedballa \emph{et al.} 2019). However, this itself is not
-necessarily indicative of an interaction (Blanchet \emph{et al.} 2020).
-This is an example of semantic confusion around the word
+data (Niedballa \emph{et al.} 2019). However, co-occurrence itself is
+not necessarily indicative of an interaction (Blanchet \emph{et al.}
+2020). This is an example of semantic confusion around the word
 ``interaction''---for example one might consider competition a type of
 species interaction, even though it is marked by a lack of co-occurrence
-between species, unlike other types of interactions, like trophism or
-pollination, which require both species to be together at the same place
+between species, unlike other types of interactions, like predation or
+parasitism, which require both species to be together at the same place
 and time. Here we consider interaction in the latter sense, where two
@@
 occur in an ecosystem. This means we can be confident two species
-actually interact if we have a record of it (given an estimate of
-species misidentification probability), but not at all confident that a
-pair of species \emph{do not} interact if we have \emph{no record} of
-those species observed together. In other words, it is difficult to
-distinguish \emph{true-negatives} (two species never interact) from
+actually interact if we have a record of it (assuming they are correctly
+identified), but not at all confident that a pair of species \emph{do
+not} interact if we have \emph{no record} of those species observed
+together. In other words, it is difficult to distinguish
+\emph{true-negatives} (two species never interact) from
 \emph{false-negatives} (two species interact sometimes, but we do not
-have a record of it). For a concrete example of a false-negative in a
-food web, see fig.~\ref{fig:concept}. Because even the most highly
-sampled systems will still contain missing interactions, there is
-increasing interest in combining species-level data (e.g.~traits,
-abundance, range, phylogenetic relatedness, etc.) to build models to
-predict interactions between species we haven't observed together before
-(Strydom \emph{et al.} 2021). However, the noise of false-negatives
-could impact the efficacy of our predictive models and have practical
-consequences for answering questions about interactions (de Aguiar
-\emph{et al.} 2019). This data constraint is amplified as the
+have a record of this interaction). For a concrete example of a
+false-negative in a food web, see fig.~\ref{fig:concept}. Because even
+the most highly sampled systems will still contain false-negatives,
+there is increasing interest in combining species-level data
+(e.g.~traits, abundance, range, phylogenetic relatedness, etc.) to build
+models to predict interactions between species we haven't observed
+together before (Strydom \emph{et al.} 2021). However, the noise of
+false-negatives could impact the efficacy of our predictive models and
+have practical consequences for answering questions about interactions
+(de Aguiar \emph{et al.} 2019). This data constraint is amplified as the
 interaction data we have is geographically biased toward the usual
@@
 of population abundance (Griffiths 1998). This relationship between
-sampling effort and spatial coverage and species detectability . This
-has motivated more quantitatively robust approaches to account for error
-in sampling data in many contexts: to determine if a given species is
+sampling effort and spatial coverage and species detectability has
+motivated more quantitatively robust approaches to account for error in
+sampling data in many contexts: to determine if a given species is
 extinct (Boakes \emph{et al.} 2015), to determine sampling design (Moore
@@
 associations leads to increasing probability of false-negatives in
-interaction data, and that these positive associations are rampant in
+interaction data, and that these positive associations are common in
 existing network data. Second, observed co-occurrence is often equated
@@
 species interactions can benefit from simulation modeling of the
-sampling process. We demonstrate how the realized false-negative rate of
+sampling process. We demonstrate how the realized false-negative-rate of
 interactions is related to the relative abundance of the species pool,
-and use simulation to produce a null estimate of the false-negative rate
-given total sampling effort (the total count of all individuals of all
-species seen), and to introduce a method for introducing uncertainty
-into model predictions of interaction probability to account for
-observation error. We then show that positive associations in
-co-occurrence data can increase the realized number of false-negatives,
-and demonstrate these positive associations are rampant in network
-datasets, and conclude by recommending that the simulation of sampling
-effort and species occurrence can and should be used to help design
-surveys of species interaction diversity (Moore \& McCarthy 2016), and
-by advocating use of null models like those presented here as a tool for
-both guiding design of surveys of species interactions and for modeling
-detection error in predictive models.
+and introduce a method to produce a null estimate of the
+false-negative-rate given total sampling effort (the total count of all
+interactions seen among all species-pairs) and a method for including
+uncertainty into model predictions of interaction probabilities to
+account for observation error. We then show that positive associations
+in co-occurrence data can increase the realized number of
+false-negatives, and demonstrate these positive associations are rampant
+in network datasets, and conclude by recommending that the simulation of
+sampling effort and species occurrence can and should be used to help
+design surveys of species interaction diversity (Moore \& McCarthy
+2016), and by advocating use of null models like those presented here as
+a tool for both guiding design of surveys of species interactions and
+for modeling detection error in predictive models.
 
@@
 they actually do. Therefore, this interaction between bears and pike is
-a false negative.}\label{fig:concept}
+a false-negative.}\label{fig:concept}
 }
@@
 interactions}\label{accounting-for-false-negatives-in-species-interactions}}
+
+In this section, we demonstate how difference in relative-abundance can
+lead to many false-negatives in interaction data. We also introduce a
+method for producing a null estimate of the false-negative-rate in
+datasets via simulation, and a method for incorporating uncertainty
+directly into predictions of species interactions to account for
+observation error.
 
@@
 not-interacting with an independent and fixed probability, which we
-denote \(p_{fn}\) and subsequently refer to as the False-Negative Rate
+denote \(p_{fn}\) and subsequently refer to as the False-Negative-Rate
 (FNR). If we observe the same species not-interacting \(N\) times, then
@@
 Because the true FNR is latent, we can never actually be sure what the
-actual number of false negatives in our data---however, we can use
-simulation to estimate it for datasets of a given size using neutral
-models of observation. If some of the ``worst-case'' FNRs presented in
-fig.~\ref{fig:geometric}(A) seem unrealistically high, consider that
-species are observed in proportion to their relative abundance. In the
-next section we demonstrate that the distribution of abundance in
-ecosystems can lead to very high realized values of FNR (\(p_{fn}\))
-simply as an artifact of sampling effort.
+actual number of false-negatives in our data---however, we can use
+simulation to estimate the FNR for datasets of a given size using
+neutral models of observation. If some of the ``worst-case'' FNRs
+presented in fig.~\ref{fig:geometric}(A) seem unrealistically high,
+considering that species are observed in proportion to their relative
+abundance. In the next section we demonstrate that the distribution of
+abundance in ecosystems can lead to very high realized values of FNR
+(\(p_{fn}\)) simply as an artifact of sampling effort.
 
@@
 non-interaction (x-axis). Each color reflects a different value of
-\(p_{fn}\), the false-negative rate (FNR)---this is effectively the cdf
+\(p_{fn}\), the false-negative-rate (FNR)---this is effectively the cdf
 of the geometric distribution. \textbf{(B)} The expected number of total
@@
 species with relative abundance \(P(A)\) (x-axis) and a second species
-with relative abundance \(P(Y)\). \textbf{(C)}: False negative rate
+with relative abundance \(P(Y)\). \textbf{(C)}: false-negative-rate
 (y-axis) as a function of total sampling effort (x-axis) and network
@@
 in the main text. For each draw from the niche model, 200 sets of 1500
-observations are simulated, for which each the mean false negative rate
-at each observation-step is computed. Means denoted with points, with 1
-in the first shade and 2 in the second. \textbf{(D)}: Same as
-\textbf{(C)}, except using empirical food webs from Mangal database,
-where richness. The outlier on \textbf{(D)} is a 714 species
+observations are simulated, for which the mean false-negative-rate at
+each observation-step is computed. Means denoted with points, with 1 in
+the first shade and 2 in the second. \textbf{(D)}: Same as \textbf{(C)},
+except using empirical food webs from Mangal database, where richness.
+The outlier on \textbf{(D)} is a 714 species
 food-web.}\label{fig:geometric}
@@
 
-where the MAP estimate of \((\mu, \phi)\) applied to Mangal data from
-(MacDonald \emph{et al.} 2020) is \((\mu=0.086, \phi=24.3)\). All
-simulations were done with 500 independent replicates of unique niche
-model networks per unique number of observations \(n\). All analyses
-presented here are done in Julia v1.8 (Bezanson \emph{et al.} 2015)
-using both EcologicalNetworks.jl v0.5 and Mangal.jl v0.4 (Banville
-\emph{et al.} 2021) and are hosted on
+where the maximum \emph{a posteriori} (MAP) estimate of \((\mu, \phi)\)
+applied to Mangal data from (MacDonald \emph{et al.} 2020) is
+\((\mu=0.086, \phi=24.3)\). All simulations were done with 500
+independent replicates of unique niche model networks per unique number
+of observations \(n\). All analyses presented here are done in Julia
+v1.8 (Bezanson \emph{et al.} 2015) using both EcologicalNetworks.jl v0.5
+and Mangal.jl v0.4 (Banville \emph{et al.} 2021) and are hosted on
 \href{https://github.com/gottacatchenall/ms_false_negatives/tree/main/src}{Github}).
 Note that the empirical data, for the reasons described above, very
-likely already contains many false negatives, we'll revisit this issue
+likely already contains many false-negatives, we'll revisit this issue
 in the final section.
@@
 From fig.~\ref{fig:geometric}(C) it is evident that the number of
-species considered in a study is inseparable from the false-negative
-rate in that study, and this effect should be taken into account when
-designing samples of ecological networks in the future. We see a similar
-qualitative pattern in fig.~\ref{fig:geometric}(D) where the FNR drops
-off quickly as a function of observation effort, mediated by total
-richness. The practical consequence of the bottom row of
+species considered in a study is inseparable from the
+false-negative-rate in that study, and this effect should be taken into
+account when designing samples of ecological networks in the future. We
+see a similar qualitative pattern in fig.~\ref{fig:geometric}(D) where
+the FNR drops off quickly as a function of observation effort, mediated
+by total richness. The practical consequence of the bottom row of
 fig.~\ref{fig:geometric} is whether the total number of observations of
@@
 \includegraphics{./figures/uncertainty_sampler.png}
-\caption{(A) The process for estimating the false-negative rate (FNR)
+\caption{(A) The process for estimating the false-negative-rate (FNR)
 for an interaction dataset consisting of \(N\) total observed
@@
 \section{Positive associations in co-occurrence increase the
-false-negative
-rate}\label{positive-associations-in-co-occurrence-increase-the-false-negative-rate}}
+false-negative-rate}\label{positive-associations-in-co-occurrence-increase-the-false-negative-rate}}
 
@@
 cooccurrence together due to their interaction (Cazelles \emph{et al.}
-2016). However, here we demonstrate that the probability of observing a
+2016). However, here we demonstrate that the probability of having a
 false-negative can be higher if there is some positive association in
@@
 across space/time, then the spatial/temporal biases induced by data
-collection would further impact the realized false negative rate, as the
+collection would further impact the realized false-negative-rate, as the
 probability of false negative would not be constant for each pair of
@@
 To test for these positive associations in data we scoured Mangal for
-datasets with many spatial or temporal replicates of the same system.
-For each dataset, we compute the marginal probability \(P(A)\) of
-occurrence of each species \(A\) across all networks in the dataset. For
-each pair of interacting species \(A\) and \(B\), we then compute and
-compare the probability of co-occurrence if each species occurs
-independently, \(P(A)P(B)\), to the empirical joint probability of
-co-occurrence, \(P(AB)\). Following our analysis above, if \(P(AB)\) is
-greater than \(P(A)P(B)\), then we expect our neutral estimates of the
-FNR above to underestimate the realized FNR. In fig.~\ref{fig:mangal},
-we see the difference between \(P(AB)\) and \(P(A)P(B)\) for the seven
-suitable datasets with enough spatio-temporal replicates and a shared
-taxonomic backbone (meaning all individual networks use common species
-identifiers) found on Mangal to perform this analysis. Further details
-about each dataset are reported in tbl.~\ref{tbl:id}.
+datasets with many spatial or temporal replicates of the same system,
+which led the the resulting seven datasets set in figure
+fig.~\ref{fig:mangal}. For each dataset, we compute the marginal
+probability \(P(A)\) of occurrence of each species \(A\) across all
+networks in the dataset. For each pair of interacting species \(A\) and
+\(B\), we then compute and compare the probability of co-occurrence if
+each species occurs independently, \(P(A)P(B)\), to the empirical joint
+probability of co-occurrence, \(P(AB)\). Following our analysis above,
+if \(P(AB)\) is greater than \(P(A)P(B)\), then we expect our neutral
+estimates of the FNR above to underestimate the realized FNR. In
+fig.~\ref{fig:mangal}, we see the difference between \(P(AB)\) and
+\(P(A)P(B)\) for the seven suitable datasets with enough spatio-temporal
+replicates and a shared taxonomic backbone (meaning all individual
+networks use common species identifiers) found on Mangal to perform this
+analysis. Further details about each dataset are reported in
+tbl.~\ref{tbl:id}.
 
@@
 \begin{longtable}[]{@{}ccccccccc@{}}
-\caption{\label{tbl:id}This table describes the datasets used in the
-above analysis (Fig 2). The table reports the type of each dataset, the
-total number of networks in each dataset \((N)\), the total species
-richness in each dataset \((S)\), the connectance of each metaweb (all
-interactions across the entire spatial-temporal extent) \((C)\), the
-mean species richness across each local network \(\bar{S}\), the mean
-connectance of each local network \(\bar{C}\), the mean
-\(\beta\)-diversity among overlapping species across all pairs of
-network species (\(\bar{\beta}_{OS}\)), and the mean \(\beta\)-diversity
-among all species in the metaweb (\(\bar{\beta}_{WN}\)). Both metrics
-are computed using KGL \(\beta\)-diversity (Koleff \emph{et al.}
+\caption{\label{tbl:id}The datasets used in the above analysis (Fig 2).
+The table reports the type of each dataset, the total number of networks
+in each dataset \((N)\), the total species richness in each dataset
+\((S)\), the connectance of each metaweb (all interactions across the
+entire spatial-temporal extent) \((C)\), the mean species richness
+across each local network \(\bar{S}\), the mean connectance of each
+local network \(\bar{C}\), the mean \(\beta\)-diversity among
+overlapping species across all pairs of network species
+(\(\bar{\beta}_{OS}\)), and the mean \(\beta\)-diversity among all
+species in the metaweb (\(\bar{\beta}_{WN}\)). Both metrics are computed
+using KGL \(\beta\)-diversity (Koleff \emph{et al.}
 2003)}\tabularnewline
@@
 
-Here, we assess the effect of false negatives on our ability to make
+Here, we assess the effect of false-negatives on our ability to make
 predictions about interactions, as well as their effect on network
@@
 (PR-AUC; right) for each different predictive model (colors/shapes)
-across a spectrum of the proportion of added false negatives (x-axis).
+across a spectrum of the proportion of added false-negatives (x-axis).
 \textbf{(C)} The mean trophic-level of all species in a network
@@
 predict ``no-interaction'' for all possible species pairs, which does
-far better than random guessing (ROC-AUC = 0.5) in terms the false
+far better than random guessing (ROC-AUC = 0.5) in terms of the false
 positive rate (one of the components of ROC-AUC). This highlights a more
@@
 maximize the amount of information contained in our data given the
-expensive nature of sampling interactions.
+expense of sampling interactions.
 
@@
 mean trophic level, despite varying widely between niche model
-simulations, tends to be relatively robust to false negatives and does
+simulations, tends to be relatively robust to false-negatives and does
 not deviate widely from the true value until very large FNRs,
@@
 giant component, rather than the emergence of one. Further applications
-of percolation theory to the topology of ecological networks could
-improve our understanding of how false-negatives impact the inferences
-about the structure and dynamics on these networks.
+of percolation theory (Li \emph{et al.} 2021) to the topology of sampled
+ecological networks could improve our understanding of how
+false-negatives impact the inferences about the structure and dynamics
+on these networks.
 
@@
 ecosystems, but our understanding of interactions is limited due to the
-intrinsic difficulty of sampling. Here we have provided a null model for
-the expected number of false-negatives in an interaction dataset. We
-demonstrated that we expect many false-negatives in species interaction
-datasets purely due to the intrinsic variation of abundances within a
-community. We also, for the first time to our knowledge, measured the
-strength of association between co-occurrence and interactions (Cazelles
-\emph{et al.} 2016) across many empirical systems, and found that these
-positive associations are both very common, and showed algebraically
-that they increase the realized FNR. We have also shown that
-false-negatives could further impact our ability to both predict
-interactions and infer properties of the networks, which highlights the
-need for further research into methods for correcting this bias in
-existing data.
+intrinsic difficulty of sampling them. Here we have provided a null
+model for the expected number of false-negatives in an interaction
+dataset. We demonstrated that we expect many false-negatives in species
+interaction datasets purely due to the intrinsic variation of abundances
+within a community. We also, for the first time to our knowledge,
+measured the strength of association between co-occurrence and
+interactions (Cazelles \emph{et al.} 2016) across many empirical
+systems, and found that these positive associations are both very
+common, and showed algebraically that they increase the realized FNR. We
+have also shown that false-negatives could further impact our ability to
+both predict interactions and infer properties of the networks, which
+highlights the need for further research into methods for correcting
+this bias in existing data.
 
@@
 
-This work has several practical consequences for the design of
-interaction samples. Simulating the process of observation could be a
-powerful tool for estimating the sampling effort required by a study
-that takes relative abundance into account, and provides a null baseline
-for expected FNR. It is necessary to take the size of the species pool
-into account when deciding how many total samples is sufficient for an
-``acceptable'' FNR (fig.~\ref{fig:geometric}(C \& D)). Further the
-spatial and temporal turnover of interactions means any approach to
-sampling prioritization must be spatiotemporal. We demonstrated earlier
-that observed negatives outside of the range of both species aren't
-informative, and therefore using species distribution models could aid
-in this spatial prioritization of sampling sites.
+This work has several practical consequences for the design of surveys
+for species' interactions. Simulating the process of observation could
+be a powerful tool for estimating the sampling effort required by a
+study that takes relative abundance into account, and provides a null
+baseline for expected FNR. It is necessary to take the size of the
+species pool into account when deciding how many total samples is
+sufficient for an ``acceptable'' FNR (fig.~\ref{fig:geometric}(C \& D)).
+Further the spatial and temporal turnover of interactions means any
+approach to sampling prioritization must be spatiotemporal. We
+demonstrated earlier that observed negatives outside of the range of
+both species aren't informative, and therefore using species
+distribution models could aid in this spatial prioritization of sampling
+sites.
 
@@
 characterizes the whole system? We suggest that modeling observation
-error like we have done here can address these questions and aid in the
-design of samples of species interactions. To try and sample to avoid
-all false-negatives is a fool's errand. Species ranges overlap to form
+error as we have done here can address these questions and aid in the
+design of samples of species interactions. To try to survey to avoid all
+false-negatives is a fool's errand. Species ranges overlap to form
 mosaics, which themselves are often changing in time. Communities and
@@
 extent and temporal resolution, and to determine what the sampling
-effort required prior to sampling.
+effort required should be prior to sampling.
 
@@
 inference and predictive models we apply to this data, is imperative in
-understanding how biodiversity is changing, and making actionable
-forecasts about the future of ecological interactions on our planet.
+understanding how biodiversity is changing, and making forecasts that
+can guide conservation action.
+
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+AG \& MDC acknowledge the support of the Liber Ero Chair for
+Biodiversity conservation and NSERC.
 

### 2023-01-14 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@248cde172ef469d2562cfb1e543110f64eef9496 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@fc540949f9b43d58c34c27f827e5607a20741112 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@7aa656d41d88975532ffd237498f5e8ea2810b9f 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@c62b1bbd14631093c54d29eb7c03d729d3efe513 🚀

@@
 \,\textsuperscript{3,2}, %
-\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
+\href{https://orcid.org/0000-0002-6004-4027}{Laura J.\,Pollock}%
 %
@@
 %
-\,\textsuperscript{1,2}
+\,\textsuperscript{1,4}
 \vskip 1em
@@
 Centre for Biodiversity Sciences; \textsuperscript{3}\,Université de
-Montréal\\
+Montréal; \textsuperscript{4}\,Québec Centre for Biodiversity Science\\
 \vskip 1em
@@
 interacting species. These interactions allow communities of species to
-persist through time through both neutral and adaptive processes. Still
-a robust understanding of (and ability to predict and forecast)
-interactions among species remains elusive. This knowledge-gap is
-largely driven by a shortfall of data---although species occurrence data
-has rapidly increased in the last decade, species interaction data has
-not kept pace, largely due to the intrinsic difficulty and effort
-required to sample interactions. These sampling challenges bias data and
-hinder inferences about the structure and dynamics of interactions
-networks. Here, we demonstrate the realized false-negative rate (the
-percentage of species that actually interact but for which we do not yet
-have a record) can be quite high, even in thoroughly sampled systems,
-due to the intrinsic variation in abundances across species in a
-community. We illustrate how a null model of occurrence detection can be
-used to estimate the false-negative rate in a given dataset. One
-hypothesis is that interactions between ``rare'' species are themselves
-rare because these species are less likely to encounter one-another than
-species of higher relative abundance. However, we demonstrate that
-across several datasets of spatial or temporally replicated networks,
-there are positive associations that suggest these interactions actually
-exist but just are not observed. Finally, we assess how false negatives
-influence various models of network prediction, and recommend directly
-accounting for observation error in predictive models. We conclude by
-discussing how the understanding of false-negatives can inform how we
-design monitoring schemes for species interactions.\\%
+persist through time through both neutral and adaptive processes.
+Despite their importance, a robust understanding of (and ability to
+predict and forecast) interactions among species remains elusive. This
+knowledge-gap is largely driven by a shortfall of data---although
+species occurrence data has rapidly increased in the last decade,
+species interaction data has not kept pace, largely due to the intrinsic
+difficulty and effort required to sample interactions. This means there
+are many interactions between species that occur in nature, but we do
+not think this interaction occurs because we have no record of it. These
+so-called ``false-negatives'' bias data and hinder inference about the
+structure and dynamics of interaction networks. Here, we demonstrate the
+realized rate of false-negatives in data can be quite high, even in
+thoroughly sampled systems, due to the intrinsic variation in abundances
+across species in a community. We illustrate how a null model of
+occurrence detection can be used to estimate the false-negative rate in
+a given dataset. We also show how to directly incorporate uncertainty
+due to observation error into model-based predictions of interaction
+probabilities between species. One hypothesis is that interactions
+between ``rare'' species are themselves rare because these species are
+less likely to encounter one-another than species of higher relative
+abundance, and that this can (in part) explain the common pattern of
+nestedness in bipartite interaction networks. However, we demonstrate
+that across several datasets of spatial or temporally replicated
+networks, there are positive associations between species co-occurrence
+and interactions, which suggests these interactions among ``rare''
+species actually exist but simply are not observed. Finally, we assess
+how false negatives influence various models of network prediction, and
+recommend directly accounting for observation error in predictive
+models. We conclude by discussing how the understanding of
+false-negatives can inform how we design monitoring schemes for species
+interactions.\\%
 
@@
 cooccurrence together due to their interaction (Cazelles \emph{et al.}
-2016). However, here we demonstrate that the probability of observing a
-false negative can be higher if there is some positive association in
+2016). However, here we demonstrate that the probability of having a
+false-negative can be higher if there is some positive association in
 the occurrence of species \(A\) and \(B\). If we denote the probability

### 2023-01-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@b47a6b7b3faa32128c1c7850dd6a20efef0eca20 🚀

@@
 co-occurrence for a given pair of species---the fewer the particles, the
-higher the variance of the resulting approximation (see supplemental
-figure 1 for an example). Equation (\textbf{ref:eq:eq1?}) is undefined
-for 0 particles (i.e.~0 observations co-occurrence), although as \(n_p\)
-approaches \(0\) the approxated normal (once truncated) approaches a
-uniform distribution on the interval \((0,1)\), the maximum entropy
-distribution where we have no information about the possibility of an
-interaction.
+higher the variance of the resulting approximation. The normal
+approximation is undefined for 0 particles (i.e.~0 observations
+co-occurrence), although as \(n_p\) approaches \(0\) the approxated
+normal (once truncated) approaches a uniform distribution on the
+interval \((0,1)\), the maximum entropy distribution where we have no
+information about the possibility of an interaction.
 
@@
 interaction of \(0.5\), where we are the most unsure about whether this
-interaction exists . For non-zero \(p_{fn}\) and \(p_{fp}\), the above
-model always moves the mean interaction probability toward 0.5
-(supplemental figure 2), siding toward higher uncertainty in the latter
-(higher entropy) sense. Improving the incorporation of different forms
-of uncertainty in probabilistic interaction predictions seems a
-necessary next step toward understanding what pairs of species we know
-the least about, in order to prioritize sampling to provide the most new
+interaction exists. Improving the incorporation of different forms of
+uncertainty in probabilistic interaction predictions seems a necessary
+next step toward understanding what pairs of species we know the least
+about, in order to prioritize sampling to provide the most new
 information possible.
@@
 or negative associations which shift the probability of species
-cooccurrence together due to their interaction (Cazelles \emph{et al.}
-2016). However, here we demonstrate that the probability of having a
+cooccurrence away from what is expected based on their relative
+abundances due to their interaction (Cazelles \emph{et al.} 2016).
+However, here we demonstrate that the probability of having a
 false-negative can be higher if there is some positive association in

### 2023-01-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@d250e92aa9612d39e1283c22025bf6fb78863610 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@114806505e9b51e115f1faeaff195f84a965611d 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@cc38d6bfa2362a09493e9a46979610d8934b75b7 🚀

@@
 \usepackage{lineno}
-\usepackage[nolists,noheads]{endfloat}
+% \usepackage[nolists,noheads]{endfloat}
+
+\usepackage{floatrow}
+
+\floatsetup[figure]{
+              floatwidth=\textwidth}
 
@@
 Here, we illustrate how our confidence that a pair of species never
-interacts highly depends on sampling effort. We suggest that surveys of
-species interactions can benefit from simulation modeling of the
-sampling process. We demonstrate how the realized false-negative-rate of
-interactions is related to the relative abundance of the species pool,
-and introduce a method to produce a null estimate of the
-false-negative-rate given total sampling effort (the total count of all
-interactions seen among all species-pairs) and a method for including
-uncertainty into model predictions of interaction probabilities to
-account for observation error. We then show that positive associations
-in co-occurrence data can increase the realized number of
-false-negatives, and demonstrate these positive associations are rampant
-in network datasets, and conclude by recommending that the simulation of
-sampling effort and species occurrence can and should be used to help
-design surveys of species interaction diversity (Moore \& McCarthy
-2016), and by advocating use of null models like those presented here as
-a tool for both guiding design of surveys of species interactions and
-for modeling detection error in predictive models.
+interacts highly depends on sampling effort. We demonstrate how the
+realized false-negative-rate of interactions is related to the relative
+abundance of the species pool, and introduce a method to produce a null
+estimate of the false-negative-rate given total sampling effort (the
+total count of all interactions seen among all species-pairs) and a
+method for including uncertainty into model predictions of interaction
+probabilities to account for observation error. We then confront these
+models with data, by showing that positive associations in co-occurrence
+data can increase the realized number of false-negatives and by showing
+these positive associations are rampant in network datasets. We conclude
+by recommending that the simulation of sampling effort and species
+occurrence can and should be used to help design surveys of species
+interaction diversity (Moore \& McCarthy 2016), and by advocating use of
+null models like those presented here as a tool for both guiding design
+of surveys of species interactions and for including detection error
+into predictive models.
 
@@
 normal approximation to binomial. As a reminder, as the total number of
-samples \(n\) from a binomial distribution with success probability
-\(p\) from approaches infinity, the sum of total successes across all
-samples approaches a normal distribution with mean \(np\) and variance
-\(np(1-p)\). We can use this to correct the estimate \(p_{ij}\) based on
-the expected false-negative-rate \(p_{fn}\) and false-positive rate
-\(p_{fp}\) to obtain the limiting distribution as the number of
+samples \(N\) from a binomial distribution for \(n\) trials with success
+probability \(p\) from approaches infinity, the sum of total successes
+across all samples approaches a normal distribution with mean \(np\) and
+variance \(np(1-p)\). We can use this to correct the estimate \(p_{ij}\)
+based on the expected false-negative-rate \(p_{fn}\) and false-positive
+rate \(p_{fp}\) to obtain the limiting distribution as the number of
 resamples approaches infinity for the resampled \(p_{ij}^*\) for a given

### 2023-01-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@c996e47ff1b1567c3517efc1a6d065ac6522a5ab 🚀

@@
 non-interaction (x-axis). Each color reflects a different value of
-\(p_{fn}\), the false-negative-rate (FNR)---this is effectively the cdf
-of the geometric distribution. \textbf{(B)} The expected number of total
-observations needed (colors) to observe 10 co-occurrences between a
-species with relative abundance \(P(A)\) (x-axis) and a second species
-with relative abundance \(P(Y)\). \textbf{(C)}: false-negative-rate
-(y-axis) as a function of total sampling effort (x-axis) and network
-size, computed using the method described above. For 500 independent
-draws from the niche model (Williams \& Martinez (2000)) at varying
-levels of species richness (colors) with connectance drawn according to
-the flexible-links model (MacDonald \emph{et al.} (2020)) as described
-in the main text. For each draw from the niche model, 200 sets of 1500
-observations are simulated, for which the mean false-negative-rate at
-each observation-step is computed. Means denoted with points, with 1 in
-the first shade and 2 in the second. \textbf{(D)}: Same as \textbf{(C)},
-except using empirical food webs from Mangal database, where richness.
-The outlier on \textbf{(D)} is a 714 species
-food-web.}\label{fig:geometric}
+\(p_{fn}\), the false-negative-rate (FNR)---this is effectively the
+cumulative distribution function (cdf) of the geometric distribution.
+\textbf{(B)} The expected number of total observations needed (colors)
+to observe 10 co-occurrences between a species with relative abundance
+\(P(A)\) (x-axis) and a second species with relative abundance \(P(Y)\).
+\textbf{(C)}: false-negative-rate (y-axis) as a function of total
+sampling effort (x-axis) and network size, computed using the method
+described above. For 500 independent draws from the niche model
+(Williams \& Martinez (2000)) at varying levels of species richness
+(colors) with connectance drawn according to the flexible-links model
+(MacDonald \emph{et al.} (2020)) as described in the main text. For each
+draw from the niche model, 200 sets of 1500 observations are simulated,
+for which the mean false-negative-rate at each observation-step is
+computed. Means denoted with points, with 1 in the first shade and 2 in
+the second. \textbf{(D)}: Same as \textbf{(C)}, except using empirical
+food webs from Mangal database, where richness. The outlier on
+\textbf{(D)} is a 714 species food-web.}\label{fig:geometric}
 }
@@
 method for interaction probability resampling applied to three mammals
-and three parasites from the Hadfield \emph{et al.} (2014)
-dataset.}\label{fig:resampling_concept}
+and three parasites from the Hadfield \emph{et al.} (2014) dataset. The
+original probability \(p_{ij}\) is indicated with a vertical dashed
+line. The histogram is simulated from the resampling process, and the
+line indicates the gaussian approximation to this
+distribution.}\label{fig:resampling_concept}
 }
@@
 output is a probability, although in practice often the probability mass
-outside \((0,1)\) is exteremly low. As an example case study, we use a
+outside \((0,1)\) is extremely low. As an example case study, we use a
 boosted-regression-tree to predict interactions in a host-parasite
@@
 computation required by simulating samples from this distribution
-directly. Further, it enables continuous exanination of the number of
+directly. Further, it enables continuous extension of the number of
 particles \(n_p\) as a uncertainty width. The natural analogue for the
@@
 approximation is undefined for 0 particles (i.e.~0 observations
-co-occurrence), although as \(n_p\) approaches \(0\) the approxated
-normal (once truncated) approaches a uniform distribution on the
-interval \((0,1)\), the maximum entropy distribution where we have no
-information about the possibility of an interaction.
+co-occurrence), although as \(n_p\) approaches 0 the approximated normal
+(once truncated) approaches a uniform distribution on the interval
+\((0,1)\), the maximum entropy distribution where we have no information
+about the possibility of an interaction.
 

### 2023-01-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@2bbe8eebead4e02de00580ad1b3ebabcb23e734b 🚀

@@
 are many interactions between species that occur in nature, but we do
-not think this interaction occurs because we have no record of it. These
-so-called ``false-negatives'' bias data and hinder inference about the
-structure and dynamics of interaction networks. Here, we demonstrate the
-realized rate of false-negatives in data can be quite high, even in
+not know these interactions occur because we have never observed them.
+These so-called ``false-negatives'' bias data and hinder inference about
+the structure and dynamics of interaction networks. Here, we demonstrate
+the realized rate of false-negatives in data can be quite high, even in
 thoroughly sampled systems, due to the intrinsic variation in abundances
@@
 importance of class-balance is outside the scope of this paper, but is
-explored in-depth in Poisot (2022).
+explored in-depth in Poisot (2022). Further we see, if anything, gradual
+decline in the performance of the model until we reach very high FNR
+levels (i.e.~\(p_{fn} > 0.7\)). This is consistent with other recent
+work (Gupta \emph{et al.} 2023), although it must be considered that the
+empircal data on which these models are trained already are almost
+certain to already contain false-negatives.
 
@@
 simulations, tends to be relatively robust to false-negatives and does
-not deviate widely from the true value until very large FNRs,
-i.e.~\(p_{fn} > 0.7\). This is not entirely unsurprising. Removing links
-randomly from a food-web is effectively the inverse problem of the
-emergence of a giant component (more than half of the nodes are in a
-connected network) in random graphs (see Li \emph{et al.} (2021) for a
-thorough review). The primary difference being that we are removing
-edges, not adding them, and thus we are witnessing the dissolution of a
-giant component, rather than the emergence of one. Further applications
-of percolation theory (Li \emph{et al.} 2021) to the topology of sampled
-ecological networks could improve our understanding of how
-false-negatives impact the inferences about the structure and dynamics
-on these networks.
+not deviate widely from the true value until very large FNRs. This is
+not entirely unsurprising. Removing links randomly from a food-web is
+effectively the inverse problem of the emergence of a giant component
+(more than half of the nodes are in a connected network) in random
+graphs (see Li \emph{et al.} (2021) for a thorough review). The primary
+difference being that we are removing edges, not adding them, and thus
+we are witnessing the dissolution of a giant component, rather than the
+emergence of one. Further applications of percolation theory (Li
+\emph{et al.} 2021) to the topology of sampled ecological networks could
+improve our understanding of how false-negatives impact the inferences
+about the structure and dynamics on these networks.
 
@@
 
+\leavevmode\hypertarget{ref-Gupta2023HowMan}{}%
+Gupta, A., Figueroa H., D., O'Gorman, E., Jones, I., Woodward, G. \&
+Petchey, O.L. (2023). How many predator guts are required to predict
+trophic interactions? \emph{Food Webs}, 34, e00269.
+
 \leavevmode\hypertarget{ref-Hadfield2014TalTwo}{}%

### 2023-01-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@d17b5d1877e8977bb42c0098c54144b7771057d5 🚀

@@
 %
-\,\textsuperscript{1,4}
+\,\textsuperscript{1,2}
 
 \textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences\quad \textsuperscript{3}\,Université de
-Montréal\quad \textsuperscript{4}\,Québec Centre for Biodiversity
-Science
+Centre for Biodiversity Science\quad \textsuperscript{3}\,Université de
+Montréal
 

### 2023-01-14 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@d17b5d1877e8977bb42c0098c54144b7771057d5 🚀

@@
 %
-\,\textsuperscript{1,4}
+\,\textsuperscript{1,2}
 \vskip 1em
 \textsuperscript{1}\,McGill University; \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences; \textsuperscript{3}\,Université de
-Montréal; \textsuperscript{4}\,Québec Centre for Biodiversity Science\\
+Centre for Biodiversity Science; \textsuperscript{3}\,Université de
+Montréal\\
 \vskip 1em

### 2023-01-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@180544d298320a138724f387d02bf364de4f7cec 🚀

@@
 
-We can then further truncate to remain on the interval \((0,1)\) (as the
-output is a probability, although in practice often the probability mass
-outside \((0,1)\) is extremely low. As an example case study, we use a
-boosted-regression-tree to predict interactions in a host-parasite
+We can then further truncate this distribution to remain on the interval
+\((0,1)\), as the output is a probability, although in practice often
+the probability mass outside \((0,1)\) is extremely low except for
+\(p_{ij}\) values very close to 0 or 1. As an example case study, we use
+a boosted-regression-tree to predict interactions in a host-parasite
 network (Hadfield \emph{et al.} 2014) (with features derived in the same

### 2023-01-15 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@4c36d68d2b35929aed751583bcffe5633d308d72 🚀

@@
 species occurrence data has rapidly increased in the last decade,
-species interaction data has not kept pace, largely due to the intrinsic
-difficulty and effort required to sample interactions. This means there
-are many interactions between species that occur in nature, but we do
-not know these interactions occur because we have never observed them.
-These so-called ``false-negatives'' bias data and hinder inference about
-the structure and dynamics of interaction networks. Here, we demonstrate
-the realized rate of false-negatives in data can be quite high, even in
-thoroughly sampled systems, due to the intrinsic variation in abundances
-across species in a community. We illustrate how a null model of
-occurrence detection can be used to estimate the false-negative rate in
-a given dataset. We also show how to directly incorporate uncertainty
-due to observation error into model-based predictions of interaction
+species interaction data has not kept pace, largely due to the effort
+required to sample interactions. This means there are many interactions
+between species that occur in nature, but we do not know these
+interactions occur because we have never observed them. These so-called
+``false-negatives'' bias data and hinder inference about the structure
+and dynamics of interaction networks. Here, we demonstrate the realized
+rate of false-negatives in data can be quite high, even in thoroughly
+sampled systems, due to the intrinsic variation in abundances across
+species in a community. We illustrate how a null model of occurrence
+detection can be used to estimate the false-negative rate in a given
+dataset. We also show how to directly incorporate uncertainty due to
+observation error into model-based predictions of interaction
 probabilities between species. One hypothesis is that interactions
@@
 
-which yields the normal approximation
+which is obatinable by definition (supp 1.)
+
+For notation, here we refer to a normal distribution with mean \(\mu\)
+and standard-deviation \(\sigma\) as \(\mathcal{N}(\mu,\sigma)\)
+
+Then yields the normal approximation
 

### 2023-01-15 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@914afb2218a709c84b34774e733984514e44dffe 🚀

@@
 then being correctly observed with probabilities given by \(p_{fp}\) and
-\(p_{fn}\) to yield a single boolean outcome for each particle.
-(``Resampling'' within fig.~\ref{fig:resampling_concept} (B)). Over many
-samples of particles, the resulting frequency of `true' outcomes is a
-single resample of the interaction probability \(p_{ij}^*\). Across
-several samples each of several particles, this forms a distribution of
+\(p_{fn}\) to yield a single boolean outcome for each particle
+(``Resampling'' within fig.~\ref{fig:resampling_concept} (B)). Across of
+many particles, the resulting frequency of `true' outcomes is a single
+resample of the interaction probability \(p_{ij}^*\). Across several
+samples each of several particles, this forms a distribution of
 probabilities which are adjusted by the true and false negative rates.
@@
 computation required by simulating samples from this distribution
-directly. Further, it enables continuous extension of the number of
-particles \(n_p\) as a uncertainty width. The natural analogue for the
-number of particles sampled is the number of observations of
-co-occurrence for a given pair of species---the fewer the particles, the
-higher the variance of the resulting approximation. The normal
+directly. Further, it enables the extension of the natural analogue
+between \(n_p\) (the number of particles) and the number of observations
+of co-occurrence for a given pair of species---the fewer the particles,
+the higher the variance of the resulting approximation. The normal
 approximation is undefined for 0 particles (i.e.~0 observations
 co-occurrence), although as \(n_p\) approaches 0 the approximated normal
-(once truncated) approaches a uniform distribution on the interval
+(once truncated) approaches the uniform distribution on the interval
 \((0,1)\), the maximum entropy distribution where we have no information

### 2023-01-18 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@049ecca54d9d7f2aabeb6256287c983af898dbcf 🚀

@@
 
-Our work highlights the need for a quantitatively robust approach to
-sampling design, both for interactions (Jordano 2016) and all other
-aspects of biodiversity (Carlson \emph{et al.} 2020). As anthropogenic
-forces create rapid shifts in our planet's climate and biosphere, this
-is an imperative to maximize the amount of ecological information we get
-in our finite samples, and make our inferences and decisions based on
-this data as robust as possible. Where we choose to sample, and how
-often we choose to sample there, has strong impacts on the inferences we
-make from data. Incorporating a better understanding of sampling effort
-and bias to the design of biodiversity monitoring systems, and the
-inference and predictive models we apply to this data, is imperative in
-understanding how biodiversity is changing, and making forecasts that
-can guide conservation action.
-
 \hypertarget{acknowledgements}{%

### 2023-01-18 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@d94f60669f977395219738fc8e002f2be9273b27 🚀

@@
 
-In this section, we demonstate how difference in relative-abundance can
-lead to many false-negatives in interaction data. We also introduce a
-method for producing a null estimate of the false-negative-rate in
-datasets via simulation, and a method for incorporating uncertainty
+In this section, we demonstate how differences in species'
+relative-abundance can lead to many false-negatives in interaction data.
+We also introduce a method for producing a null estimate of the
+false-negative-rate in datasets via simulation. Because the true
+false-negative-rate is latent, we can never actually be sure how many
+false-negatives are in our data. However, here we outline an approach to
+deal with this fact---first by using simulation to estimate the
+false-negative-rate for a dataset of a fixed size using neutral models
+of observation. We then illustrate how to incorporate uncertainty
 directly into predictions of species interactions to account for
-observation error.
+observation error based on null estimates of both false-positive rates
+(as an priori estimate of species misidentification probability) and
+false-positive rates (as generated via the method we introduce).
 
@@
 range of each species aren't informative because co-occurrence was not
-possible, and therefore neither was an interaction. Second, we can use
-this relation to compute the expected number of total observations
-needed to obtain a ``goal'' number of observations of a particular pair
-of species (fig.~\ref{fig:geometric}(B)). As an example, if we
-hypothesize that \(A\) and \(B\) do not interact, and we want to see
-species \(A\) and \(B\) both co-occurring and \emph{not interacting} 10
-times to be confident this is a true negative, then we need an expected
-1000 observations of all species if the relative abundances of \(A\) and
+possible, and therefore neither was an interaction. If some of the
+``worst-case'' FNRs presented in fig.~\ref{fig:geometric}(A) seem
+unrealistically high, considering that species are observed in
+proportion to their relative abundance. In the next section we
+demonstrate that the distribution of abundance in ecosystems can lead to
+very high realized values of FNR (\(p_{fn}\)) simply as an artifact of
+sampling effort. Second, we can use this relation to compute the
+expected number of total observations needed to obtain a ``goal'' number
+of observations of a particular pair of species
+(fig.~\ref{fig:geometric}(B)). As an example, if we hypothesize that
+\(A\) and \(B\) do not interact, and we want to see species \(A\) and
+\(B\) both co-occurring and \emph{not interacting} 10 times to be
+confident this is a true negative, then we need an expected 1000
+observations of all species if the relative abundances of \(A\) and
 \(B\) are both \(0.1\).
-
-Because the true FNR is latent, we can never actually be sure what the
-actual number of false-negatives in our data---however, we can use
-simulation to estimate the FNR for datasets of a given size using
-neutral models of observation. If some of the ``worst-case'' FNRs
-presented in fig.~\ref{fig:geometric}(A) seem unrealistically high,
-considering that species are observed in proportion to their relative
-abundance. In the next section we demonstrate that the distribution of
-abundance in ecosystems can lead to very high realized values of FNR
-(\(p_{fn}\)) simply as an artifact of sampling effort.
 

### 2023-01-18 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@29c663e2b848f627726a16f11a5eada481426451 🚀

@@
 The importance of \emph{sampling effort} and its impact on resulting
-ecological data has produced a rich body of literature.The recorded
+ecological data has produced a rich body of literature. The recorded
 number of species in a dataset or sample depends on the total number of
@@
 of population abundance (Griffiths 1998). This relationship between
-sampling effort and spatial coverage and species detectability has
+sampling effort, spatial coverage, and species detectability has
 motivated more quantitatively robust approaches to account for error in
@@
 interaction is ``important'' for both species; Cazelles \emph{et al.}
-(2016)), but in this paper we later show increasing strength of
+(2016)), but in this paper we later show increasing strength of these
 associations leads to increasing probability of false-negatives in

### 2023-01-18 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@29c663e2b848f627726a16f11a5eada481426451 🚀

@@
 {\small{\bfseries Keywords}:\par
-community ecology\\network ecology\\sampling effort\\species
-interactions\\spatial sampling\\simulation\\}
+species interactions\\network ecology\\sampling effort\\spatial
+ecology\\null model\\}
 }

### 2023-01-18 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@4223e1f8a53cac167f3fafac47821bd9fd219043 🚀

@@
 geometric distribution, a special case of the negative-binomial
-distribution) is shown in fig.~\ref{fig:geometric}(A) for varying values
+distribution) is shown in fig.~\ref{fig:geometric}(a) for varying values
 of \(p_{fn}\) and illustrates a fundamental link between our ability to
@@
 
-From fig.~\ref{fig:geometric}(A) it is clear that the more often we see
+From fig.~\ref{fig:geometric}(a) it is clear that the more often we see
 two species co-occurring, but \emph{not interacting}, the more likely
@@
 possible, and therefore neither was an interaction. If some of the
-``worst-case'' FNRs presented in fig.~\ref{fig:geometric}(A) seem
+``worst-case'' FNRs presented in fig.~\ref{fig:geometric}(a) seem
 unrealistically high, considering that species are observed in
@@
 of observations of a particular pair of species
-(fig.~\ref{fig:geometric}(B)). As an example, if we hypothesize that
+(fig.~\ref{fig:geometric}(b)). As an example, if we hypothesize that
 \(A\) and \(B\) do not interact, and we want to see species \(A\) and
@@
 \includegraphics{./figures/fig1.png}
-\caption{\textbf{(A)} The probability that an observed interaction is a
+\caption{\textbf{(a)} The probability that an observed interaction is a
 true negative (y-axis) given how many times it has been sampled as a
@@
 cumulative distribution function (cdf) of the geometric distribution.
-\textbf{(B)} The expected number of total observations needed (colors)
+\textbf{(b)} The expected number of total observations needed (colors)
 to observe 10 co-occurrences between a species with relative abundance
 \(P(A)\) (x-axis) and a second species with relative abundance \(P(Y)\).
-\textbf{(C)}: false-negative-rate (y-axis) as a function of total
+\textbf{(c)}: false-negative-rate (y-axis) as a function of total
 sampling effort (x-axis) and network size, computed using the method
@@
 computed. Means denoted with points, with 1 in the first shade and 2 in
-the second. \textbf{(D)}: Same as \textbf{(C)}, except using empirical
+the second. \textbf{(d)}: Same as \textbf{(c)}, except using empirical
 food webs from Mangal database, where richness. The outlier on
-\textbf{(D)} is a 714 species food-web.}\label{fig:geometric}
+\textbf{(d)} is a 714 species food-web.}\label{fig:geometric}
 }
@@
 process is illustrated conceptually in
-fig.~\ref{fig:resampling_concept}(A).
-
-In fig.~\ref{fig:geometric}(C) we see this model of observation applied
+fig.~\ref{fig:resampling_concept}(a).
+
+In fig.~\ref{fig:geometric}(c) we see this model of observation applied
 to niche model networks across varying levels of species richness, and
-in fig.~\ref{fig:geometric}(D) the observation model applied to Mangal
+in fig.~\ref{fig:geometric}(d) the observation model applied to Mangal
 food webs. For all niche model simulations in this manuscript, for a
@@
 
-From fig.~\ref{fig:geometric}(C) it is evident that the number of
+From fig.~\ref{fig:geometric}(c) it is evident that the number of
 species considered in a study is inseparable from the
@@
 account when designing samples of ecological networks in the future. We
-see a similar qualitative pattern in fig.~\ref{fig:geometric}(D) where
+see a similar qualitative pattern in fig.~\ref{fig:geometric}(d) where
 the FNR drops off quickly as a function of observation effort, mediated
@@
 for sampling---is the goal to detect a particular species (as in
-fig.~\ref{fig:geometric}(C)), or to get a representative sample of
+fig.~\ref{fig:geometric}(c)), or to get a representative sample of
 interactions across the species pool? These arguments are
@@
 \includegraphics{./figures/uncertainty_sampler.png}
-\caption{(A) The process for estimating the false-negative-rate (FNR)
+\caption{(a) The process for estimating the false-negative-rate (FNR)
 for an interaction dataset consisting of \(N\) total observed
-interactions. (B) The method for resampling interaction probability
-based on estimates of false-negative and false-positive rates. (C) The
+interactions. (b) The method for resampling interaction probability
+based on estimates of false-negative and false-positive rates. (c) The
 method for interaction probability resampling applied to three mammals
@@
 line. The histogram is simulated from the resampling process, and the
-line indicates the gaussian approximation to this
-distribution.}\label{fig:resampling_concept}
+line indicates the gaussian approximation to this distribution. Both
+resampling simulations and the gaussian approximation is applied with
+\(n_p =150\)}\label{fig:resampling_concept}
 }
@@
 \(p_{fn}\) to yield a single boolean outcome for each particle
-(``Resampling'' within fig.~\ref{fig:resampling_concept} (B)). Across of
+(``Resampling'' within fig.~\ref{fig:resampling_concept}(b)). Across of
 many particles, the resulting frequency of `true' outcomes is a single
@@
 a set of a few resampled interaction probabilities between mammals and
-parasite species shown in figure fig.~\ref{fig:resampling_concept}(C).
+parasite species shown in figure fig.~\ref{fig:resampling_concept}(c).
 
@@
 case, the probability of observing a single false-negative in our naive
-model from fig.~\ref{fig:geometric}(A) is \(p_{fn}= 1-P(AB)\), which due
+model from fig.~\ref{fig:geometric}(a) is \(p_{fn}= 1-P(AB)\), which due
 to the above inequality implies \(p_{fn}>1-P(A)P(B)\). This indicates an
@@
 relevant as it is a better indicator of prediction of false-negatives.
-The results of these simulations are shown in
-fig.~\ref{fig:addedfnr}(A\&B).
+The results of these simulations are shown in fig.~\ref{fig:addedfnr}(a
+\& b).
 
@@
 \includegraphics{./figures/fig3.png}
-\caption{\textbf{(A)} The area-under the receiver-operator curve
-(ROC-AUC) and \textbf{(B)} The area-under the precision-recall curve
+\caption{\textbf{(a)} The area-under the receiver-operator curve
+(ROC-AUC) and \textbf{(b)} The area-under the precision-recall curve
 (PR-AUC; right) for each different predictive model (colors/shapes)
 across a spectrum of the proportion of added false-negatives (x-axis).
-\textbf{(C)} The mean trophic-level of all species in a network
+\textbf{(c)} The mean trophic-level of all species in a network
 generated with the niche model across different species richnesses
@@
 
-One interesting result seen in fig.~\ref{fig:addedfnr}(A\&B) is that the
-ROC-AUC value does not approach random in the same way the PR-AUC curve
-does as we increase the added FNR. The reason for this is that ROC-AUC
-is fundamentally not as useful a metric in assessing predictive capacity
-as PR-AUC. As we keep adding more false-negatives, the network
+One interesting result seen in fig.~\ref{fig:addedfnr}(a \& b) is that
+the ROC-AUC value does not approach random in the same way the PR-AUC
+curve does as we increase the added FNR. The reason for this is that
+ROC-AUC is fundamentally not as useful a metric in assessing predictive
+capacity as PR-AUC. As we keep adding more false-negatives, the network
 eventually becomes a zeros matrix, and these models can still learn to
@@
 We also consider how the FNR affects network properties. In
-fig.~\ref{fig:addedfnr}(C) we see the mean trophic level across networks
+fig.~\ref{fig:addedfnr}(c) we see the mean trophic level across networks
 simulated using the niche model (as above), across a spectrum of FNR
@@
 that have not been observed but that still may become climatically
-infeasible. As is evident from fig.~\ref{fig:geometric}(A), we can never
+infeasible. As is evident from fig.~\ref{fig:geometric}(a), we can never
 guarantee there are no false-negatives in data. In recent years, there
@@
 species pool into account when deciding how many total samples is
-sufficient for an ``acceptable'' FNR (fig.~\ref{fig:geometric}(C \& D)).
+sufficient for an ``acceptable'' FNR (fig.~\ref{fig:geometric}(c \& d)).
 Further the spatial and temporal turnover of interactions means any
@@
 model food webs, false-negatives do not impact the measure of total
-trophic levels until very high FNR (figure fig.~\ref{fig:addedfnr}(C)),
+trophic levels until very high FNR (figure fig.~\ref{fig:addedfnr}(c)),
 although we cannot generalize this further to other properties. This has

### 2023-01-18 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@b4bd3f5d37331adac55f411fca44a592ffee5897 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@4492ba2cf17e43e9026bc17d4063ad707480e746 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@b87502c61ca9e00e7fbeba50799359bb66a76753 🚀

@@
 
+\begin{figure}
+\hypertarget{fig:concept}{%
+\centering
+\includegraphics{./figures/concept.png}
+\caption{This conceptual example considers a sample of the trophic
+community of bears, wolves, salmon (pink fish), pike (yellow fish),
+berry trees, and aspen trees. The true metaweb (all realized
+interactions across the entire spatial extent) is shown on the left. In
+the center is what a hypothetical ecologist samples at each site. Notice
+that although bears are observed co-occurring with both salmon and pike,
+there was never a direct observation of bears eating pike, even though
+they actually do. Therefore, this interaction between bears and pike is
+a false-negative.}\label{fig:concept}
+}
+\end{figure}
+
 The importance of \emph{sampling effort} and its impact on resulting
@@
 into predictive models.
-
-\begin{figure}
-\hypertarget{fig:concept}{%
-\centering
-\includegraphics{./figures/concept.png}
-\caption{This conceptual example considers a sample of the trophic
-community of bears, wolves, salmon (pink fish), pike (yellow fish),
-berry trees, and aspen trees. The true metaweb (all realized
-interactions across the entire spatial extent) is shown on the left. In
-the center is what a hypothetical ecologist samples at each site. Notice
-that although bears are observed co-occurring with both salmon and pike,
-there was never a direct observation of bears eating pike, even though
-they actually do. Therefore, this interaction between bears and pike is
-a false-negative.}\label{fig:concept}
-}
-\end{figure}
 
@@
 across all samples approaches a normal distribution with mean \(np\) and
-variance \(np(1-p)\). We can use this to correct the estimate \(p_{ij}\)
-based on the expected false-negative-rate \(p_{fn}\) and false-positive
-rate \(p_{fp}\) to obtain the limiting distribution as the number of
-resamples approaches infinity for the resampled \(p_{ij}^*\) for a given
-number of particles \(n_p\). We do this by first adjusting for the rates
-of observation error to get the mean resampled probability,
-\(\mathbb{E}[{p_{ij}^*}]\), as
+variance \(np(1-p)\). For notation, here we refer to a normal
+distribution with mean \(\mu\) and standard-deviation \(\sigma\) as
+\(\mathcal{N}(\mu,\sigma)\). We can use this to correct the estimate
+\(p_{ij}\) based on the expected false-negative-rate \(p_{fn}\) and
+false-positive rate \(p_{fp}\) to obtain the limiting distribution as
+the number of resamples approaches infinity for the resampled
+\(p_{ij}^*\) for a given number of particles \(n_p\). We do this by
+first adjusting for the rates of observation error to get the mean
+resampled probability, \(\mathbb{E}[{p_{ij}^*}]\), as
 
@@
 
-which is obatinable by definition (supp 1.)
-
-For notation, here we refer to a normal distribution with mean \(\mu\)
-and standard-deviation \(\sigma\) as \(\mathcal{N}(\mu,\sigma)\)
-
-Then yields the normal approximation
+This yields the normal approximation
 

### 2023-01-18 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@e7b136a5043c607ef450d8b87226b0e4e956ead9 🚀

@@
 directly into predictions of species interactions to account for
-observation error based on null estimates of both false-positive rates
-(as an priori estimate of species misidentification probability) and
-false-positive rates (as generated via the method we introduce).
+observation error based on null estimates of both the false-positive
+rate (as an \emph{a priori} estimate of species misidentification
+probability) and false-negative rate (as generated via the method we
+introduce).
 
@@
 the probability of a true-negative (denoted \(p_{tn}\)) is given by
-\(p_{tn}=1-(p_{fn})^N\). This relation (the probability-mass-function of
-geometric distribution, a special case of the negative-binomial
-distribution) is shown in fig.~\ref{fig:geometric}(a) for varying values
-of \(p_{fn}\) and illustrates a fundamental link between our ability to
-reliably say an interaction doesn't exist---\(p_{tn}\)---and the number
-of times \(N\) we have observed a given species. In addition, note that
-there is no non-zero \(p_{fn}\) for which we can ever \emph{prove} that
-an interaction does not exist---no matter how many observations of
+\(p_{tn}=1-(p_{fn})^N\). This relation (the
+cumalitive-distribution-function of geometric distribution, a special
+case of the negative-binomial distribution) is shown in
+fig.~\ref{fig:geometric}(a) for varying values of \(p_{fn}\) and
+illustrates a fundamental link between our ability to reliably say an
+interaction doesn't exist---\(p_{tn}\)---and the number of times \(N\)
+we have observed a given species. In addition, note that there is no
+non-zero \(p_{fn}\) for which we can ever \emph{prove} that an
+interaction does not exist---no matter how many observations of
 non-interactions \(N\) we have, \(p_{tn}<1\).
@@
 range of each species aren't informative because co-occurrence was not
-possible, and therefore neither was an interaction. If some of the
-``worst-case'' FNRs presented in fig.~\ref{fig:geometric}(a) seem
-unrealistically high, considering that species are observed in
-proportion to their relative abundance. In the next section we
-demonstrate that the distribution of abundance in ecosystems can lead to
-very high realized values of FNR (\(p_{fn}\)) simply as an artifact of
-sampling effort. Second, we can use this relation to compute the
+possible, and therefore neither was an interaction. In the next section
+we demonstrate that the distribution of abundance in ecosystems can lead
+to very high realized values of FNR (\(p_{fn}\)) simply as an artifact
+of sampling effort. Second, we can use this relation to compute the
 expected number of total observations needed to obtain a ``goal'' number
@@
 consequence of abundance distributions spanning many orders of magnitude
-of abundance is that observing two ``rare'' species interacting requires
-two low probability events: observing two rare species \emph{at the same
-time}.
+is that observing two ``rare'' species interacting requires two low
+probability events: observing two rare species \emph{at the same time}.
 
 To simulate the process of observation, for an ecological network \(M\)
-with \(S\) species, we sample abundances for each species from a
-standard-log-normal distribution. For each true interaction in the
-adjacency matrix \(M\) (i.e. \(M_{ij}=1\)) we estimate the probability
+with \(S\) species, we sample relative abundances for each species from
+a standard-log-normal distribution. For each true interaction in the
+adjacency matrix \(M\) (i.e.~\(M_{ij}=1\)) we estimate the probability
 of observing both species \(i\) and \(j\) at a given place and time by
-simulating \(n\) observations of all individuals of any a species, where
+simulating \(n\) observations of all individuals of any species, where
 the species of the individual observed at the \(\{1,2,\dots,n\}\)-th
-observation is drawn from the generated log-normal distribution of
+observation is drawn from the generated categorical distribution of
 abundances. For each pair of species \((i,j)\), if both \(i\) and \(j\)
@@
 independent replicates of unique niche model networks per unique number
-of observations \(n\). All analyses presented here are done in Julia
-v1.8 (Bezanson \emph{et al.} 2015) using both EcologicalNetworks.jl v0.5
-and Mangal.jl v0.4 (Banville \emph{et al.} 2021) and are hosted on
+of total interactions observed \(n\). All analyses presented here are
+done in Julia v1.8 (Bezanson \emph{et al.} 2015) using both
+EcologicalNetworks.jl v0.5 and Mangal.jl v0.4 (Banville \emph{et al.}
+2021) and are hosted on
 \href{https://github.com/gottacatchenall/ms_false_negatives/tree/main/src}{Github}).
@@
 account when designing samples of ecological networks in the future. We
-see a similar qualitative pattern in fig.~\ref{fig:geometric}(d) where
-the FNR drops off quickly as a function of observation effort, mediated
-by total richness. The practical consequence of the bottom row of
-fig.~\ref{fig:geometric} is whether the total number of observations of
-all species (the x-axis) for the threshold FNR we deem acceptable (the
-y-axis) is feasible. This raises two points: first, empirical data on
-interactions are subject to the practical limitations of funding and
-human-work hours, and therefore existing data tend to fall on the order
-of hundreds or thousands observations of individuals per site. Clear
-aggregation of data on sampling effort has proven difficult to find and
-a meta-analysis of network data and sampling effort seems both pertinent
-and necessary, in addition to the effects of aggregation of interactions
-across taxonomic scales (Gauzens \emph{et al.} 2013; Giacomuzzo \&
-Jordán 2021). This inherent limitation on in-situ sampling means we
-should optimize where we sample across space so that for a given number
-of samples, we obtain the maximum information possible. Second, what is
-meant by ``acceptable'' FNR? This raises the question: does a shifting
-FNR lead to rapid transitions in our ability inference and predictions
-about the structure and dynamics of networks, or does it produce a
-roughly linear decay in model efficacy? We explore this in the next
-section.
+see a similar qualitative pattern in empirical networks
+(fig.~\ref{fig:geometric}(d)) where the FNR drops off quickly as a
+function of observation effort, mediated by total richness. The
+practical consequence of the bottom row of fig.~\ref{fig:geometric} when
+conducting an analysis is whether there are enough total number of
+observed interactions (the x-axis) for the threshold FNR we deem
+acceptable (the y-axis) is feasible. This raises two points: first,
+empirical data on interactions are subject to the practical limitations
+of funding and human-work hours, and therefore existing data tend to
+fall on the order of hundreds or thousands observations of individuals
+per site. Clear aggregation of data on sampling effort has proven
+difficult to find and a meta-analysis of network data and sampling
+effort seems both pertinent and necessary, in addition to the effects of
+aggregation of interactions across taxonomic scales (Gauzens \emph{et
+al.} 2013; Giacomuzzo \& Jordán 2021). This inherent limitation on
+in-situ sampling means we should optimize where we sample across space
+so that for a given number of samples, we obtain the maximum information
+possible. Second, what is meant by ``acceptable'' FNR? This raises the
+question: does a shifting FNR lead to rapid transitions in our ability
+inference and predictions about the structure and dynamics of networks,
+or does it produce a roughly linear decay in model efficacy? We explore
+this in the final section.
 
@@
 similar to above to generate expectations about the number of
-false-negatives in a data set of a given size. This could prove fruitful
+false-negatives in a dataset of a given size. This could prove fruitful
 both for designing surveys of interactions but also because we may want
@@
 introduce adjusts the value of a model's predictions to produce a
-distribution of interaction probabilities, which are adjusted by a given
+distribution of interaction probabilities corrected by a given
 false-negative-rate \(p_{fn}\) and false-positive-rate \(p_{fp}\)
-(outlined in figure fig.~\ref{fig:resampling_concept}). We describe
-first how to sample from this distribution of adjusted interaction
+(outlined in figure fig.~\ref{fig:resampling_concept}). First we
+describe how to sample from this distribution of adjusted interaction
 probabilities via simulation, and show that this distribution can be
@@
 
-We then consider the output prediction from an arbitrary prediction
-model, which is the probability \(p_{ij}\) that two species \(i\) and
-\(j\) interact. To get an estimate of \(p_{ij}\) that accounts for
-observation error, we resample the probability of each interaction
-\(p_{ij}\) by simulating a set of several `particles,' where each
-particle is a realization of an interaction occurring (either true or
-false with probabilities \(p_{ij}\) and \(1-p_{ij}\) respectively) and
-then being correctly observed with probabilities given by \(p_{fp}\) and
+To get an estimate of each interaction probability that accounts for
+observation error, we resample the output prediction from an arbitrary
+model for each interaction \(p_{ij}\) by simulating a set of several
+`particles.' Each particle is a realization of an interaction
+\emph{actually occurring} assuming \(p_{ij}\) is a correct estimate of
+the probability of an interaction being \emph{observed}. Each particle
+starts as being drawn as true or false according to \(p_{ij}\), and then
+adjusting this by the rate of observation error given by \(p_{fp}\) and
 \(p_{fn}\) to yield a single boolean outcome for each particle
@@
 many particles, the resulting frequency of `true' outcomes is a single
-resample of the interaction probability \(p_{ij}^*\). Across several
+resample of the probability \(p_{ij}^*\) that the interaction actually
+\emph{occurred}, not just that it was \emph{observed}. Across several
 samples each of several particles, this forms a distribution of
-probabilities which are adjusted by the true and false negative rates.
+probabilities which are adjusted by the true and false-negative-rates.
 
@@
 bootstrap aggregated (or bagged) with 100 replicates each. We partition
-the data into 80-20 training-test split, and then seed the training data
-with false negatives at varying rates, but crucially do nothing to the
-test data. We fit all of these models using MLJ.jl, a high-level Julia
-framework for a wide-variety of ML models (Blaom \emph{et al.} 2020). We
-evaluate the efficacy of these models using two common measures of
-binary classifier performance: the area under the receiver-operator
-curve (ROC-AUC) and the area under the precision-recall curve (PR-AUC),
-for more details see Poisot (2022). Here, PR-AUC is slightly more
-relevant as it is a better indicator of prediction of false-negatives.
-The results of these simulations are shown in fig.~\ref{fig:addedfnr}(a
-\& b).
+the data into 80-20 training-test splits, and then seed the training
+data with false negatives at varying rates, but crucially do
+\emph{nothing} to the test data. We fit all of these models using
+MLJ.jl, a high-level Julia framework for a wide-variety of ML models
+(Blaom \emph{et al.} 2020). We evaluate the efficacy of these models
+using two common measures of binary classifier performance: the area
+under the receiver-operator curve (ROC-AUC) and the area under the
+precision-recall curve (PR-AUC), for more details see Poisot (2022).
+Here, PR-AUC is slightly more relevant as it is a better indicator of
+prediction of false-negatives. The results of these simulations are
+shown in fig.~\ref{fig:addedfnr}(a \& b).
 

### 2023-01-19 src/make_fig02.jl
:bug: typo in paper name

@@ -15,7 +15,7 @@ diffs = CSV.read(joinpath("src", "artifacts", "joint_marginal_diffs.csv"), DataF
 metadata = CSV.read(joinpath("src", "artifacts", "metadata.csv"), DataFrame)
 
 titles = Dict(
-    "kolpelke_et_al_2017" => "Kopelke et al. (2017)",
+    "kolpelke_et_al_2017" => "Kolpelke et al. (2017)",
     "hadfield_2014" => "Hadfield et al. (2014)",
     "havens_1992" => "Havens (1992)", 
     "ponisio_2017" => "Ponisio et al. (2017)",

### 2023-01-19 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@af66c40bb666900249d36c51087196be6372a8e5 🚀

@@
 ``false-negatives'' bias data and hinder inference about the structure
-and dynamics of interaction networks. Here, we demonstrate the realized
-rate of false-negatives in data can be quite high, even in thoroughly
-sampled systems, due to the intrinsic variation in abundances across
-species in a community. We illustrate how a null model of occurrence
-detection can be used to estimate the false-negative rate in a given
-dataset. We also show how to directly incorporate uncertainty due to
-observation error into model-based predictions of interaction
-probabilities between species. One hypothesis is that interactions
-between ``rare'' species are themselves rare because these species are
-less likely to encounter one-another than species of higher relative
-abundance, and that this can (in part) explain the common pattern of
-nestedness in bipartite interaction networks. However, we demonstrate
-that across several datasets of spatial or temporally replicated
-networks, there are positive associations between species co-occurrence
-and interactions, which suggests these interactions among ``rare''
-species actually exist but simply are not observed. Finally, we assess
-how false negatives influence various models of network prediction, and
-recommend directly accounting for observation error in predictive
-models. We conclude by discussing how the understanding of
-false-negatives can inform how we design monitoring schemes for species
-interactions.\\%
+and dynamics of interaction networks. Here, we show the realized number
+of false-negatives in data can be quite high, even in thoroughly sampled
+systems, due to variation in abundances in a community. We provide a
+null model of occurrence detection to estimate the false-negative rate
+in a given dataset. We also show how to directly incorporate uncertainty
+due to observation error into model-based predictions of interactions
+between species. One hypothesis is interactions between ``rare'' species
+are themselves rare because these species are less likely to encounter
+one-another than species of higher relative abundance, and this can (in
+part) explain the common pattern of nestedness in bipartite interaction
+networks. However, we demonstrate that across several datasets of
+spatial/temporally replicated networks, there are positive associations
+between species co-occurrence and interactions, which suggests these
+interactions among ``rare'' species actually exist but simply are not
+observed. Finally, we assess how false negatives influence various
+models of network prediction, and recommend directly accounting for
+observation error in predictive models. We conclude by discussing how
+the understanding of false-negatives can inform how we design monitoring
+schemes for species interaction surveys.\\%
 

### 2023-01-19 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@8e6ee5a7b9efde3dd5a1f78187a66a4d871429d1 🚀

@@
 ``false-negatives'' bias data and hinder inference about the structure
-and dynamics of interaction networks. Here, we show the realized number
-of false-negatives in data can be quite high, even in thoroughly sampled
-systems, due to variation in abundances in a community. We provide a
-null model of occurrence detection to estimate the false-negative rate
-in a given dataset. We also show how to directly incorporate uncertainty
-due to observation error into model-based predictions of interactions
-between species. One hypothesis is interactions between ``rare'' species
-are themselves rare because these species are less likely to encounter
-one-another than species of higher relative abundance, and this can (in
-part) explain the common pattern of nestedness in bipartite interaction
-networks. However, we demonstrate that across several datasets of
-spatial/temporally replicated networks, there are positive associations
-between species co-occurrence and interactions, which suggests these
-interactions among ``rare'' species actually exist but simply are not
-observed. Finally, we assess how false negatives influence various
-models of network prediction, and recommend directly accounting for
-observation error in predictive models. We conclude by discussing how
-the understanding of false-negatives can inform how we design monitoring
-schemes for species interaction surveys.\\%
+and dynamics of interaction networks. Here, we demonstrate the realized
+rate of false-negatives in data can be quite high, even in thoroughly
+sampled systems, due to the intrinsic variation in abundances across
+species in a community. We illustrate how a null model of occurrence
+detection can be used to estimate the false-negative rate in a given
+dataset. We also show how to directly incorporate uncertainty due to
+observation error into model-based predictions of interaction
+probabilities between species. One hypothesis is that interactions
+between ``rare'' species are themselves rare because these species are
+less likely to encounter one-another than species of higher relative
+abundance, and that this can (in part) explain the common pattern of
+nestedness in bipartite interaction networks. However, we demonstrate
+that across several datasets of spatial or temporally replicated
+networks, there are positive associations between species co-occurrence
+and interactions, which suggests these interactions among ``rare''
+species actually exist but simply are not observed. Finally, we assess
+how false negatives influence various models of network prediction, and
+recommend directly accounting for observation error in predictive
+models. We conclude by discussing how the understanding of
+false-negatives can inform how we design monitoring schemes for species
+interactions.\\%
 

### 2023-01-19 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@b1111fbc4467eccc97cf9b54046a9cf4c689a728 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@8b2cb66e35b89fb801c6971762a748f2ed2b5f3f 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@8e6ee5a7b9efde3dd5a1f78187a66a4d871429d1 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@ba79ef2cc47ef1115261d1c57192fcb4e3a85138 🚀

@@
 ``false-negatives'' bias data and hinder inference about the structure
-and dynamics of interaction networks. Here, we demonstrate the realized
-rate of false-negatives in data can be quite high, even in thoroughly
-sampled systems, due to the intrinsic variation in abundances across
-species in a community. We illustrate how a null model of occurrence
-detection can be used to estimate the false-negative rate in a given
-dataset. We also show how to directly incorporate uncertainty due to
-observation error into model-based predictions of interaction
-probabilities between species. One hypothesis is that interactions
-between ``rare'' species are themselves rare because these species are
-less likely to encounter one-another than species of higher relative
-abundance, and that this can (in part) explain the common pattern of
-nestedness in bipartite interaction networks. However, we demonstrate
-that across several datasets of spatial or temporally replicated
-networks, there are positive associations between species co-occurrence
-and interactions, which suggests these interactions among ``rare''
-species actually exist but simply are not observed. Finally, we assess
-how false negatives influence various models of network prediction, and
-recommend directly accounting for observation error in predictive
-models. We conclude by discussing how the understanding of
-false-negatives can inform how we design monitoring schemes for species
-interactions.\\%
+and dynamics of interaction networks. Here, we show the realized number
+of false-negatives in data can be quite high, even in thoroughly sampled
+systems, due to variation in abundances in a community. We provide a
+null model of occurrence detection to estimate the false-negative rate
+in a given dataset. We also show how to directly incorporate uncertainty
+due to observation error into model-based predictions of interactions
+between species. One hypothesis is interactions between ``rare'' species
+are themselves rare because these species are less likely to encounter
+one-another than species of higher relative abundance, and this can (in
+part) explain the common pattern of nestedness in bipartite interaction
+networks. However, we demonstrate that across several datasets of
+spatial/temporally replicated networks, there are positive associations
+between species co-occurrence and interactions, which suggests these
+interactions among ``rare'' species actually exist but simply are not
+observed. Finally, we assess how false negatives influence various
+models of network prediction, and recommend directly accounting for
+observation error in predictive models. We conclude by discussing how
+the understanding of false-negatives can inform how we design monitoring
+schemes for species interaction surveys.\\%
+
+\vfill
 

### 2023-01-19 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@ba79ef2cc47ef1115261d1c57192fcb4e3a85138 🚀

--- 2023-01-19 preprint.tex
@@
 species interactions\\network ecology\\sampling effort\\spatial
-ecology\\null model\\}
+ecology\\null models\\}
 }

### 2023-01-19 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@db88b22e66fe7a52f34004194ca2201959f6d789 🚀

@@
 schemes for species interaction surveys.\\%
+        {\bfseries Keywords:}\,species interactions, network ecology,
+sampling effort, spatial ecology, null models\\%
 
@@
 
+{\small{\bfseries Keywords}:\par
+species interactions\\network ecology\\sampling effort\\spatial
+ecology\\null models\\}
 \vfill

### 2023-01-19 .assets/scripts/abstract.py
:shrug:

@@ -9,7 +9,7 @@ abstract["abstractdata"] = {}
 if type(metadata["abstract"]) == dict:
     abstract["abstractdata"]["structured"] = True
     abstract["abstractdata"]["content"] = [{"key": header, "value": metadata["abstract"][header]} for header in metadata["abstract"]]
-
+    print("hello from abstract.py")
 if type(metadata["abstract"]) == list:
     abstract["abstractdata"]["itemized"] = True
     abstract["abstractdata"]["content"] = [header for header in metadata["abstract"]]

### 2023-01-19 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@db3d8784d332f0b18890069a0d14ddb014fae540 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@03fc93283dfacb8a049af58abd945d3e5baa0c09 🚀

--- 2023-01-19 draft.tex
@@
 EcologicalNetworks.jl v0.5 and Mangal.jl v0.4 (Banville \emph{et al.}
-2021) and are hosted on
-\href{https://github.com/gottacatchenall/ms_false_negatives/tree/main/src}{Github}).
-Note that the empirical data, for the reasons described above, very
-likely already contains many false-negatives, we'll revisit this issue
-in the final section.
+2021) and are hosted on \href{}{Github} (\textbf{link removed for
+double-blind review}). Note that the empirical data, for the reasons
+described above, very likely already contains many false-negatives,
+we'll revisit this issue in the final section.
 
@@
 
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
-
-AG \& MDC acknowledge the support of the Liber Ero Chair for
-Biodiversity conservation and NSERC.
-
 \hypertarget{references}{%

### 2023-01-19 src/resampling/main.jl
src from other folder

@@ -1,0 +1,208 @@
+using EcologicalNetworks
+using Distributions
+using ProgressMeter
+using CairoMakie
+
+include(joinpath("src", "utils.jl"))
+
+ids = map(i -> i.ID, filter(i -> contains(i.Reference, "Hadfield"), web_of_life()))
+B = convert.(BipartiteNetwork, web_of_life.(ids))
+M = reduce(∪, B)
+
+function get_metadata()
+    C = zeros(Int64, size(M)) 
+    N = zeros(Int64, size(M))  
+
+    # We then move through the metaweb step by step
+    for (i,si) in enumerate(species(M; dims=1)), (j,sj) in enumerate(species(M; dims=2))
+        for b in B
+            if si in species(b)
+                if sj in species(b)
+                    C[i,j] += 1
+
+                    i_b_idx, j_b_idx = findall(x->x==si, b.T)[begin], findall(x->x==sj, b.B)[begin]
+                    if b[i_b_idx, j_b_idx] == 1
+                        N[i,j] += 1
+                    end
+                end
+            end
+        end
+    end
+    return C,N
+end 
+
+C,N = get_metadata()
+
+probabilistic_network = BipartiteProbabilisticNetwork(rand(size(M)...)) # Prob net object from EcologicalNetworks
+RAs = [rand(LogNormal(0,1), i) for i in size(probabilistic_network)]
+RAs = [r ./ sum(r) for r in RAs] 
+
+relabd = RelativeAbundance([M.T, M.B], RAs)
+cooc = CooccurrenceMatrix([M.T,M.B], C)
+ints = InteractionsMatrix([M.T,M.B], N)
+
+exp_fpr = Exponential(0.02)
+cooccurrence_sample = InteractionUncertaintySampler.sample(CooccurrenceSampler(relabd), 1000)
+mean_fnr = FNR(cooccurrence_sample, C, M)
+
+
+using DataFrames, CSV
+df = CSV.read("modelfit.csv", DataFrame)
+
+# predicted prob metaweb
+P = zeros(size(M))
+for r in eachrow(df)
+    i = findfirst(i->M.T[i]==string(r.speciesI), 1:length(M.T))
+    j = findfirst(i->M.B[i]==string(r.speciesJ), 1:length(M.B))
+    P[i,j] = r.prediction
+end 
+
[…]

### 2023-01-19 src/resampling/src/computemeasures.jl

@@ -1,0 +1,97 @@
+struct ConfusionMatrix
+    tp::Any
+    tn::Any
+    fp::Any
+    fn::Any
+    function ConfusionMatrix(a, b, c, d)
+        s = a + b + c + d
+        return new(a / s, b / s, c / s, d / s)
+    end
+end
+
+ConfusionMatrix(A::Matrix{Float64}) = ConfusionMatrix(A[1, 1], A[2, 2], A[2, 1], A[1, 2])
+ConfusionMatrix(A::Matrix) = ConfusionMatrix(A[1, 1], A[2, 2], A[2, 1], A[1, 2])
+
+tpr(M::ConfusionMatrix) = M.tp / (M.tp + M.fn)
+tnr(M::ConfusionMatrix) = M.tn / (M.tn + M.fp)
+ppv(M::ConfusionMatrix) = M.tp / (M.tp + M.fp)
+npv(M::ConfusionMatrix) = M.tn / (M.tn + M.fn)
+fnr(M::ConfusionMatrix) = M.fn / (M.fn + M.tp)
+fpr(M::ConfusionMatrix) = M.fp / (M.fp + M.tn)
+fdir(M::ConfusionMatrix) = M.fp / (M.fp + M.tp)
+fomr(M::ConfusionMatrix) = M.fn / (M.fn + M.tn)
+plr(M::ConfusionMatrix) = tpr(M) / fpr(M)
+nlr(M::ConfusionMatrix) = fnr(M) / tnr(M)
+pt(M::ConfusionMatrix) = sqrt(fpr(M)) / (sqrt(tpr(M)) + sqrt(fpr(M)))
+csi(M::ConfusionMatrix) = M.tp / (M.tp + M.fn + M.fp)
+prevalence(M::ConfusionMatrix) = (M.tp + M.fn) / (M.tp + M.fn + M.tn + M.fp)
+accuracy(M::ConfusionMatrix) = (M.tp + M.tn) / (M.tp + M.tn + M.fp + M.fn)
+balanced(M::ConfusionMatrix) = (tpr(M) + tnr(M)) * 0.5
+f1(M::ConfusionMatrix) = 2 * (ppv(M) * tpr(M)) / (ppv(M) + tpr(M))
+fm(M::ConfusionMatrix) = sqrt(ppv(M) * tpr(M))
+informedness(M::ConfusionMatrix) = tpr(M) + tnr(M) - 1.0
[…]

### 2023-01-19 src/resampling/src/modelfit.jl

@@ -1,0 +1,210 @@
+using EcologicalNetworks
+using Plots
+using Random
+using EcologicalNetworks
+using MultivariateStats
+using ProgressMeter
+using Statistics
+using DataFrames
+using MLJ
+using StatsBase
+using CSV
+
+include("computemeasures.jl")
+
+ids = map(i -> i.ID, filter(i -> contains(i.Reference, "Hadfield"), web_of_life()))
+B = convert.(BipartiteNetwork, web_of_life.(ids))
+M = reduce(∪, B)
+
+function load_features()
+
+
+    N = convert(UnipartiteNetwork, M)
+    K = EcologicalNetworks.mirror(N)
+
+    pc = fit(PPCA, Float64.(Array(K.edges)))
+    pr = MultivariateStats.transform(pc, Float64.(Array(K.edges)))
+
+    nf = 15
+
+    cooc = zeros(Bool, prod(size(M)))                  # H/P co-occurrence?
+    labels = zeros(Bool, prod(size(M)))                # H/P interaction?
+    features = zeros(Float64, (2 * nf, prod(size(M))))   # H/P latent traits
+
+    # We then move through the metaweb step by step
+    cursor = 0
+    for i in species(M; dims=1), j in species(M; dims=2)
+        cursor += 1
+        # Interaction in the metaweb?
+        labels[cursor] = M[i, j]
+        # Values in the PCA space
+        p_i = findfirst(i .== species(N))
+        p_j = findfirst(j .== species(N))
+        features[1:nf, cursor] .= pr[1:nf, p_i]
+        features[(nf + 1):end, cursor] .= pr[1:nf, p_j]
+        # Co-occurrence?
+        for b in B
+            if i in species(b)
+                if j in species(b)
+                    cooc[cursor] = true
+                end
+            end
+        end
+    end
+
+    # We only work on the species pairs that DO co-occur
+    x = Float64.(copy(features[:, :])) # Latent traits
+    y = labels
+
+    x,y
+end
+
+function feature_dataframe(featuresmatrix, labels)
+    total_nf, nlabels = size(featuresmatrix)
+    nf_per_species = Int64(total_nf/2)
+
+    df = DataFrame(label=labels)
+    for i in 1:nf_per_species
[…]

### 2023-01-19 src/resampling/src/utils.jl

@@ -1,0 +1,59 @@
+
+struct CooccurrenceMatrix{S,F}
+    species::Vector{S}
+    matrix::Matrix{F}
+end
+
+struct InteractionsMatrix{S,F}
+    species::Vector{S}
+    matrix::Matrix{F}
+end
+
+struct RelativeAbundance{S,F}
+    species::Vector{S}
+    relativeabundances::Vector{F}
+end
+
+num_partitions(ra::RelativeAbundance) = length(ra.species)
+partition(ra::RelativeAbundance, i) = 
+    RelativeAbundance([ra.species[i]], [ra.relativeabundances[i]])
+
+function sample(ra::RelativeAbundance, n)
+    K = num_partitions(ra)
+    K == 1 ? ra.species[begin][rand(Categorical(ra.relativeabundances[begin]), n)] : sample.([partition(ra, i) for i in 1:K],n) 
+end 
+
+
+# sample from relative abundance
+struct CooccurrenceSampler
+    relativeabundance::RelativeAbundance
+end
+function sample(cs::CooccurrenceSampler, n)
+    species = cs.relativeabundance.species
+    cooc_sample = sample(cs.relativeabundance, n)
+    mat = length(species) > 1 ? zeros(Bool,size(species[1])[1], size(species[2])[1]) : zeros(Bool,size(species[1]), size(species[1]))
+
+    if length(species) == 1
+        for (i,s) in enumerate(species[1]), (j,t) in enumerate(species[1])
+            mat[i,j] = s ∈ cooc_sample && t ∈ cooc_sample[1]
+        end
+    else
+        for (i,s) in enumerate(species[1]), (j,t) in enumerate(species[2])
+            mat[i,j] = s ∈ cooc_sample[1] && t ∈ cooc_sample[2]
+        end
+    end
+
+    CooccurrenceMatrix(cs.relativeabundance.species, mat)
+end 
+
+
+# compute FNR stats from Coocc sample
+function FNR(cooccurrence_sample, C, M)
+    cooc = findall(I->C[I] > 0, CartesianIndices(adjacency(M)))
+    sampled, real = cooccurrence_sample.matrix, adjacency(M)
+
+    fn = length(findall(I->real[I] && !sampled[I], CartesianIndices(sampled)))
+    fn/prod(size(real[cooc]))
+end 
+
+

### 2023-02-28 src/resampling/main.jl
:facepalm: duplicate sentence?

@@ -42,12 +42,12 @@ cooc = CooccurrenceMatrix([M.T,M.B], C)
 ints = InteractionsMatrix([M.T,M.B], N)
 
 exp_fpr = Exponential(0.02)
-cooccurrence_sample = InteractionUncertaintySampler.sample(CooccurrenceSampler(relabd), 1000)
+cooccurrence_sample = sample(CooccurrenceSampler(relabd), 1000)
 mean_fnr = FNR(cooccurrence_sample, C, M)
 
 
 using DataFrames, CSV
-df = CSV.read("modelfit.csv", DataFrame)
+df = CSV.read("./src/resampling/src/modelfit.csv", DataFrame)
 
 # predicted prob metaweb
 P = zeros(size(M))
